### 2017-10-02 paper.tex
initialize the paper

\documentclass[12pt]{article}
\usepackage{tikz}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{amsthm}
\usepackage{bm}
\usepackage{tcolorbox}
\tcbuselibrary{skins}
\usepackage{lipsum}
\usepackage[linesnumbered]{algorithm2e}
\makeatletter
\renewcommand{\@algocf@capt@plain}{above}
\makeatother
\usetikzlibrary{decorations.pathreplacing}
\usetikzlibrary{arrows}
\usetikzlibrary{snakes}
\usetikzlibrary{calc}
\let\emptyset\varnothing
\definecolor{hotpink}{rgb}{0.9,0,0.5}
\definecolor{deepgray}{gray}{0.35}
\definecolor{deepgray2}{gray}{0.25}
\definecolor{deepgray3}{gray}{0.10}
\definecolor{lightgray}{gray}{0.95}
\definecolor{lightgray2}{gray}{0.85}
\definecolor{purple1}{RGB}{239,229,244}
\definecolor{purple2}{RGB}{216,191,216}
\definecolor{lightblue}{rgb}{0.73,0.33,0.83}
\definecolor{lightpurple}{rgb}{.8,.2,.8}
\definecolor{textcolor}{rgb}{0,0,5}
\definecolor{blue1}{RGB}{187,217,238}
\definecolor{blue2}{RGB}{235,244,250}
\definecolor{yellow1}{RGB}{255,255,102}
\definecolor{blue3}{RGB}{63,40,96}
\definecolor{red1}{RGB}{255, 102, 102}
\definecolor{green1}{RGB}{102, 255, 102}
\newtheorem{lemma}{Lemma}
\newtheorem{theorem}{Theorem}
\newtheorem{definition}{Definition}
\theoremstyle{definition}
\def\proof{\par{\bf Proof}. \ignorespaces}
\def\qedsymbol{\vbox{\hrule\hbox{%
                     \vrule height1.3ex\hskip0.8ex\vrule}\hrule}}
\def\endproof{\qquad\qedsymbol\medskip\par}

% \usepackage{booktabs} % For formal tables
% \usepackage{cite}
\usepackage{url}
% \newtheorem{definition}{Definition}[section]
% \newtheorem{theorem}{Theorem}[section]
% \usepackage{algorithmic}
% \usepackage[cmex10]{amsmath}
\usepackage{amssymb}

\title{A Closer Look at Time-Preserving Paths on Evolving Graphs}

\author{Jiahao Chen and 
Weijian Zhang
\thanks{%
  School of Mathematics,
The University of Manchester,
                Manchester, M13 9PL, England.
\texttt{weijian.zhang@manchester.ac.uk}.
}
}

\def\R{\mathbb{R}}
\def\C{\mathbb{C}}
\def\nbyn{n \times n}
\def\mbyn{m \times n}
\def\l{\lambda}
\def\norm#1{\|#1\|}      
\def\normi#1{\|#1\|_1}
\def\normo#1{\|#1\|_{\infty}}
\def\Chat{\widehat{C}}
\def\e{eigenvalue}

% \DeclareMathOperator{\diag}{diag}   % Requires amsmath.
\def\diag{\mathop{\mathrm{diag}}}     % If not using amsmath.
\def\trace{\mathop{\mathrm{trace}}}   % If not using amsmath.

\def\At{\widetilde{A}}
\def\normt#1{\|#1\|_2}

% Note: this clashes with amsmath.
\def\bmatrix#1{\left[\matrix{#1}\right]}

\begin{document}

%\subtitlenote{The full version of the author's guide is available as
 % \texttt{acmart.pdf} document}

\maketitle

\begin{abstract}
This paper studies evolving graph centrality from the perspective of time-preserving paths. We describe time-preserving paths based on two dimensions of variation, namely static edges and causal edges.

A time-preserving path on evolving graph makes implicit assumptions about the type of edges in which a path traverse. For example, some measures count only static edges,
while some measures take account of both static edges and causal edges. In addition, the length of a time-preserving path can be either spatial or temporal.

We study the impact of different time-preserving paths on node centrality. We compare evolving graph centrality with the aggregated static graph case to gain insight about the advantage of evolving graph model. We construct an evolving coauthor network from
a collection of research papers for the experiments.
\end{abstract}

\section{Introduction}
\label{sec:introduction}

In the 1985 science-fiction film ``Back to the Future'', Marty McFly (played by Michael J. Fox) traveled back in time and accidentally changed the history.
However, we cannot travel back in time or even send a message to the past.
An evolving graph in general is a time dependent graph $G(t) = (V(t), E(t))$.
To traverse an evolving graph, one has to consider time. In particular, a path on an evolving graph needs to be time-preserving, meaning a node can not pass a massage (through an edge) to a node at a earlier time.

% time-respecting path
We represent an evolving graph as a time-ordered sequences of graphs, similar to the work of Tang and coworkers \cite{tang10, tang102, tang09, nicosia13} and Grindrod, Higham and coworkers \cite{grindrod11, grindrod13}. The idea is to divide the system's time span into temporal slices and regards it as a sequence of static graphs $\{G^{[t]}\}$, one for each layer. A node on a slice $G^{[t]}$ is represented by a pair $(v, t)$, where $v$ is a node of $G^{[t]}$ and $t$ is the time stamp of the slice. A time-respecting path of length $n$ is a sequence of these node pairs $\langle (v_1, t_1), (v_2, t_2), \ldots ,(v_m, t_m)\rangle$, where $t_1 \le t_2 \le \cdots \le t_n$. Note if $t_i = t_j$, then $\langle (v_i, t_i), (v_j, t_j) \rangle$ is an edge at a temporal slice,  otherwise it is an edge linking nodes from different temporal slices. 
We call edges of the first kind \emph{static edges} and of the second kind
\emph{causal edges}.
For example, in Figure \ref{fig:eg_shortest_path}
$\langle (1, t_1), (2, t_1) \rangle$ is a static edge at time stamp $t_1$ and $\langle (3, t_2), (3, t_3) \rangle$ is a causal edge between time stamp $t_2$ and time stamp $t_3$.
The difference between static edges and causal edges were introduced in \cite{chen16}.

\begin{figure}[h]
 \begin{center}
    \begin{tikzpicture}[scale=.38, line width =1.5pt]
  \node[circle,fill=green1, minimum size=0.2cm] (n7) at (-5,7) {2};
  \node[circle,draw=red1, minimum size=0.2cm] (n8) at (-10,5) {3};
  \node[circle,fill=green1, minimum size=0.2cm] (n10) at (-8,10) {1};
  \node[circle,draw=red1, minimum size=0.2cm] (n6) at (3,7) {2};
  \node[circle,fill=green1, minimum size=0.2cm] (n4) at (-2,5) {3};
  \node[circle,fill=green1, minimum size=0.2cm] (n1) at (0,10) {1};

   \node[circle,fill=green1, minimum size=0.2cm] (n11) at (11,7) {2};
  \node[circle,fill=green1, minimum size=0.2cm] (n12) at (6,5)  {3};
  \node[circle,draw=red1, minimum size=0.2cm] (n14) at (8,10) {1};

  \foreach \from/\to in {n10/n7, n1/n4, n11/n12}
   \draw[every edge,->] (\from) -- (\to);
 \draw[dotted,->](n4) -- (n12);
\draw[dotted,->](n7) to[out=80, in=40](n11);
\draw [decorate,decoration={brace,amplitude=5pt},xshift=-4pt,yshift=0pt]
(4,3) -- (-2,3) node [midway,yshift=-0.6cm]{ $t_2$};
\draw [decorate,decoration={brace,amplitude=5pt},xshift=-4pt,yshift=0pt]
(-4,3) -- (-10.5,3) node [midway,yshift=-0.6cm]{ $t_1$};
\draw [decorate,decoration={brace,amplitude=5pt},xshift=-4pt,yshift=0pt]
(11.5,3) -- (5.5,3) node [midway,yshift=-0.6cm]{ $t_3$};
    \end{tikzpicture}
\end{center}
\caption{An evolving directed graph with 3 time stamps $t_1$, $t_2$ and $t_3$.
At each time stamp, the evolving graph is represented as a graph.
The green filled circles represent active nodes while the red circles represent
inactive nodes. Directed edges in each time stamp are shown as black arrows and directed edges between graphs are shown as dotted arrows.}
\label{fig:eg_shortest_path}
\end{figure}

It is natural to define the length of a path on a static graph as the number of nodes traveled through the path. For the weighted graph case, the length of a path is the total weight of all the edges in the path. We observe that static edges link nodes in space while causal edges link nodes in time. Hence we would like to distinguish temporal distance from spatial distance on an evolving graph: the length of a static edge is equal to the edge weight (or $1$ in the unweighted graph case); the length of a causal edge is the time distance between the two nodes. In the simplest case, the time-respecting path
$\langle (1, t_1) ,(2, t_1) , (2, t_3), (3, t_3)\rangle$ in Figure \ref{fig:eg_shortest_path} has length $4$ in total because two static edges $\langle (1, t_1) (2, t_1) \rangle$ and $\langle (2, t_3), (3, t_3) \rangle$ have length one, whereas $\langle (2, t_1) (2, t_3) \rangle$ traverse $2$ time stamps so has length $2$.

% We studies evolving graph centrality from the perspective of temporal network flows.
% Researchers have identified the time-preserving nature of such network flows, i.e., 
% we cannot travel between nodes from a later time to an early time.
% However, a closer look tells us there are subtle differences 
% in previous papers

% How about a reverse time-preserving network flow?

% our contribution this paper
Borgatti noted in \cite{borgatti05} that the manner of traffic flow entails a new way to think about centrality. In particularly, the importance of a node in a network can not be determined without reference to how traffic flows through the network. A time-preserving path on evolving graphs can be described by static edges, causal edges, or both.
Grindrod et al.'s definition of dynamic walk \cite{grindrod11} only count static edges. 
Tang et al \cite{tang10s} measures a temporal shortest path in time unites (or causal edges) only. If a node can reached by another node in $k$ time stamps then the distance between the two nodes is $k$. Chen and Zhang \cite{chen16} considered both static edges and causal edges in their definition of temporal path. 
To develop a centrality algorithm on evolving graphs, one has to consider the manner of temporal traffic flow.

The aim of this paper is as follows. First, to identity the type of time-preserving path in a list of common evolving graph centrality measures. Second, to vary static and causal edge weights and analyze the impact on selected measures of centrality.
Third, to solve a real world problem using evolving graph centrality: identify key authors in an evolving coauthor network. 
We design the experiment using the Julia dynamic network analysis package
EvolvingGraphs.jl (\url{https://github.com/EtymoIO/EvolvingGraphs.jl}).
We use the research paper data gathered from Etymo (\url{https://etymo.io}), a visual search engine for data scientists.

\section{Background}
\label{sec:preliminaries}

Let $G$ be a directed graph with $n$ nodes with the corresponding adjacency matrix 
$A \in \R$.

A \textbf{walk} of length $r$ from node $i_1$ to node $j_{r+1}$ is a sequence of edges
$(i_1, i_2), (i_2, i_3), \ldots (i_r, i_{r+1})$.

\subsection{Graph Centrality}
\label{sec:katz-centrality}

% definition of various graph centrality algorithms
We review the Katz centrality here.
Let $A$ be the adjacency matrix of a graph $G=(V,E)$ and $\rho(A)$ be the spectral radius of $A$. Suppose $\alpha < 1/ \rho(A)$, then the Katz centrality vector of $G$ is
\[
(I - \alpha A)^{-1}e.
\]

The betweenness centrality of a node $i$ in a static graph is defined as
$$
C_i = \sum_{j \in V}\sum_{k \in V, k \ne j} \frac{\rho_{jk}(i)}{\rho_{jk}},
$$
where $\rho_{jk}$ is the number of shortest paths from node $j$ to node $k$, while $\rho_{jk}(i)$ is the number of shortest paths from node $j$ to node $k$ that pass through node $i$.

% \subsection{Eigenvector Centrality}
% \label{sec:eigenv-centr}

% Given an adjacency matrix $A$ of a graph $G$, eigenvector centrality is defined as the dominant eigenvector of $A$, i.e.,
% \[
% \lambda v = Av,
% \]
% where $\lambda$ is the dominate eigenvalue of $A$ and $v$ is the corresponding eigenvector. Variations of eigenvector centrality includes Katz centrality \cite{katz53}, PageRank \cite{page99}, Hubbell's clique identification \cite{hubbell65}, Friedkin's actors' network centrality \cite{friedkin91}.
% In general, all eigenvector-like centrality are influence measures, meaning that even if a node $a$ only influences one node $b$, who influences many other nodes, then $a$ is highly influential.

% Let $A$ be the adjacency matrix of a graph $G = (V,E)$, i.e., $A_{i,j} = 1$ if node $i$ is linked to node $j$ and $A_{i,j} = 0$ otherwise. The idea of eigenvector centrality is that
% each node's centrality is the sum of the centrality values of the nodes that it is connected to. In other words, the relative centrality of node $v$ can be defined as 
% \[
% x_v = \frac{1}{\lambda}\sum_{t \in M(v)} x_t = \frac{1}{\lambda}\sum_{t \in G} A_{v, t}x_t,
% \]
% where $M(v)$ is the set of neighbor nodes of $v$. We can write it in matrix notation as
% \[
% \lambda x = Ax.
% \]
% The eigenvector centrality of $G$ is the dominant (or principle) eigenvector of $A$.
% One may ask why we choose dominant eigenvector not any other eigenvectors? The answer comes from Perron-Frobenius Theorem (more details later).

% In \cite{bonacich91}, Bonacich prove the following theorem. 
% \begin{theorem}
%   Assume that a symmetric non-negative matrix $A$ has a single largest eigenvalue $\lambda_1$ and its corresponding eigenvector $v_1$. Let $e$ be a column vector of ones. The infinite sum $A + \beta A^2 + \beta^2 A^3 + \beta^3 A^4 + \cdots$ converges
% if $|\beta| < 1/ \lambda_1$. Moreover, as $\beta$ approaches $1/\lambda_1$ from below,
% $(1-\beta\alpha_1)(A+ \beta A^2 + \beta^2 A^3 + \beta^3 A^4 + \cdots)e$ approaches $v_1$. 
% \end{theorem}
% In other words, the eigenvector centrality of $G$ can be thought as proportional to an
% infinite sum
% \begin{equation}
% \label{eq:s}
% Se = Ae+ \beta A^2e + \beta^2 A^3e + \beta^3 A^4e + \cdots.
% \end{equation}
% Note however if $\beta = 1/\lambda_1$, the series does not converge.
% Eq. \eqref{eq:s} offers great flexibility to think about related centrality measures.
% For example, in the PageRank case
% \[
% r = Gr,
% \]
% where $G$ is a stochastic matrix. Then
% \[
% Se = Ge + \beta G^2e + \beta^2 G^3e + \beta^3 G^4 e + \cdots
% \]
% converges to $r$ as $\beta$ approaches $1$ from below.

% Note when $\alpha < 1/\rho(A)$, the spectral radius of $A$,
% \[
% (I - \alpha A)^{-1} = I + \alpha A + \alpha^2 A^2 + \alpha^3 A^3 + \cdots.
% \]
% Hence from eq. \eqref{eq:s} we have
% \[
% \beta Se + 1 = (I - \beta A)^{-1}e.
% \]
% This means eigenvector centrality can interpreted as Katz centrality with special chosen parameter value $\beta$. We mention that Aprahamian et. al. \cite{ahh16} consider selecting the Katz parameter based on the objective of matching the centrality of the exponential counterpart.

% \textbf{WZ:} some analysis need to be done on the relationship between
% $\beta$ and $v_1$. Derive some upper or lower bounds.

% %katz case
% Suppose we let 
% \[
% S = A + \alpha_1^{-1} A^2 + \alpha_1^{-2} A^3 + \cdots,
% \]
% then $u = Se$ is proportional to the eigenvector $v_1$.

% In PageRank's case
% \[
% r = Gr,
% \]
% which means $\alpha_1 = 1$.

% Since Katz centrality can be written as
% \[
% (1- \alpha A)
% \]
% so it can be regard as a special case of eigenvector centrality.

% % \subsection{The Datasets}
% % \label{sec:datasets}

% % The data is a list of papers with associated information, including author names, affiliation, journal, and year of publication, and the full text content. We will test our algorithms on a collection of articles from, NIPS, an
% d ICLR.

% \subsection{Author Name Disambiguation}
% \label{sec:auth-name-disamb}

% We follow the idea from \cite{martin13} to disambiguate author names.

% \section{Eigenvector Centrality on Evolving Graphs}
% \label{sec:centr-algor}

% Let $A^{[t]}$ be the corresponding graph $G^{[t]}$ at a time label $t$. In \cite{grindrod11},
% Grindrod et. al. observes that the matrix product $A^{[t_1]}A^{[t_2]}\cdots A^{[t_w]}$ has
% $(i,j)$ element that counts the number of dynamic walks of length $w$ from node $i$ to node $j$ on which the $m$-th step of the walk takes place at time $t_m$. Therefore, the Katz centrality for evolving graphs can be written as
% \[
% Q = (I - \alpha A^{[0]})^{-1}(I - \alpha A^{[1]})^{-1} \cdots (I - \alpha A^{[m]})^{-1}.
% \]

% Follow the discussion from Section \ref{sec:eigenv-centr}, we can generalize eigenvector centrality and PageRank on evolving graphs.

\section{Time-Preserving Paths}
\label{sec:time-pres-paths}

We now describe time-preserving paths in more details. We follow the definition of
\emph{evolving graph}, \emph{temporal node} and \emph{active node} in \cite{chen16}.

\begin{definition}
  An \textbf{evolving graph} $G_n$ is a sequence of (static) graphs 
$G_n = \langle G^{[1]}, G^{[2]},  \ldots ,G^{[n]} \rangle$ with associated time stamps
$t_1, t_2, \ldots, t_n$ respectively. Each $G^{[t]} = (V^{[t]}, E^{[t]})$ represents a (static) graph labeled by a time t.
\end{definition}

Note the node sets $V^{[t]}$ can change over time, i.e., nodes may appear or disappear at a particular time stamp.
For example, in Figure \ref{fig:eg_shortest_path}, at time stamp $t_1$, $V^{[1]} = \langle 1, 2 \rangle$ and $E^{[1]} = \langle (1,2) \rangle$. Each graph $G^{[t]}$ can be represented by its adjacency matrix $A^{[t]}$. 
We can represent $G_n$ by a list of adjacency matrices $A_n = \langle A^{[1]}, A^{[2]}, \ldots, A^{[n]} \rangle$.

\begin{definition}
  A \textbf{temporal node} is a pair (v, t), where $v \in V^{[t]}$ is a node at a time $t$.
\end{definition}

%At each time stamp, we only count temporal nodes that connects by an edge.

\begin{definition}
  A temporal node $(v, t)$ is an \textbf{active node} if there exists at least one edge $e \in E^{[t]}$ that connects $v \in V^{[t]}$ to another node $w \in V^{[t]}, w\ne v$. Otherwise it is called an inactive node.
\end{definition}

In Figure \ref{fig:eg_shortest_path}, the filled green circles are active nodes. For the adjacency matrix representation, a node $i$ is active at time stamp $t$, then
the $i$th row or the $i$th column of $A^{[t]}$ has at least one none-zero entry.
 In general, a time-preserving path can be defined as follows.

\begin{definition}
A \textbf{time-preserving path}  of length $m$ on an evolving graph $G_n$ is a time-ordered sequence of active nodes, $\langle (v_1, t_1), (v_2, t_2), \ldots, (v_m, t_m) \rangle$, where $t_1 \le t_2 \le \cdots t_m$ and 
$v_i = v_j$ if and only if $t_i \ne t_j$.
\end{definition}

Note $\langle (v_i, t_i), (v_j, t_i) \rangle$ represents a static edge on graph $G^{[t_i]}$ while $\langle (v_i, t_i), (v_i, t_j) \rangle$ represents a causal edge from time stamp $t_i$ to time stamp $t_j$.

\begin{definition}
A \textbf{static edge} $\langle (v_i, t), (v_j, t)\rangle$ is a pair of elements of $V^{[t]}$, i.e., $v_i \in V^{[t]}$ and 
$v_j \in V^{[t]}$.
 A \textbf{causal edge} $\langle (v, t_i), (v, t_j)\rangle$ is a pair of the same node at different time stamps. 
\end{definition}

We can denote a \emph{weighted static edge} as $\langle (v_i, t), (v_j, t), w_s \rangle$ and a \emph{weighted causal edge} as $\langle (v, t_i), (v, t_j), w_t \rangle$.
Here $w_s$ represents the spatial distance between the two nodes $v_i$ and $v_j$; $w_t$ represents the 
temporal distance of $v$ at different time stamps. 
In Figure \ref{fig:eg_shortest_path}, the black arrows represent static edges and the dotted arrows represent causal edges.
Suppose we assign all the static edge weight to be $1$ and
assign the causal edge to be the number of time stamps between the pair. Then in Figure \ref{fig:eg_shortest_path}
the edge weight between $(1, t_1)$ and $(2, t_1)$ is $1$ and the edge weight between $(2, t_1)$ and $(2, t_3)$
 is $2$.

A time-preserving path can traverse both causal edges and static edges.
We will see in the next section evolving centrality measures make implicit assumptions about the type of edges in the 
time-preserving path that is used.

\subsection{Reverse Temporal Flows}
\label{sec:reverse-temp-flows}

We can not travel back in time. But reverse the direction of temporal flows can help
identify the ``hub'' nodes or the source of the flows. The authority score of a page is 
proportional to its importance, and the hub score describes the quality of a page as a link collection of important related pages \cite{kleinberg99}.
Indeed, reverse PageRank has
been studied by \cite{fogaras03, bar08, gleich15}. In reverse PageRank we compute PageRank on the graph with reversed direction, i.e., reverse the direction of each edge $(i,j)$ to $(j, i)$.
Fogaras \cite{fogaras03} shows that Reversed Page Rank sores express hub quality.

Recall a time-preserving path is a time-ordered sequence of active nodes. Here we define a \emph{reversed temporal path} to be a reversed time-ordered sequence of active nodes, i.e.,
$t_1 \ge t_2 \ge \cdots \ge t_m$.

\section{Relation to Centrality Measures}
\label{sec:topol-temp-flow}

We review a few well-known measures of evolving graph centrality.

\subsection{Temporal Katz Centrality}
\label{sec:temp-katz-centr}

In \cite{grindrod11}, Grindrod et. al. defines a \emph{dynamic walk} of length $m$ from
node $v_1$ to node $v_{w+1}$  as a sequence of edges 
$(v_1, v_2), (v_2, v_3), \ldots (v_w, v_{w+1})$ and a non-decreasing sequence of times
$t_{r_1} \leq t_{r_2} \leq \cdots \leq t_{r_w}$ such that the adjacency matrix at time stamp
$r_m$, i.e., $A_{i_m, i_{m+1}}^{[r_m]} \ne 0$. Note in this definition, the authors only take account of the static edges and the length of a dynamic walk is determined by the number of static edges.

The Katz centrality is based on a sequence of matrix products
\begin{equation}
\label{eq:katz}
Q = (I - \alpha A^{[0]})^{-1}(I - \alpha A^{[1]})^{-1} \cdots (I - \alpha A^{[M]})^{-1}.
\end{equation}
The $i$th row and column sums
$$
C_i^{broadcast} = \sum_{k=1}^n Q_{ik}, \quad C_i^{receive} = \sum_{k=1}^n Q_{ki}
$$
are the broadcast centrality and receive centrality of node $i$.

\subsection{Temporal Betweenness Centrality}
\label{sec:temp-betw-centr}

\subsection{Temporal Closeness Centrality}
\label{sec:temp-clos-centr}

To write later.

\subsection{Temporal PageRank}
\label{sec:temporal-pagerank}

To write later.

\subsection{Centrality on a Block Adjacency Matrix}
\label{sec:centr-block-adjac}

We can represent an evolving graph $G_n$ by a static graph $G$.

Here we discuss different types of temporal flow on the evolving graphs.
\begin{itemize}
\item Only static edges.
\item Only causal edges.
\item Both causal edges and static edges.
\item Reverse temporal flows.
\item Active nodes.
\end{itemize}

\subsection{Only Static Edges}
\label{sec:only-static-edges}

\subsection{Only Causal Edges}
\label{sec:only-causal-edges}

In \cite{tang10s}, a temporal shortest path is measured in time units only, i.e., if node
$v_i$ can reach node $v_j$ in $k$ time steps then the distance between node
$v_i$ and $v_j$ is $k$. If we define temporal path in this way (only take accounts of the time stamps), we have a new centrality definition. 
We can use temporal breadth first
search \cite{chen16} to discover all the temporal paths and then only take account of the difference between the time stamp of the first node and the time stamp of the last node.

In matrix form, the nonzero entries of $A^{[t_i]} A^{[t_{i+1}]}$ counts all the temporal paths of length $1$, and 
$A^{[t_i]}\cdots A^{[t_j]}$, where $i < j$ counts all the temporal paths of length $j -i$. 
For example, $A^{[1]}A^{[4]}$, $A^{[1]}A^{[1]}A^{[4]}$ and $A^{[1]}A^{[2]}A^{[3]}A^{[4]}$ are both walks of length 3.
In the original Katz centrality, the `attenuation' factor $\alpha$ is imposed on the
number of walks, i.e., longer walks has smaller effect to overall rating. In this case, the final result is the summation of all products of the form
\[
\alpha^k A^{[i]} \cdots A^{[i+k]}
\]
Note this can not be written in \eqref{eq:katz}. The eigenvector centrality vector $v$ is the limit of
\[
v = \lim_{k \rightarrow \inf}\big[ \frac{1}{k} (A + \lambda_1^{-1} A^2 + \lambda_1^{-2}A^3 + \cdots + \lambda_1^{-k}A^{k+1})\big].
\]
Here we can replace $A^2$ or $A^3$ by $A^{[1]}A^{[2]}$ for the evolving graph case.
Since PageRank is a eigenvalue problem of a weighted matrix $G$ (instead of $A$),
 we can also express PageRank in this form. There has some work on writing evolving graph Pagerank as a sequence of PageRank matrix product.

\subsection{Both Static Edges and Causal Edges}
\label{sec:both-static-edges}

Another definition of temporal path was introduced by \cite{chen16}. In their definition,
both static edges and causal edges are considered. We can written the evolving graph centrality as a big static block matrix and Katz centrality of this big matrix. This gives you the importance of each node at different time stamps. We can `average' these ratings at different time stamp to get the final results.

Let's see a simple example. For the evolving graph shown below

\section{Experiments}
\label{sec:experiments}

In this section we describe some illustrative

\subsection{Synthetic Data}
\label{sec:synthetic-data}

\subsection{JMLR Coauthor Network}
\label{sec:jmlr-coauth-netw}

We construct the evolving coauthor network from Etymo (\url{https://etymo.io}).
We collected $1566$ publications published by Journal of Machine Learning Research (JMLR) papers from $2001$ to $2017$ with authors involved. We regard each year
as a time stamp and there are $17$ time stamps in total. At each time stamp, we 
create a undirected edge (or two directed edges) between two authors if they have coauthored at least one paper.

A second network is

author names, affiliation, journal, and year of publication.

We are interested in finding out how good evolving graph centrality algorithms
comparing with static graph ones. 
Also how the way to

stability, reasonable solutions that can be applied in practice.

% \subsubsection{Aggregated Graphs and Evolving Graphs}
% \label{sec:aggr-graphs-evolv}

Evolving graph model is

We conduct the experiments on a list of papers with associated information, including author names, affiliation, journal, and year of publication

Evaluating and comparing the performance of centrality algorithms is hard as there is no formal definition for the ``qualities'' of a person.

% subsection{Simulations}
% \label{sec:simulations-1}

% In \cite{borgatti05}, Borgatti simulate different types of walk flow on the network and
% compare the node statistics with the centrality measures.

% For katz centrality, eigenvector centrality, and PageRank (all on evolving graphs), we test all 3 different types of temporal flows.

% Problem setup: given a group of authors in an evolving graph, finding the most important authors. We use real dataset with real names.

% Build the evolving graph with author name disambiguation and apply the above algorithms.

% \subsection{Katz Centrality}
% \label{sec:katz-centrality-1}

% \subsection{Eigenvector Centrality}
% \label{sec:eigenv-centr-1}

% \subsection{PageRank}
% \label{sec:pagerank}

\section{Conclusion}
\label{sec:conclusion}

To write later.

\bibliographystyle{plain}
\bibliography{sigproc}

\end{document}

%%% Local Variables:
%%% mode: latex
%%% TeX-master: t
%%% End:

### 2017-10-05 paper.tex
add more content

@@
 
-A time-preserving path on evolving graph makes implicit assumptions about the type of edges in which a path traverse. For example, some measures count only static edges,
-while some measures take account of both static edges and causal edges. In addition, the length of a time-preserving path can be either spatial or temporal.
+A time-preserving path on evolving graphs makes implicit assumptions about the type of edges in which a path traverse. For example, some papers count only static edges,
+while some take account of both static edges and causal edges. In addition, the length of a time-preserving path can be either spatial or temporal.
 
-We study the impact of different time-preserving paths on node centrality.
-We compare evolving graph centrality with the aggregated static graph case to gain insight about the advantage of evolving graph model.
-We construct an evolving coauthor network from
-a collection of research papers for the experiments.
+We study the impact of different time-preserving paths on node centrality by varying the edge weights of static and causal edges.
+We also compare evolving graph centrality with the aggregated static graph case to gain insight about the advantage of evolving graph model.
+We construct an evolving coauthor network from a collection of research papers for the experiments.
 \end{abstract}
@@
 
-In the 1985 science-fiction film ``Back to the Future'', Marty McFly (played by Michael J. Fox) traveled back in time and accidentally changed the history.
+In the 1985 science-fiction film ``Back to the Future'', Marty McFly (played by Michael J. Fox) travelled back in time and accidentally changed the history.
 However, we cannot travel back in time or even send a message to the past.
@@
 We represent an evolving graph as a time-ordered sequences of graphs, similar to the work of Tang and coworkers \cite{tang10, tang102, tang09, nicosia13} and Grindrod, Higham and coworkers \cite{grindrod11, grindrod13}.
-The idea is to divide the system's time span into temporal slices and regards it as a sequence of static graphs $\{G^{[t]}\}$, one for each layer.
-A node on a slice $G^{[t]}$ is represented by a pair $(v, t)$, where $v$ is a node of $G^{[t]}$ and $t$ is the time stamp of the slice.
+The idea is to divide the system's time span into temporal slices and regards it as a sequence of static graphs $G^{[t]}$, one for each layer.
+A node on a slice $G^{[t]}$ is represented by a pair $(v, t)$, where $v$ is a node of
+$G^{[t]}$ and $t$ is the time stamp of the slice.
 A time-respecting path of length $n$ is a sequence of these node pairs $\langle (v_1, t_1), (v_2, t_2), \ldots ,(v_m, t_m)\rangle$, where $t_1 \le t_2 \le \cdots \le t_n$.
@@
 
-It is natural to define the length of a path on a static graph as the number of nodes traveled through the path.
+It is natural to define the length of a path on a static graph as the number of nodes travelled through the path.
 For the weighted graph case, the length of a path is the total weight of all the edges in the path.
@@
 In particularly, the importance of a node in a network can not be determined without reference to how traffic flows through the network.
+To develop a centrality algorithm on evolving graphs, one has to consider the manner of temporal traffic flow.
 A time-preserving path on evolving graphs can be described by static edges, causal edges, or both.
 Grindrod et al.'s definition of dynamic walk \cite{grindrod11} only count static edges.
-Tang et al \cite{tang10s} measures a temporal shortest path in time unites (or causal edges) only.
+Tang et al.
+\cite{tang10s} measures a temporal shortest path in time unites (or causal edges) only.
 If a node can reached by another node in $k$ time stamps then the distance between the two nodes is $k$.
 Chen and Zhang \cite{chen16} considered both static edges and causal edges in their definition of temporal path.
-To develop a centrality algorithm on evolving graphs, one has to consider the manner of temporal traffic flow.
 
@@
 
-The betweenness centrality of a node $i$ in a static graph is defined as
+The \emph{betweenness centrality} of a node $i$ in a static graph is defined as
 $$
@@
 $$
-where $\rho_{jk}$ is the number of shortest paths from node $j$ to node $k$, while $\rho_{jk}(i)$ is the number of shortest paths from node $j$ to node $k$ that pass through node $i$.
+where $\rho_{jk}$ is the number of shortest paths from node $j$ to node $k$, while $\rho_{jk}(i)$ is the number of shortest paths from node $j$ to node $k$ that pass through node $i$
 
+% The \emph{communicability betweenness centraltiy} \cite{estrada09} for a node $i$ is defined as
+% $$
+% C_i = C_N\sum_p \sum_q \frac{\exp(A)_{p,q} - \exp(A - E(i))_{p,q}}{\exp(A)_{p,q}},
+% $$
+% where $C_N = \frac{1}{(N-1)^2 - (N-1)}$ is a normalizing factor and $E(i)$
+% has nonzeros only in row and column $i$, and in such row and column has $-1$ wherever $A$ has $1$. Similarly, the \emph{resolvent betweenness centrality} for node $i$ is defined as
+% $$
+% C_i = C_N\sum_p \sum_q \frac{(I - \alpha A)^{-1}_{p,q} - (I - \alpha(A - E(i)))^{-1}_{p,q}}{(I - \alpha A)^{-1}_{p,q}}.
+% $$
 % \subsection{Eigenvector Centrality}
@@
 
+In \cite{tang10s}, a temporal shortest path is measured in time units only, i.e., if node
+$v_i$ can reach node $v_j$ in $k$ time steps then the distance between node
+$v_i$ and $v_j$ is $k$. We can apply temporal breadth first
+search (BFS) \cite{chen16} to discover the temporal paths and then only take account of the temporal difference between the first node $(v_1, t_1)$ and the last node $(v_n, t_n)$, i.e., $t_n - t_1$.
+
+If we use this definition of temporal path for the temporal Katz centrality introduced by
+\cite{grindrod11}, we have a new centrality measure.
+In the matrix form, the nonzero entries of $A^{[t_i]} A^{[t_{i+1}]}$ counts all the temporal paths of length $1$, and
+$A^{[t_i]}\cdots A^{[t_j]}$, where $i < j$ counts all the temporal paths of length $j -i$.
+For example, $A^{[1]}A^{[4]}$, $A^{[1]}A^{[1]}A^{[4]}$ and $A^{[1]}A^{[2]}A^{[3]}A^{[4]}$ are all walks of length 3.
+In the original Katz centrality, the `attenuation' factor $\alpha$ is imposed on the
+number of walks, i.e., longer walks has smaller effect to the overall rating.
+Hence the final result is the summation of all products of the form
+\[
+\alpha^k A^{[i]} \cdots A^{[i+k]}
+\]
+Note this can not be written in \eqref{eq:katz}, as discussed in Section \ref{sec:temp-katz-centr}.
+
+Another definition of temporal path was introduced by \cite{chen16}. Here
+both static edges and causal edges are considered.
+We can represent an evolving graph with a block adjacency matrix.
+Centraliy on this block matrix gives the importance of each node at all time stamps.
+We can average these rating at different time stamps to
+get the final rating.
+
 We review a few well-known measures of evolving graph centrality.
-
+(Design a simple example and discuss it in each case below.)
 \subsection{Temporal Katz Centrality}
@@
 
-In \cite{grindrod11}, Grindrod et. al. defines a \emph{dynamic walk} of length $m$ from
+In \cite{grindrod11}, Grindrod et al. defines a \emph{dynamic walk} of length $m$ from
 node $v_1$ to node $v_{w+1}$  as a sequence of edges
@@
 
+Recall that betweenness centrality of a node in a static graph is defined by counting the fraction of shortest paths that traverse it.
+We could extend
+betweenness centrality on evolving graphs by replacing shortest paths with temporal shortest paths \cite{nicosia13}.
+\begin{equation}
+  \label{eq:bet1}
+C_i^{betweenness} = \sum_{j \in V}\sum_{k \in V, k \ne j}\frac{\alpha_{jk}(i)}{\alpha_{jk}},
+\end{equation}
+where $\alpha_{jk}$ represents the number of temporal shortest paths from node $j$ to node $k$ and $\alpha_{jk}(i)$ represents the number of temporal shortest paths from node $j$ to node $k$ that pass through the node $i$.
+
+One may want to take into account the length of time a node trains a message. The temporal betweenness centrality of the node $i$ at time stamp $t_m$ is defined as
+\begin{equation}
+  \label{eq:bet2}
+  C_i^{betweenness}(t_m) = \sum_{j\ne i}\sum_{k\ne j, k\ne i}\frac{U_{j,k,t_m}(i)}{\alpha_{j,k}},
+\end{equation}
+where as before $\alpha_{j,k}$ represents the number of temporal shortest paths from $j$ to $k$ and $U_{j,k,t_m}(i)$ represents the number of temporal shortest paths from $j$ to $k$ in which node $i$ is traversed from
+the path in the time stamp $t_m$ or a previous time stamp $t_{m-1}$. Then
+average temporal betweenness of node $i$ is then defined as
+$$
+  C_i^{betweenness} = \frac{1}{M}\sum_m C_i^{betweenness}(t_m).
+$$
+Note \eqref{eq:bet1} only takes account of static edges while \eqref{eq:bet2} takes account of both static edges and causal edges.
+
 \subsection{Temporal Closeness Centrality}
@@
 
-To write later.
-
-\subsection{Temporal PageRank}
-\label{sec:temporal-pagerank}
-
-To write later.
+Let $d_{ij}$ is the length of temporal shortest path from $i$ and $j$ in an evolving graph. Then
+the closeness centrality of a node $i$ is defined
+$$
+C_i^{closeness} = \frac{N-1}{\sum_j d_{ij}}.
+$$
+Note depends on how we define the length of temporal shortest path, the closeness centrality can takes account of only static edges, only causal edges, or both.
 
@@
 
-We can represent an evolving graph $G_n$ by a static graph $G$.
+In \cite{chen16}, we derive a block adjacency matrix representation.
+Let $E'$ be the set of causal edges and $\hat E$ be the set of static edges then
+an evolving graph can be represented as
+$$
+\bm M_n =
+\begin{pmatrix}
+A^{[t_1]} & M^{[t_1, t_2]} & \ldots & M^{[t_1, t_n]} \\
+0         & A^{[t_2]} & \ldots & M^{[t_2, t_n]} \\
+          & \ldots    &        &     \\
+0         & 0         & \ldots & A^{[t_n]}
+\end{pmatrix},
+$$
+where $M^{[t_i, t_j]}$ is the matrix whose rows are labeled by $V^{[t_i]}$ and columns are labeled by $V^{[t_j]}$, and whose entries are
+$$
+  M_{uv}^{[t_i, t_j]} =
+  \begin{cases}
+    1 & \mbox{if} (u, v) \in E' \\
+    0 & \mbox{otherwise}.
+  \end{cases}
+$$
+The adjacency matrix blocks $A^{[t]}$ encode the static edge set $\hat E$, whereas the off-diagonal blocks $M^{[t_i, t_j]}$ encode the causal edge set $E'$.
 
-Here we discuss different types of temporal flow on the evolving graphs.
-\begin{itemize}
-\item Only static edges.
-\item Only causal edges.
-\item Both causal edges and static edges.
-\item Reverse temporal flows.
-\item Active nodes.
-\end{itemize}
+We can apply static graph centrality algorithms to $M_n$ and then take the average of ratings at each each time stamp. For example, we can construct the Google matrix
+$G_n$ from $M_n$ and the ranking of the nodes can be found by solving
+$$
+ r= G_n r.
+$$
 
-\subsection{Only Static Edges}
-\label{sec:only-static-edges}
+For Figue \ref{fig:eg_shortest_path}, we have
 
-\subsection{Only Causal Edges}
-\label{sec:only-causal-edges}
+\begin{align*}
+V & = \{(1,\!t_1), (2,\!t_1), (1,\!t_2), (3,\!t_2), (2,\!t_3), (3,\!t_3)\},\\
+\tilde E &= \{((1,\!t_1), (2,\!t_1)), ((1,\!t_2), (3,\!t_2)), ((2,\!t_3), (3,\!t_3))\},\\
+E'  &= \{((1,\!t_1), (1,\!t_2)), ((2,\!t_2), (2,\!t_3)), ((3,\!t_2), (3,\!t_3))\}.
+\end{align*}
 
-In \cite{tang10s}, a temporal shortest path is measured in time units only, i.e., if node
-$v_i$ can reach node $v_j$ in $k$ time steps then the distance between node
-$v_i$ and $v_j$ is $k$. If we define temporal path in this way (only take accounts of the time stamps), we have a new centrality definition. 
-We can use temporal breadth first
-search \cite{chen16} to discover all the temporal paths and then only take account of the difference between the time stamp of the first node and the time stamp of the last node.
+and corresponding block adjacency matrix is
 
-In matrix form, the nonzero entries of $A^{[t_i]} A^{[t_{i+1}]}$ counts all the temporal paths of length $1$, and 
-$A^{[t_i]}\cdots A^{[t_j]}$, where $i < j$ counts all the temporal paths of length $j -i$. 
-For example, $A^{[1]}A^{[4]}$, $A^{[1]}A^{[1]}A^{[4]}$ and $A^{[1]}A^{[2]}A^{[3]}A^{[4]}$ are both walks of length 3.
-In the original Katz centrality, the `attenuation' factor $\alpha$ is imposed on the
-number of walks, i.e., longer walks has smaller effect to overall rating. In this case, the final result is the summation of all products of the form
 \[
-\alpha^k A^{[i]} \cdots A^{[i+k]}
+\bm M_3 = \begin{pmatrix}
+0 & 1 & 1 & 0 & 0 & 0 \\
+0 & 0 & 0 & 0 & 1 & 0 \\
+0 & 0 & 0 & 1 & 0 & 0 \\
+0 & 0 & 0 & 0 & 0 & 1 \\
+0 & 0 & 0 & 0 & 0 & 1 \\
+0 & 0 & 0 & 0 & 0 & 0
+\end{pmatrix}
 \]
-Note this can not be written in \eqref{eq:katz}. The eigenvector centrality vector $v$ is the limit of
-\[
-v = \lim_{k \rightarrow \inf}\big[ \frac{1}{k} (A + \lambda_1^{-1} A^2 + \lambda_1^{-2}A^3 + \cdots + \lambda_1^{-k}A^{k+1})\big].
-\]
-Here we can replace $A^2$ or $A^3$ by $A^{[1]}A^{[2]}$ for the evolving graph case.
-Since PageRank is a eigenvalue problem of a weighted matrix $G$ (instead of $A$),
- we can also express PageRank in this form. There has some work on writing evolving graph Pagerank as a sequence of PageRank matrix product.
 
-\subsection{Both Static Edges and Causal Edges}
-\label{sec:both-static-edges}
+The static graph representation of Figure \ref{fig:eg_shortest_path} is shown in Figure \ref{fig:static}.
 
-Another definition of temporal path was introduced by \cite{chen16}. In their definition,
-both static edges and causal edges are considered.
-We can written the evolving graph centrality as a big static block matrix and Katz centrality of this big matrix.
-This gives you the importance of each node at different time stamps.
-We can `average' these ratings at different time stamp to get the final results.
+\begin{figure}[h]
+ \begin{center}
+   \begin{tikzpicture}[scale=.36, line width =1.4pt]
+  \node[circle,fill=green1, minimum size=0.1cm, inner sep = 0pt] (n7) at (-5,7)
+{\scriptsize $(2,t_1)$};
+  \node[circle,draw=red1, minimum size=0.2cm, inner sep = 0pt] (n8) at (-10,5)
+{\scriptsize $(3,t_1)$};
+  \node[circle,fill=green1, minimum size=0.1cm, inner sep = 0pt] (n10) at (-8,10) {\scriptsize $(1,t_1)$};
 
-Let's see a simple example. For the evolving graph shown below
+  \node[circle,draw=red1, minimum size=0.2cm, inner sep = 0pt] (n6) at (3,7)
+{\scriptsize $(2,t_2)$};
+  \node[circle,fill=green1, minimum size=0.2cm,  inner sep = 0pt] (n4) at (-2,5)
+{\scriptsize $(3,t_2)$};
+  \node[circle,fill=green1, minimum size=0.2cm,  inner sep = 0pt] (n1) at (0,10)
+{\scriptsize $(1,t_2)$};
+
+   \node[circle,fill=green1, minimum size=0.2cm,  inner sep = 0pt] (n11) at (11,7)
+{\scriptsize $(2,t_3)$};
+  \node[circle,fill=green1, minimum size=0.2cm,  inner sep = 0pt] (n12) at (6,5)
+{\scriptsize $(3,t_3)$};
+  \node[circle,draw=red1, minimum size=0.2cm,  inner sep = 0pt] (n14) at (8,10)
+{\scriptsize $(1,t_3)$};
+
+  \foreach \from/\to in {n10/n7, n1/n4, n11/n12}
+   \draw[every edge,->] (\from) -- (\to);
+     \draw[dotted,->](n7) to[out=80, in=40] (n11);
+  \draw[dotted,->](n10) to[out=10, in=180] (n1);
+   \draw[dotted,->](n4) to[out=-30,in=-150] (n12);
+    \end{tikzpicture}
+\end{center}
+\caption{A static graph corresponding to the evolving graph example of
+Figure~\ref{fig:eg_shortest_path}. The green nodes are active nodes while the
+red nodes are inactive nodes.
+The black lines are edges in the static edge set $\tilde E$ and are encoded
+algebraically in the diagonal blocks $A^{[t]}$ of the adjacency matrix $\bm M_3$.
+The dotted lines are edges in the causal edge set $E'$ and are encoded algebraically in
+the off-diagonal blocks $M^{[t_i, t_j]}$.
+The graph containing all the edges and temporal nodes has adjacency matrix $\bm M_3$.}
+\label{fig:static}
+\end{figure}
 
@@
 
-In this section we describe some illustrative
-
-\subsection{Synthetic Data}
-\label{sec:synthetic-data}
+In this section, we vary the edge
+weights in both static and causal edges to study the impact of time-preserving paths on evolving graph centrality.
+We also compare evolving graph centrality with the aggregated static graph case to gain insight about the advantage of evolving graph model.
 
@@
 
-A second network is
+(add results here.)
 
-author names, affiliation, journal, and year of publication.
+A second network is constructed by linking leading authors in different papers whose
+ideas are similar. The resulting network represent the connectivity of ideas in all the research papers in the database.
 
-We are interested in finding out how good evolving graph centrality algorithms
-comparing with static graph ones. 
-Also how the way to
-
-stability, reasonable solutions that can be applied in practice.
+(add results here.)
 
@@
 % \label{sec:aggr-graphs-evolv}
-
-Evolving graph model is
-
-We conduct the experiments on a list of papers with associated information, including author names, affiliation, journal, and year of publication
-
-Evaluating and comparing the performance of centrality algorithms is hard as there is no formal definition for the ``qualities'' of a person.
 

### 2017-11-04 paper.tex
various updates and fixes

@@
 
-A time-preserving path on evolving graphs makes implicit assumptions about the type of edges in which a path traverse. For example, some papers count only static edges,
-while some take account of both static edges and causal edges. In addition, the length of a time-preserving path can be either spatial or temporal.
+A time-preserving path on evolving graphs makes implicit assumptions about the type of edges that a path traverses.
+For example, the path can count only static edges or can take account of both static edges and causal edges.
+In addition, the length of a time-preserving path can be either spatial or temporal.
 
 We study the impact of different time-preserving paths on node centrality by varying the edge weights of static and causal edges.
-We also compare evolving graph centrality with the aggregated static graph case to gain insight about the advantage of evolving graph model.
+We also compare evolving graph centrality with the aggregated static graph case to gain insight about the advantage of an evolving graph model.
 We construct an evolving coauthor network from a collection of research papers for the experiments.
@@
 
-In the 1985 science-fiction film ``Back to the Future'', Marty McFly (played by Michael J. Fox) travelled back in time and accidentally changed the history.
+In the 1985 science-fiction film ``Back to the Future'', Marty McFly (played by Michael J. Fox) travelled back in time and accidentally changed history.
 However, we cannot travel back in time or even send a message to the past.
-An evolving graph in general is a time dependent graph $G(t) = (V(t), E(t))$.
+An evolving graph in general is a time-dependent graph $G(t) = (V(t), E(t))$.
 To traverse an evolving graph, one has to consider time.
@@
 % time-respecting path
-We represent an evolving graph as a time-ordered sequences of graphs, similar to the work of Tang and coworkers \cite{tang10, tang102, tang09, nicosia13} and Grindrod, Higham and coworkers \cite{grindrod11, grindrod13}.
+We represent an evolving graph as a time-ordered sequences of graphs, similar to the work of Tang and coworkers \cite{nicosia13, tang09, tang102, tang10} and Grindrod, Higham and coworkers \cite{grindrod13,grindrod11}.
 The idea is to divide the system's time span into temporal slices and regards it as a sequence of static graphs $G^{[t]}$, one for each layer.
@@
 $\langle (1, t_1), (2, t_1) \rangle$ is a static edge at time stamp $t_1$ and $\langle (3, t_2), (3, t_3) \rangle$ is a causal edge between time stamp $t_2$ and time stamp $t_3$.
-The difference between static edges and causal edges were introduced in \cite{chen16}.
+The difference between static edges and causal edges were first explicitly considered in \cite{chen16}.
 
@@
   \node[circle,fill=green1, minimum size=0.2cm] (n1) at (0,10) {1};
-
    \node[circle,fill=green1, minimum size=0.2cm] (n11) at (11,7) {2};
@@
   \node[circle,draw=red1, minimum size=0.2cm] (n14) at (8,10) {1};
-
+  \node (w1) at (-6, 9) {$w_1$};
+  \node (w2) at (3, 13) {$w_2$};
+  \node (w3) at (-2, 8) {$w_3$};
+  \node (w4) at (2, 4) {$w_4$};
+  \node (w5) at (8.5, 7) {$w_5$};s
   \foreach \from/\to in {n10/n7, n1/n4, n11/n12}
@@
 The green filled circles represent active nodes while the red circles represent
-inactive nodes. Directed edges in each time stamp are shown as black arrows and directed edges between graphs are shown as dotted arrows.}
+inactive nodes. Directed edges in each time stamp are shown as black arrows and directed edges between graphs are shown as dotted arrows, where $w_1, w_2 \ldots w_5$ are edge weights.}
 \label{fig:eg_shortest_path}
@@
 A time-preserving path on evolving graphs can be described by static edges, causal edges, or both.
-Grindrod et al.'s definition of dynamic walk \cite{grindrod11} only count static edges.
+Grindrod et al.'s definition of dynamic walk \cite{grindrod11} only counts static edges.
 Tang et al.
-\cite{tang10s} measures a temporal shortest path in time unites (or causal edges) only.
-If a node can reached by another node in $k$ time stamps then the distance between the two nodes is $k$.
+\cite{tang10s} measure a temporal shortest path in time unit (or causal edges) only.
+If a node can be reached by another node in $k$ time stamps then the distance between the two nodes is $k$.
 Chen and Zhang \cite{chen16} considered both static edges and causal edges in their definition of temporal path.
 
-The aim of this paper is as follows.
-First, to identity the type of time-preserving path in a list of common evolving graph centrality measures.
+The aims of this paper are as follows.
+First, to identify the type of time-preserving path in a list of common evolving graph centrality measures.
 Second, to vary static and causal edge weights and analyze the impact on selected measures of centrality.
 Third, to solve a real world problem using evolving graph centrality: identify key authors in an evolving coauthor network.
-We design the experiment using the Julia dynamic network analysis package
+We carry out the experiment using the Julia dynamic network analysis package
 EvolvingGraphs.jl (\url{https://github.com/EtymoIO/EvolvingGraphs.jl}).
@@
 
-A \textbf{walk} of length $r$ from node $i_1$ to node $j_{r+1}$ is a sequence of edges
+A \textbf{walk} of length $r$ from node $i_1$ to node $i_{r+1}$ is a sequence of edges
 $(i_1, i_2), (i_2, i_3), \ldots (i_r, i_{r+1})$.
@@
 We review the Katz centrality here.
-Let $A$ be the adjacency matrix of a graph $G=(V,E)$ and $\rho(A)$ be the spectral radius of $A$. Suppose $\alpha < 1/ \rho(A)$, then the Katz centrality vector of $G$ is
+Let $A$ be the adjacency matrix of a graph $G=(V,E)$ and $\rho(A)$ be the spectral radius of $A$. If $\alpha < 1/ \rho(A)$, then the Katz centrality vector of $G$ is
 \[
@@
 
-We now describe time-preserving paths in more details. We follow the definition of
+We now describe time-preserving paths in more detail. We follow the definition of
 \emph{evolving graph}, \emph{temporal node} and \emph{active node} in \cite{chen16}.
@@
 \begin{definition}
-A \textbf{time-preserving path}  of length $m$ on an evolving graph $G_n$ is a time-ordered sequence of active nodes, $\langle (v_1, t_1), (v_2, t_2), \ldots, (v_m, t_m) \rangle$, where $t_1 \le t_2 \le \cdots t_m$ and
+A \textbf{time-preserving path}  of length $m$ on an evolving graph $G_n$ is a time-ordered sequence of active nodes, $\langle (v_1, t_1), (v_2, t_2), \ldots, (v_m, t_m) \rangle$, where $t_1 \le t_2 \le \cdots \le t_m$ and
 $v_i = v_j$ if and only if $t_i \ne t_j$.
@@
 A time-preserving path can traverse both causal edges and static edges.
-We will see in the next section evolving centrality measures make implicit assumptions about the type of edges in the
+We will see in the next section that evolving centrality measures make implicit assumptions about the type of edges in the
 time-preserving path that is used.
@@
 
-We can not travel back in time. But reverse the direction of temporal flows can help
+We can not travel back in time. But reversing the direction of temporal flows can help
 identify the ``hub'' nodes or the source of the flows. The authority score of a page is
@@
 Indeed, reverse PageRank has
-been studied by \cite{fogaras03, bar08, gleich15}. In reverse PageRank we compute PageRank on the graph with reversed direction, i.e., reverse the direction of each edge $(i,j)$ to $(j, i)$.
-Fogaras \cite{fogaras03} shows that Reversed Page Rank sores express hub quality.
+been studied by \cite{bar08, fogaras03, gleich15}. In reverse PageRank we compute PageRank on the graph with reversed direction, i.e., reverse the direction of each edge $(i,j)$ to $(j, i)$.
+Fogaras \cite{fogaras03} shows that Reversed Page Rank scores express hub quality.
 
@@
 
-If we use this definition of temporal path for the temporal Katz centrality introduced by
+If we use this definition of temporal path for the temporal Katz centrality introduced in
 \cite{grindrod11}, we have a new centrality measure.
@@
 \]
-Note this can not be written in \eqref{eq:katz}, as discussed in Section \ref{sec:temp-katz-centr}.
+% Note this can not be written in \eqref{eq:katz}, as discussed in Section \ref{sec:temp-katz-centr}.
 
@@
 both static edges and causal edges are considered.
-We can represent an evolving graph with a block adjacency matrix.
-Centraliy on this block matrix gives the importance of each node at all time stamps.
+We can represent an evolving graph by a block adjacency matrix, as shown in Section \ref{sec:centr-block-adjac}.
+Centrality on this block matrix gives the importance of each node at all time stamps.
 We can average these rating at different time stamps to
@@
 
-In \cite{grindrod11}, Grindrod et al. defines a \emph{dynamic walk} of length $m$ from
+In \cite{grindrod11}, Grindrod et al. define a \emph{dynamic walk} of length $m$ from
 node $v_1$ to node $v_{w+1}$  as a sequence of edges
@@
 $t_{r_1} \leq t_{r_2} \leq \cdots \leq t_{r_w}$ such that the adjacency matrix at time stamp
-$r_m$, i.e., $A_{i_m, i_{m+1}}^{[r_m]} \ne 0$. Note in this definition, the authors only take account of the static edges and the length of a dynamic walk is determined by the number of static edges.
+$r_m$, i.e., $A_{i_m, i_{m+1}}^{[r_m]} \ne 0$.
+Note that in this definition the authors only take account of the static edges and the length of a dynamic walk is determined by the number of static edges.
 
@@
 
-One may want to take into account the length of time a node trains a message. The temporal betweenness centrality of the node $i$ at time stamp $t_m$ is defined as
+One may want to take into account the length of time a node passes a message. The temporal betweenness centrality of the node $i$ at time stamp $t_m$ is defined as
 \begin{equation}
@@
 \end{equation}
-where as before $\alpha_{j,k}$ represents the number of temporal shortest paths from $j$ to $k$ and $U_{j,k,t_m}(i)$ represents the number of temporal shortest paths from $j$ to $k$ in which node $i$ is traversed from
+where, as before, $\alpha_{j,k}$ represents the number of temporal shortest paths from $j$ to $k$ and $U_{j,k,t_m}(i)$ represents the number of temporal shortest paths from $j$ to $k$ in which node $i$ is traversed from
 the path in the time stamp $t_m$ or a previous time stamp $t_{m-1}$. Then
@@
 
-Let $d_{ij}$ is the length of temporal shortest path from $i$ and $j$ in an evolving graph. Then
+Let $d_{ij}$ be the length of a temporal shortest path from $i$ and $j$ in an evolving graph. Then
 the closeness centrality of a node $i$ is defined
@@
 $$
-Note depends on how we define the length of temporal shortest path, the closeness centrality can takes account of only static edges, only causal edges, or both.
+Note that this depends on how we define the length of temporal shortest path. The closeness centrality can takes account of only static edges, only causal edges, or both.
 
@@
 
-In \cite{chen16}, we derive a block adjacency matrix representation.
-Let $E'$ be the set of causal edges and $\hat E$ be the set of static edges then
+In \cite{chen16}, we derive a block adjacency matrix representation of an evolvign graph.
+If $E'$ is the set of causal edges and $\hat E$ is the set of static edges then
 an evolving graph can be represented as
@@
 
+(Need to justify the benefit of this approach.)
 We can apply static graph centrality algorithms to $M_n$ and then take the average of ratings at each each time stamp. For example, we can construct the Google matrix
@@
 We construct the evolving coauthor network from Etymo (\url{https://etymo.io}).
-We collected $1566$ publications published by Journal of Machine Learning Research (JMLR) papers from $2001$ to $2017$ with authors involved. We regard each year
+We collected $1566$ publications published by Journal of Machine Learning Research (JMLR) from $2001$ to $2017$ with authors involved. We regard each year
 as a time stamp and there are $17$ time stamps in total. At each time stamp, we
 create a undirected edge (or two directed edges) between two authors if they have coauthored at least one paper.
-
 (add results here.)

### 2018-03-19 paper.tex
add more contents

@@
 
-\section{Background}
-\label{sec:preliminaries}
-
-Let $G$ be a directed graph with $n$ nodes with the corresponding adjacency matrix
-$A \in \R$.
-
-A \textbf{walk} of length $r$ from node $i_1$ to node $i_{r+1}$ is a sequence of edges
-$(i_1, i_2), (i_2, i_3), \ldots (i_r, i_{r+1})$.
-
-\subsection{Graph Centrality}
-\label{sec:katz-centrality}
-
-% definition of various graph centrality algorithms
-We review the Katz centrality here.
-Let $A$ be the adjacency matrix of a graph $G=(V,E)$ and $\rho(A)$ be the spectral radius of $A$. If $\alpha < 1/ \rho(A)$, then the Katz centrality vector of $G$ is
-\[
-(I - \alpha A)^{-1}e.
-\]
-
-The \emph{betweenness centrality} of a node $i$ in a static graph is defined as
-$$
-C_i = \sum_{j \in V}\sum_{k \in V, k \ne j} \frac{\rho_{jk}(i)}{\rho_{jk}},
-$$
-where $\rho_{jk}$ is the number of shortest paths from node $j$ to node $k$, while $\rho_{jk}(i)$ is the number of shortest paths from node $j$ to node $k$ that pass through node $i$
+% \section{Background}
+% \label{sec:preliminaries}
+%
+% Let $G$ be a directed graph with $n$ nodes with the corresponding adjacency matrix
+% $A \in \R$.
+%
+% A \textbf{walk} of length $r$ from node $i_1$ to node $i_{r+1}$ is a sequence of edges
+% $(i_1, i_2), (i_2, i_3), \ldots (i_r, i_{r+1})$.
+%
+%
+% \subsection{Graph Centrality}
+% \label{sec:katz-centrality}
+%
+% % definition of various graph centrality algorithms
+% We review the Katz centrality here.
+% Let $A$ be the adjacency matrix of a graph $G=(V,E)$ and $\rho(A)$ be the spectral radius of $A$. If $\alpha < 1/ \rho(A)$, then the Katz centrality vector of $G$ is
+% \[
+% (I - \alpha A)^{-1}e.
+% \]
+%
+% The \emph{betweenness centrality} of a node $i$ in a static graph is defined as
+% $$
+% C_i = \sum_{j \in V}\sum_{k \in V, k \ne j} \frac{\rho_{jk}(i)}{\rho_{jk}},
+% $$
+% where $\rho_{jk}$ is the number of shortest paths from node $j$ to node $k$, while $\rho_{jk}(i)$ is the number of shortest paths from node $j$ to node $k$ that pass through node $i$
 
@@
 
+The Katz Centrality is a measure of importance
+
 In \cite{grindrod11}, Grindrod et al. define a \emph{dynamic walk} of length $m$ from
@@
 
-% \subsubsection{Aggregated Graphs and Evolving Graphs}
-% \label{sec:aggr-graphs-evolv}
+\subsection{Paper Subject Tag Network}
+
+We tag our research articles by subjects. The subjects re provided by ACM Computing Classification System (also contains the superclass and subclass).
+
+We can construct a time-dependent tag network by link tags in each articles. For example,
+suppose a paper $p_1$ has three tags $t_1$, $t_2$, and $t_3$, where $t_1$ is a superclass of $t_2$ and $t_3$.
+We link $t_2$ and $t_3$ in both direction and create a link from $t_1$ to $t_2$ and a link from $t_1$ to $t_3$.
+The time stamp of these edges is the published date of the paper.
 

### 2018-03-19 simulations/katz.jl

@@ -1,0 +1,23 @@
+# testing evolving graph katz centrality on author network data
+using EvolvingGraphs
+import EzXML
+
+jmlr_dict = Dict()
+
+# load graph data at each year
+# form evolving graph
+eg= evolving_graph(String, Int)
+for year in range(2001, 17)
+    g = load_graphml("jmlr_$(year).graphml")
+    add_graph!(eg, g, year)
+end
+
+rating = katz_centrality(eg)
+
+sorted_authors = sort(rating, by = x -> x[2], rev = true)
+
+println("Top 10 rating authors")
+println(sorted_authors[1:10])
+
+println("Button 10 rating authors")
+println(sorted_authors[end-10:end])

### 2018-04-11 paper.tex
make the idea clear

@@
 
-\title{A Closer Look at Time-Preserving Paths on Evolving Graphs}
+\title{A Closer Look at Time-Preserving Walks on Evolving Graphs}
 
@@
 \begin{abstract}
-This paper studies evolving graph centrality from the perspective of time-preserving paths.
-We describe time-preserving paths based on two dimensions of variation, namely static edges and causal edges.
+This paper studies evolving graph centrality from the perspective of time-preserving walks.
+We describe time-preserving walks based on two dimensions of variation, namely static edges and causal edges.
 
-A time-preserving path on evolving graphs makes implicit assumptions about the type of edges that a path traverses.
-For example, the path can count only static edges or can take account of both static edges and causal edges.
-In addition, the length of a time-preserving path can be either spatial or temporal.
+A time-preserving walk on evolving graphs makes implicit assumptions about the type of edges that a walk traverses.
+For example, the walk can count only static edges or can take account of both static edges and causal edges.
+In addition, the length of a time-preserving walk can be either spatial or temporal.
 
-We study the impact of different time-preserving paths on node centrality by varying the edge weights of static and causal edges.
+We study the impact of different time-preserving walks on node centrality by varying the edge weights of static and causal edges.
 We also compare evolving graph centrality with the aggregated static graph case to gain insight about the advantage of an evolving graph model.
@@
 However, we cannot travel back in time or even send a message to the past.
-An evolving graph in general is a time-dependent graph $G(t) = (V(t), E(t))$.
-To traverse an evolving graph, one has to consider time.
-In particular, a path on an evolving graph needs to be time-preserving, meaning a node can not pass a massage (through an edge) to a node at a earlier time.
+To traverse an evolving graph, a.k.a a time-dependent graph, one has to consider time.
+In particular, a walk on an evolving graph needs to be time-preserving, meaning a node can not pass a massage (through an edge) to a node at a earlier time.
 
-% time-respecting path
+% time-respecting walk
 We represent an evolving graph as a time-ordered sequences of graphs, similar to the work of Tang and coworkers \cite{nicosia13, tang09, tang102, tang10} and Grindrod, Higham and coworkers \cite{grindrod13,grindrod11}.
 The idea is to divide the system's time span into temporal slices and regards it as a sequence of static graphs $G^{[t]}$, one for each layer.
-A node on a slice $G^{[t]}$ is represented by a pair $(v, t)$, where $v$ is a node of
-$G^{[t]}$ and $t$ is the time stamp of the slice.
-A time-respecting path of length $n$ is a sequence of these node pairs $\langle (v_1, t_1), (v_2, t_2), \ldots ,(v_m, t_m)\rangle$, where $t_1 \le t_2 \le \cdots \le t_n$.
-Note if $t_i = t_j$, then $\langle (v_i, t_i), (v_j, t_j) \rangle$ is an edge at a temporal slice,  otherwise it is an edge linking nodes from different temporal slices.
-We call edges of the first kind \emph{static edges} and of the second kind
-\emph{causal edges}.
-For example, in Figure \ref{fig:eg_shortest_path}
+Such representation arises naturally in many real-world applications.
+For example,
+consider networks of users interacting through messaging.
+Each interaction between two users $A$ and $B$ are stored with a time stamp $t$.
+If we represent a user as a node then a user $A$ at time stamp $t$ is represented by a pair $(v,t)$ and a message sent from user $A$ to user $B$ at time stamp $t$ can be represented as $\langle (A, t) (B, t) \rangle$.
+
+In general, a node $v$ on $G^{[t]}$ is represented by a pair $(v, t)$, where $t$ is the time stamp of the temporal slice.
+A sequence of interactions between users form a walk. Suppose $A$ sent a message to $B$ at time stamp $t_1$
+and then $B$ sent this message to $C$ at time stamp $t_2$.
+We can represent this activity as $\langle (A,t_1), (B,t_1), (B, t_2), (C,t_2)\rangle$, where each pair of two nodes has meanings: $\langle (A,t_1), (B,t_1) \rangle$ and $\langle (B,t_2), (C,t_2) \rangle$ represent interactions between users $A$, $B$, and $C$ and $\langle (B,t_1), (B,t_2) \rangle$ represents the fact that user $B$ holds the message at time stamp $t_1$ and $t_2$.
+
+A time-respecting walk is a sequence of $\langle (v_1, t_1), (v_2, t_2), \ldots ,(v_m, t_m)\rangle$, where $t_1 \le t_2 \le \cdots \le t_n$ are the corresponding time stamps.
+If $t_i = t_j$, then $\langle (v_i, t_i), (v_j, t_j) \rangle$ is an edge where both nodes are on the same temporal slice,  otherwise it is an edge linking nodes from different temporal slices.
+We call edges of the first kind \emph{static edges} and of the second kind \emph{causal edges}.
+Recall in static graph, a walk of length $m$ is defined as a sequence of nodes $v_1, v_2, \ldots, v_{m+1}$ such that for each $i = 1, \ldots, m$ there is an edge from $v_i$ to $v_{i+1}$.
+How to determine the length of a time-respecting walk?
+One could define the length of a time-respecting walk as the total number of temporal slices (see shortest temporal distance in \cite{tang09}) or the number of static edges (see dynamic walk in \cite{grindrod11}).
+This paper studies the impact of these two different definitions.
+In particular, we studies a general definition of temporal distance that takes account of both temporal slices and static edges.
+
+% Related works
+Researchers have generalised many static graph centrality algorithms for evolving graphs.
+One approach is to use the fact that the elements of the matrix product of adjacency matrices at different time stamps can correctly count the number of temporal walks.
+However, not every centrality algorithm can be generalised in this way.
+Another approach is to define evolving graph centrality algorithms using time-respecting walks.
+This approach is applicable to algorithms that are defined using paths or walks.
+
+% no work on pagerank so far. By understanding temporal walk, we could provide a generalization of pagerank on evolving graphs.
+
+In Higham's following up papers, time delay is considered as alternative format of Katz centrality.
+But the impact of temporal is left unconsidered.
+We studied the problem on centrality from two different types of centrality: one that depends on matrix unfolding and one that depends on temporal walk.
+
+% our contribution this paper
+Inspired by work
+Borgatti noted in \cite{borgatti05} that the manner of traffic flow entails a new way to think about centrality.
+where the author simulate different traffic flows to study centrality.
+
+In particularly, the importance of a node in a network can not be determined without reference to how traffic flows through the network.
+To develop a centrality algorithm on evolving graphs, one has to consider the manner of temporal traffic flow.
+A time-preserving walk on evolving graphs can be described by static edges, causal edges, or both.
+
+% Grindrod et al.'s definition of dynamic walk \cite{grindrod11} only counts static edges.
+% Tang et al. \cite{tang10s} measure a temporal shortest walk in time unit (or causal edges) only.
+% If a node can be reached by another node in $k$ time stamps then the distance between the two nodes is $k$.
+Chen and Zhang \cite{chen16} considered both static edges and causal edges in their definition of temporal walk.
+
+The aims of this paper are as follows.
+First, to identify the type of time-preserving walk in a list of common evolving graph centrality measures.
+Second, to vary static and causal edge weights and analyze the impact on selected measures of centrality.
+Third, to solve a real world problem using evolving graph centrality: identify key authors in an evolving coauthor network.
+We carry out the experiment using the Julia dynamic network analysis package
+EvolvingGraphs.jl (\url{https://github.com/EtymoIO/EvolvingGraphs.jl}).
+We use the research paper data gathered from Etymo (\url{https://etymo.io}), a visual search engine for data scientists.
+
+\section{Time-Preserving walks}
+\label{sec:time-pres-walks}
+
+For example, in Figure \ref{fig:eg_shortest_walk}
 $\langle (1, t_1), (2, t_1) \rangle$ is a static edge at time stamp $t_1$ and $\langle (3, t_2), (3, t_3) \rangle$ is a causal edge between time stamp $t_2$ and time stamp $t_3$.
@@
 inactive nodes. Directed edges in each time stamp are shown as black arrows and directed edges between graphs are shown as dotted arrows, where $w_1, w_2 \ldots w_5$ are edge weights.}
-\label{fig:eg_shortest_path}
+\label{fig:eg_shortest_walk}
 \end{figure}
 
-It is natural to define the length of a path on a static graph as the number of nodes travelled through the path.
-For the weighted graph case, the length of a path is the total weight of all the edges in the path.
+It is natural to define the length of a walk on a static graph as the number of nodes travelled through the walk.
+For the weighted graph case, the length of a walk is the total weight of all the edges in the walk.
 We observe that static edges link nodes in space while causal edges link nodes in time.
 Hence we would like to distinguish temporal distance from spatial distance on an evolving graph: the length of a static edge is equal to the edge weight (or $1$ in the unweighted graph case); the length of a causal edge is the time distance between the two nodes.
-In the simplest case, the time-respecting path
-$\langle (1, t_1) ,(2, t_1) , (2, t_3), (3, t_3)\rangle$ in Figure \ref{fig:eg_shortest_path} has length $4$ in total because two static edges $\langle (1, t_1) (2, t_1) \rangle$ and $\langle (2, t_3), (3, t_3) \rangle$ have length one, whereas $\langle (2, t_1) (2, t_3) \rangle$ traverse $2$ time stamps so has length $2$.
+In the simplest case, the time-respecting walk
+$\langle (1, t_1) ,(2, t_1) , (2, t_3), (3, t_3)\rangle$ in Figure \ref{fig:eg_shortest_walk} has length $4$ in total because two static edges $\langle (1, t_1) (2, t_1) \rangle$ and $\langle (2, t_3), (3, t_3) \rangle$ have length one, whereas $\langle (2, t_1) (2, t_3) \rangle$ traverse $2$ time stamps so has length $2$.
 
-% We studies evolving graph centrality from the perspective of temporal network flows.
-% Researchers have identified the time-preserving nature of such network flows, i.e.,
-% we cannot travel between nodes from a later time to an early time.
-% However, a closer look tells us there are subtle differences
-% in previous papers
-
-% How about a reverse time-preserving network flow?
-
-% our contribution this paper
-Borgatti noted in \cite{borgatti05} that the manner of traffic flow entails a new way to think about centrality.
-In particularly, the importance of a node in a network can not be determined without reference to how traffic flows through the network.
-To develop a centrality algorithm on evolving graphs, one has to consider the manner of temporal traffic flow.
-A time-preserving path on evolving graphs can be described by static edges, causal edges, or both.
-Grindrod et al.'s definition of dynamic walk \cite{grindrod11} only counts static edges.
-Tang et al.
-\cite{tang10s} measure a temporal shortest path in time unit (or causal edges) only.
-If a node can be reached by another node in $k$ time stamps then the distance between the two nodes is $k$.
-Chen and Zhang \cite{chen16} considered both static edges and causal edges in their definition of temporal path.
-
-The aims of this paper are as follows.
-First, to identify the type of time-preserving path in a list of common evolving graph centrality measures.
-Second, to vary static and causal edge weights and analyze the impact on selected measures of centrality.
-Third, to solve a real world problem using evolving graph centrality: identify key authors in an evolving coauthor network.
-We carry out the experiment using the Julia dynamic network analysis package
-EvolvingGraphs.jl (\url{https://github.com/EtymoIO/EvolvingGraphs.jl}).
-We use the research paper data gathered from Etymo (\url{https://etymo.io}), a visual search engine for data scientists.
-
-% \section{Background}
-% \label{sec:preliminaries}
-%
-% Let $G$ be a directed graph with $n$ nodes with the corresponding adjacency matrix
-% $A \in \R$.
-%
-% A \textbf{walk} of length $r$ from node $i_1$ to node $i_{r+1}$ is a sequence of edges
-% $(i_1, i_2), (i_2, i_3), \ldots (i_r, i_{r+1})$.
-%
-%
-% \subsection{Graph Centrality}
-% \label{sec:katz-centrality}
-%
-% % definition of various graph centrality algorithms
-% We review the Katz centrality here.
-% Let $A$ be the adjacency matrix of a graph $G=(V,E)$ and $\rho(A)$ be the spectral radius of $A$. If $\alpha < 1/ \rho(A)$, then the Katz centrality vector of $G$ is
-% \[
-% (I - \alpha A)^{-1}e.
-% \]
-%
-% The \emph{betweenness centrality} of a node $i$ in a static graph is defined as
-% $$
-% C_i = \sum_{j \in V}\sum_{k \in V, k \ne j} \frac{\rho_{jk}(i)}{\rho_{jk}},
-% $$
-% where $\rho_{jk}$ is the number of shortest paths from node $j$ to node $k$, while $\rho_{jk}(i)$ is the number of shortest paths from node $j$ to node $k$ that pass through node $i$
-
-% The \emph{communicability betweenness centraltiy} \cite{estrada09} for a node $i$ is defined as
-% $$
-% C_i = C_N\sum_p \sum_q \frac{\exp(A)_{p,q} - \exp(A - E(i))_{p,q}}{\exp(A)_{p,q}},
-% $$
-% where $C_N = \frac{1}{(N-1)^2 - (N-1)}$ is a normalizing factor and $E(i)$
-% has nonzeros only in row and column $i$, and in such row and column has $-1$ wherever $A$ has $1$. Similarly, the \emph{resolvent betweenness centrality} for node $i$ is defined as
-% $$
-% C_i = C_N\sum_p \sum_q \frac{(I - \alpha A)^{-1}_{p,q} - (I - \alpha(A - E(i)))^{-1}_{p,q}}{(I - \alpha A)^{-1}_{p,q}}.
-% $$
-% \subsection{Eigenvector Centrality}
-% \label{sec:eigenv-centr}
-
-% Given an adjacency matrix $A$ of a graph $G$, eigenvector centrality is defined as the dominant eigenvector of $A$, i.e.,
-% \[
-% \lambda v = Av,
-% \]
-% where $\lambda$ is the dominate eigenvalue of $A$ and $v$ is the corresponding eigenvector.
-Variations of eigenvector centrality includes Katz centrality \cite{katz53}, PageRank \cite{page99}, Hubbell's clique identification \cite{hubbell65}, Friedkin's actors' network centrality \cite{friedkin91}.
-% In general, all eigenvector-like centrality are influence measures, meaning that even if a node $a$ only influences one node $b$, who influences many other nodes, then $a$ is highly influential.
-
-% Let $A$ be the adjacency matrix of a graph $G = (V,E)$, i.e., $A_{i,j} = 1$ if node $i$ is linked to node $j$ and $A_{i,j} = 0$ otherwise. The idea of eigenvector centrality is that
-% each node's centrality is the sum of the centrality values of the nodes that it is connected to. In other words, the relative centrality of node $v$ can be defined as
-% \[
-% x_v = \frac{1}{\lambda}\sum_{t \in M(v)} x_t = \frac{1}{\lambda}\sum_{t \in G} A_{v, t}x_t,
-% \]
-% where $M(v)$ is the set of neighbor nodes of $v$. We can write it in matrix notation as
-% \[
-% \lambda x = Ax.
-% \]
-% The eigenvector centrality of $G$ is the dominant (or principle) eigenvector of $A$.
-% One may ask why we choose dominant eigenvector not any other eigenvectors? The answer comes from Perron-Frobenius Theorem (more details later).
-
-% In \cite{bonacich91}, Bonacich prove the following theorem.
-% \begin{theorem}
-%   Assume that a symmetric non-negative matrix $A$ has a single largest eigenvalue $\lambda_1$ and its corresponding eigenvector $v_1$.
-Let $e$ be a column vector of ones.
-The infinite sum $A + \beta A^2 + \beta^2 A^3 + \beta^3 A^4 + \cdots$ converges
-% if $|\beta| < 1/ \lambda_1$. Moreover, as $\beta$ approaches $1/\lambda_1$ from below,
-% $(1-\beta\alpha_1)(A+ \beta A^2 + \beta^2 A^3 + \beta^3 A^4 + \cdots)e$ approaches $v_1$.
-% \end{theorem}
-% In other words, the eigenvector centrality of $G$ can be thought as proportional to an
-% infinite sum
-% \begin{equation}
-% \label{eq:s}
-% Se = Ae+ \beta A^2e + \beta^2 A^3e + \beta^3 A^4e + \cdots.
-% \end{equation}
-% Note however if $\beta = 1/\lambda_1$, the series does not converge.
-% Eq. \eqref{eq:s} offers great flexibility to think about related centrality measures.
-% For example, in the PageRank case
-% \[
-% r = Gr,
-% \]
-% where $G$ is a stochastic matrix. Then
-% \[
-% Se = Ge + \beta G^2e + \beta^2 G^3e + \beta^3 G^4 e + \cdots
-% \]
-% converges to $r$ as $\beta$ approaches $1$ from below.
-
-% Note when $\alpha < 1/\rho(A)$, the spectral radius of $A$,
-% \[
-% (I - \alpha A)^{-1} = I + \alpha A + \alpha^2 A^2 + \alpha^3 A^3 + \cdots.
-% \]
-% Hence from eq. \eqref{eq:s} we have
-% \[
-% \beta Se + 1 = (I - \beta A)^{-1}e.
-% \]
-% This means eigenvector centrality can interpreted as Katz centrality with special chosen parameter value $\beta$.
-We mention that Aprahamian et.
-al.
-\cite{ahh16} consider selecting the Katz parameter based on the objective of matching the centrality of the exponential counterpart.
-
-% \textbf{WZ:} some analysis need to be done on the relationship between
-% $\beta$ and $v_1$. Derive some upper or lower bounds.
-
-% %katz case
-% Suppose we let
-% \[
-% S = A + \alpha_1^{-1} A^2 + \alpha_1^{-2} A^3 + \cdots,
-% \]
-% then $u = Se$ is proportional to the eigenvector $v_1$.
-
-% In PageRank's case
-% \[
-% r = Gr,
-% \]
-% which means $\alpha_1 = 1$.
-
-% Since Katz centrality can be written as
-% \[
-% (1- \alpha A)
-% \]
-% so it can be regard as a special case of eigenvector centrality.
-
-% % \subsection{The Datasets}
-% % \label{sec:datasets}
-
-% % The data is a list of papers with associated information, including author names, affiliation, journal, and year of publication, and the full text content.
-We will test our algorithms on a collection of articles from, NIPS, an
-% d ICLR.
-
-% \subsection{Author Name Disambiguation}
-% \label{sec:auth-name-disamb}
-
-% We follow the idea from \cite{martin13} to disambiguate author names.
-
-% \section{Eigenvector Centrality on Evolving Graphs}
-% \label{sec:centr-algor}
-
-% Let $A^{[t]}$ be the corresponding graph $G^{[t]}$ at a time label $t$. In \cite{grindrod11},
-% Grindrod et. al. observes that the matrix product $A^{[t_1]}A^{[t_2]}\cdots A^{[t_w]}$ has
-% $(i,j)$ element that counts the number of dynamic walks of length $w$ from node $i$ to node $j$ on which the $m$-th step of the walk takes place at time $t_m$.
-Therefore, the Katz centrality for evolving graphs can be written as
-% \[
-% Q = (I - \alpha A^{[0]})^{-1}(I - \alpha A^{[1]})^{-1} \cdots (I - \alpha A^{[m]})^{-1}.
-% \]
-
-% Follow the discussion from Section \ref{sec:eigenv-centr}, we can generalize eigenvector centrality and PageRank on evolving graphs.
-
-\section{Time-Preserving Paths}
-\label{sec:time-pres-paths}
-
-We now describe time-preserving paths in more detail. We follow the definition of
+We now describe time-preserving walks in more detail. We follow the definition of
 \emph{evolving graph}, \emph{temporal node} and \emph{active node} in \cite{chen16}.
@@
 Note the node sets $V^{[t]}$ can change over time, i.e., nodes may appear or disappear at a particular time stamp.
-For example, in Figure \ref{fig:eg_shortest_path}, at time stamp $t_1$, $V^{[1]} = \langle 1, 2 \rangle$ and $E^{[1]} = \langle (1,2) \rangle$.
+For example, in Figure \ref{fig:eg_shortest_walk}, at time stamp $t_1$, $V^{[1]} = \langle 1, 2 \rangle$ and $E^{[1]} = \langle (1,2) \rangle$.
 Each graph $G^{[t]}$ can be represented by its adjacency matrix $A^{[t]}$.
@@
 
-In Figure \ref{fig:eg_shortest_path}, the filled green circles are active nodes. For the adjacency matrix representation, a node $i$ is active at time stamp $t$, then
+In Figure \ref{fig:eg_shortest_walk}, the filled green circles are active nodes. For the adjacency matrix representation, a node $i$ is active at time stamp $t$, then
 the $i$th row or the $i$th column of $A^{[t]}$ has at least one none-zero entry.
- In general, a time-preserving path can be defined as follows.
+ In general, a time-preserving walk can be defined as follows.
 
 \begin{definition}
-A \textbf{time-preserving path}  of length $m$ on an evolving graph $G_n$ is a time-ordered sequence of active nodes, $\langle (v_1, t_1), (v_2, t_2), \ldots, (v_m, t_m) \rangle$, where $t_1 \le t_2 \le \cdots \le t_m$ and
+A \textbf{time-preserving walk}  of length $m$ on an evolving graph $G_n$ is a time-ordered sequence of active nodes, $\langle (v_1, t_1), (v_2, t_2), \ldots, (v_m, t_m) \rangle$, where $t_1 \le t_2 \le \cdots \le t_m$ and
 $v_i = v_j$ if and only if $t_i \ne t_j$.
@@
 temporal distance of $v$ at different time stamps.
-In Figure \ref{fig:eg_shortest_path}, the black arrows represent static edges and the dotted arrows represent causal edges.
+In Figure \ref{fig:eg_shortest_walk}, the black arrows represent static edges and the dotted arrows represent causal edges.
 Suppose we assign all the static edge weight to be $1$ and
-assign the causal edge to be the number of time stamps between the pair. Then in Figure \ref{fig:eg_shortest_path}
+assign the causal edge to be the number of time stamps between the pair. Then in Figure \ref{fig:eg_shortest_walk}
 the edge weight between $(1, t_1)$ and $(2, t_1)$ is $1$ and the edge weight between $(2, t_1)$ and $(2, t_3)$
@@
 
-A time-preserving path can traverse both causal edges and static edges.
+A time-preserving walk can traverse both causal edges and static edges.
 We will see in the next section that evolving centrality measures make implicit assumptions about the type of edges in the
-time-preserving path that is used.
+time-preserving walk that is used.
 
-\subsection{Reverse Temporal Flows}
-\label{sec:reverse-temp-flows}
-
-We can not travel back in time. But reversing the direction of temporal flows can help
-identify the ``hub'' nodes or the source of the flows. The authority score of a page is
-proportional to its importance, and the hub score describes the quality of a page as a link collection of important related pages \cite{kleinberg99}.
-Indeed, reverse PageRank has
-been studied by \cite{bar08, fogaras03, gleich15}. In reverse PageRank we compute PageRank on the graph with reversed direction, i.e., reverse the direction of each edge $(i,j)$ to $(j, i)$.
-Fogaras \cite{fogaras03} shows that Reversed Page Rank scores express hub quality.
-
-Recall a time-preserving path is a time-ordered sequence of active nodes. Here we define a \emph{reversed temporal path} to be a reversed time-ordered sequence of active nodes, i.e.,
-$t_1 \ge t_2 \ge \cdots \ge t_m$.
-
-\section{Relation to Centrality Measures}
+\section{Centrality Measures}
 \label{sec:topol-temp-flow}
 
-In \cite{tang10s}, a temporal shortest path is measured in time units only, i.e., if node
+In \cite{tang10s}, a temporal shortest walk is measured in time units only, i.e., if node
 $v_i$ can reach node $v_j$ in $k$ time steps then the distance between node
 $v_i$ and $v_j$ is $k$. We can apply temporal breadth first
-search (BFS) \cite{chen16} to discover the temporal paths and then only take account of the temporal difference between the first node $(v_1, t_1)$ and the last node $(v_n, t_n)$, i.e., $t_n - t_1$.
+search (BFS) \cite{chen16} to discover the temporal walks and then only take account of the temporal difference between the first node $(v_1, t_1)$ and the last node $(v_n, t_n)$, i.e., $t_n - t_1$.
 
-If we use this definition of temporal path for the temporal Katz centrality introduced in
+If we use this definition of temporal walk for the temporal Katz centrality introduced in
 \cite{grindrod11}, we have a new centrality measure.
-In the matrix form, the nonzero entries of $A^{[t_i]} A^{[t_{i+1}]}$ counts all the temporal paths of length $1$, and
-$A^{[t_i]}\cdots A^{[t_j]}$, where $i < j$ counts all the temporal paths of length $j -i$.
+In the matrix form, the nonzero entries of $A^{[t_i]} A^{[t_{i+1}]}$ counts all the temporal walks of length $1$, and
+$A^{[t_i]}\cdots A^{[t_j]}$, where $i < j$ counts all the temporal walks of length $j -i$.
 For example, $A^{[1]}A^{[4]}$, $A^{[1]}A^{[1]}A^{[4]}$ and $A^{[1]}A^{[2]}A^{[3]}A^{[4]}$ are all walks of length 3.
@@
 
-Another definition of temporal path was introduced by \cite{chen16}. Here
+Another definition of temporal walk was introduced by \cite{chen16}. Here
 both static edges and causal edges are considered.
@@
 (Design a simple example and discuss it in each case below.)
-\subsection{Temporal Katz Centrality}
+
+\subsection{Temporal Katz Centrality and Communicability Betweenness Centrality}
 \label{sec:temp-katz-centr}
@@
 
-\subsection{Temporal Betweenness Centrality}
+\subsection{Temporal Betweenness and Closeness Centrality}
 \label{sec:temp-betw-centr}
 
-Recall that betweenness centrality of a node in a static graph is defined by counting the fraction of shortest paths that traverse it.
+Recall that betweenness centrality of a node in a static graph is defined by counting the fraction of shortest walks that traverse it.
 We could extend
-betweenness centrality on evolving graphs by replacing shortest paths with temporal shortest paths \cite{nicosia13}.
+betweenness centrality on evolving graphs by replacing shortest walks with temporal shortest walks \cite{nicosia13}.
 \begin{equation}
@@
 \end{equation}
-where $\alpha_{jk}$ represents the number of temporal shortest paths from node $j$ to node $k$ and $\alpha_{jk}(i)$ represents the number of temporal shortest paths from node $j$ to node $k$ that pass through the node $i$.
+where $\alpha_{jk}$ represents the number of temporal shortest walks from node $j$ to node $k$ and $\alpha_{jk}(i)$ represents the number of temporal shortest walks from node $j$ to node $k$ that pass through the node $i$.
 
@@
 \end{equation}
-where, as before, $\alpha_{j,k}$ represents the number of temporal shortest paths from $j$ to $k$ and $U_{j,k,t_m}(i)$ represents the number of temporal shortest paths from $j$ to $k$ in which node $i$ is traversed from
-the path in the time stamp $t_m$ or a previous time stamp $t_{m-1}$. Then
+where, as before, $\alpha_{j,k}$ represents the number of temporal shortest walks from $j$ to $k$ and $U_{j,k,t_m}(i)$ represents the number of temporal shortest walks from $j$ to $k$ in which node $i$ is traversed from
+the walk in the time stamp $t_m$ or a previous time stamp $t_{m-1}$. Then
 average temporal betweenness of node $i$ is then defined as
@@
 
-\subsection{Temporal Closeness Centrality}
-\label{sec:temp-clos-centr}
-
-Let $d_{ij}$ be the length of a temporal shortest path from $i$ and $j$ in an evolving graph. Then
+% closeness centrality
+Similar to betweenness centrality, let $d_{ij}$ be the length of a temporal shortest walk from $i$ and $j$ in an evolving graph. Then
 the closeness centrality of a node $i$ is defined
@@
 $$
-Note that this depends on how we define the length of temporal shortest path. The closeness centrality can takes account of only static edges, only causal edges, or both.
+Note that this depends on how we define the length of temporal shortest walk. The closeness centrality can takes account of only static edges, only causal edges, or both.
 
-\subsection{Centrality on a Block Adjacency Matrix}
+\subsection{Mapping from Evolving Graphs to Static Graphs}
 \label{sec:centr-block-adjac}
@@
 
-For Figue \ref{fig:eg_shortest_path}, we have
+For Figue \ref{fig:eg_shortest_walk}, we have
 
@@
 
-The static graph representation of Figure \ref{fig:eg_shortest_path} is shown in Figure \ref{fig:static}.
+The static graph representation of Figure \ref{fig:eg_shortest_walk} is shown in Figure \ref{fig:static}.
 
@@
 \caption{A static graph corresponding to the evolving graph example of
-Figure~\ref{fig:eg_shortest_path}. The green nodes are active nodes while the
+Figure~\ref{fig:eg_shortest_walk}. The green nodes are active nodes while the
 red nodes are inactive nodes.
@@
 
+\subsection{Reverse Temporal Flows}
+\label{sec:reverse-temp-flows}
+
+We can not travel back in time. But reversing the direction of temporal flows can help
+identify the ``hub'' nodes or the source of the flows. The authority score of a page is
+proportional to its importance, and the hub score describes the quality of a page as a link collection of important related pages \cite{kleinberg99}.
+Indeed, reverse PageRank has
+been studied by \cite{bar08, fogaras03, gleich15}. In reverse PageRank we compute PageRank on the graph with reversed direction, i.e., reverse the direction of each edge $(i,j)$ to $(j, i)$.
+Fogaras \cite{fogaras03} shows that Reversed Page Rank scores express hub quality.
+
+Recall a time-preserving walk is a time-ordered sequence of active nodes. Here we define a \emph{reversed temporal walk} to be a reversed time-ordered sequence of active nodes, i.e.,
+$t_1 \ge t_2 \ge \cdots \ge t_m$.
+
+\subsection{Temporal PageRank}
+
+We consider two generalisation of pagerank: a block matrix one and a dense matrix one that is based on probability
+
 \section{Experiments}
@@
 In this section, we vary the edge
-weights in both static and causal edges to study the impact of time-preserving paths on evolving graph centrality.
+weights in both static and causal edges to study the impact of time-preserving walks on evolving graph centrality.
 We also compare evolving graph centrality with the aggregated static graph case to gain insight about the advantage of evolving graph model.
@@
 
-\subsection{Paper Subject Tag Network}
+\subsection{Paper Keyword Tag Network}
 
-We tag our research articles by subjects. The subjects re provided by ACM Computing Classification System (also contains the superclass and subclass).
+We tag our research articles by subjects.
 
@@
 The time stamp of these edges is the published date of the paper.
-
-% subsection{Simulations}
-% \label{sec:simulations-1}
-
-% In \cite{borgatti05}, Borgatti simulate different types of walk flow on the network and
-% compare the node statistics with the centrality measures.
-
-% For katz centrality, eigenvector centrality, and PageRank (all on evolving graphs), we test all 3 different types of temporal flows.
-
-% Problem setup: given a group of authors in an evolving graph, finding the most important authors. We use real dataset with real names.
-
-% Build the evolving graph with author name disambiguation and apply the above algorithms.
-
-% \subsection{Katz Centrality}
-% \label{sec:katz-centrality-1}
-
-% \subsection{Eigenvector Centrality}
-% \label{sec:eigenv-centr-1}
-
-% \subsection{PageRank}
-% \label{sec:pagerank}
 

### 2018-05-08 paper.tex
add motivation example part

@@
 \usepackage{lipsum}
+
+\usepackage{listings}
+
+%%
+%% Julia definition (c) 2014 Jubobs
+%%
+\lstdefinelanguage{Julia}%
+  {morekeywords={abstract,break,case,catch,const,continue,do,else,elseif,%
+      end,export,false,for,function,immutable,import,importall,if,in,%
+      macro,module,otherwise,quote,return,switch,true,try,type,typealias,%
+      using,while},%
+   sensitive=true,%
+   alsoother={\$},%
+   morecomment=[l]\#,%
+   morecomment=[n]{\#=}{=\#},%
+   morestring=[s]{"}{"},%
+   morestring=[m]{'}{'},%
+}[keywords,comments,strings]%
+
+\lstset{%
+    language         = Julia,
+    basicstyle       = \ttfamily,
+    keywordstyle     = \bfseries\color{blue},
+    stringstyle      = \color{magenta},
+    commentstyle     = \color{ForestGreen},
+    showstringspaces = false,
+}
+
 \usepackage[linesnumbered]{algorithm2e}
@@
 
-\title{A Closer Look at Time-Preserving Walks on Evolving Graphs}
+\title{A Closer Look at Time-Preserving paths on Evolving Graphs}
 
-\author{Jiahao Chen and
+\author{Jiahao Chen \thanks{
+Capital One,
+New York, USA.
+\texttt{cjiahao@gmail.com}
+}
+ and
 Weijian Zhang
@@
 \begin{abstract}
-This paper studies evolving graph centrality from the perspective of time-preserving walks.
-We describe time-preserving walks based on two dimensions of variation, namely static edges and causal edges.
+This paper studies evolving graph centrality from the perspective of time-preserving paths.
+We describe time-preserving paths based on two dimensions of variation, namely static edges and causal edges.
 
@@
 
-We study the impact of different time-preserving walks on node centrality by varying the edge weights of static and causal edges.
+We study the impact of different time-preserving paths on node centrality by varying the edge weights of static and causal edges.
 We also compare evolving graph centrality with the aggregated static graph case to gain insight about the advantage of an evolving graph model.
@@
 However, we cannot travel back in time or even send a message to the past.
-To traverse an evolving graph, a.k.a a time-dependent graph, one has to consider time.
+To traverse an evolving graph, a.k.a a time-dependent graph, one has to consider order of time stamps.
 In particular, a walk on an evolving graph needs to be time-preserving, meaning a node can not pass a massage (through an edge) to a node at a earlier time.
@@
 Researchers have generalised many static graph centrality algorithms for evolving graphs.
-One approach is to use the fact that the elements of the matrix product of adjacency matrices at different time stamps can correctly count the number of temporal walks.
+One approach is to use the fact that the elements of the matrix product of adjacency matrices at different time stamps can correctly count the number of temporal paths.
 However, not every centrality algorithm can be generalised in this way.
-Another approach is to define evolving graph centrality algorithms using time-respecting walks.
-This approach is applicable to algorithms that are defined using paths or walks.
+Another approach is to define evolving graph centrality algorithms using time-respecting paths.
+This approach is applicable to algorithms that are defined using paths or paths.
 
@@
 % our contribution this paper
-Inspired by work
-Borgatti noted in \cite{borgatti05} that the manner of traffic flow entails a new way to think about centrality.
+Inspired by Borgatti's work \cite{borgatti05} on simulating different flow process on static graphs, we
+
+Borgatti noted in  that the manner of traffic flow entails a new way to think about centrality.
 where the author simulate different traffic flows to study centrality.
@@
 
-\section{Time-Preserving walks}
-\label{sec:time-pres-walks}
+\section{Motivation: A Closer Look at Katz Centrality on Evolving Graphs}
+\label{sec:motivation}
+
+We let $G_n = \langle G^{[1]}, G^{[2]}, \ldots, G^{[n]} \rangle$ be an evolving graph
+and $A^{[1]}, A^{[2]}, \dots A^{[n]}$ be the corresponding adjacency matrices.
+Then the dynamic communicability matrix is defined as
+\begin{equation}
+  \label{eq:q}
+  Q^{[k]} = (I - \alpha A^{[1]})^{-1}(I - \alpha A^{[2]})^{-1} \cdots (I -  \alpha A^{[n]})^{-1},
+\end{equation}
+where parameter $\alpha < 1/ \max_k \rho(A^{[k]})$, the spectral radius of $A^{[k]}$.
+The $i$th row sum of $Q^{[k]}$ is the broadcast centrality.
+
+Suppose $A$, $B$, and $C$ are three co-workers in a large internet company. Figure \ref{fig:katz_eg}
+shows how they exchange ideas during $3$ days at work. The directions of the arrows indicate the direction of the flow of ideas.
+For example, $A$ shares a new idea with $B$ on day $1$ and $B$ shares a new idea with $C$ on dat $3$. As a result, $A$'s idea can influence $C$.
+
+\begin{figure}[h]
+ \begin{center}
+    \begin{tikzpicture}[scale=.38, line width =1.5pt]
+  \node[circle,fill=green1, minimum size=0.2cm] (n7) at (-5,7) {B};
+  \node[circle,draw=red1, minimum size=0.2cm] (n8) at (-10,5) {C};
+  \node[circle,fill=green1, minimum size=0.2cm] (n10) at (-8,10) {A};
+  \node[circle,fill=green1, minimum size=0.2cm] (n6) at (3,7) {B};
+  \node[circle,fill=green1, minimum size=0.2cm] (n4) at (-2,5) {C};
+  \node[circle,fill=green1, minimum size=0.2cm] (n1) at (0,10) {A};
+   \node[circle,fill=green1, minimum size=0.2cm] (n11) at (11,7) {B};
+  \node[circle,fill=green1, minimum size=0.2cm] (n12) at (6,5)  {C};
+  \node[circle,draw=red1, minimum size=0.2cm] (n14) at (8,10) {A};
+  \foreach \from/\to in {n10/n7, n1/n4, n4/n1, n11/n12, n1/n6}
+   \draw[every edge,->] (\from) -- (\to);
+ %\draw[dotted,->](n4) -- (n12);
+% \draw[dotted,->](n7) to[out=80, in=40](n11);
+\draw [decorate,decoration={brace,amplitude=5pt},xshift=-4pt,yshift=0pt]
+(-4,3) -- (-10.5,3) node [midway,yshift=-0.6cm]{ $1$};
+\draw [decorate,decoration={brace,amplitude=5pt},xshift=-4pt,yshift=0pt]
+(4,3) -- (-2,3) node [midway,yshift=-0.6cm]{$2$};
+\draw [decorate,decoration={brace,amplitude=5pt},xshift=-4pt,yshift=0pt]
+(11.5,3) -- (5.5,3) node [midway,yshift=-0.6cm]{ $3$};
+    \end{tikzpicture}
+\end{center}
+\caption{An evolving directed graph with 3 time stamps $1$, $2$ and $3$.
+At each time stamp, the evolving graph is represented as a graph.
+The green filled circles represent active nodes while the red circles represent
+inactive nodes. Directed edges in each time stamp are shown as black arrows.}
+\label{fig:katz_eg}
+\end{figure}
+
+We could use EvolvingGraphs.jl to generate the above evolving graph and compute the Katz centrality.
+
+\begin{lstlisting}
+using EvolvingGraphs
+using EvolvingGraphs.Centrality
+
+g = EvolvingGraph{Node{String}, Int}()
+add_bunch_of_edges!(g, [("A", "B", 1), ("A", "C", 2),
+("A", "B", 2),("C", "A", 2),("B", "C", 3)])
+\end{lstlisting}
+
+The centrality values for each node are
+\begin{lstlisting}
+katz(g)
+3-element Array{Tuple{EvolvingGraphs.Node{String},Float64},1}:
+ (Node(A), 0.742301)
+ (Node(B), 0.42943)
+ (Node(C), 0.514373)
+\end{lstlisting}
+
+As expected $A$ is the most important node in the network. $C$ is the second important node in the network as it influenced
+$A$ at time stamp $2$.
+If we reverse the time of communication between day $1$ and $3$, i.e., $B$ shares a new idea with $C$ on day $1$ and $A$ shares a new idea with $B$ on day $3$.
+Then the idea $A$ had on day $3$ can not pass to $C$ in this case.
+This is illustrated in Figure \ref{fig:katz_eg2}.
+
+\begin{figure}[h]
+ \begin{center}
+    \begin{tikzpicture}[scale=.38, line width =1.5pt]
+  \node[circle,fill=green1, minimum size=0.2cm] (n7) at (-5,7) {B};
+  \node[circle,fill=green1, minimum size=0.2cm] (n8) at (-10,5) {C};
+  \node[circle,draw=red1, minimum size=0.2cm] (n10) at (-8,10) {A};
+  \node[circle,fill=green1, minimum size=0.2cm] (n6) at (3,7) {B};
+  \node[circle,fill=green1, minimum size=0.2cm] (n4) at (-2,5) {C};
+  \node[circle,fill=green1, minimum size=0.2cm] (n1) at (0,10) {A};
+   \node[circle,fill=green1, minimum size=0.2cm] (n11) at (11,7) {B};
+  \node[circle,draw=red1, minimum size=0.2cm] (n12) at (6,5)  {C};
+  \node[circle,fill=green1, minimum size=0.2cm] (n14) at (8,10) {A};
+  \foreach \from/\to in {n7/n8, n1/n4, n4/n1, n1/n6, n14/n11}
+   \draw[every edge,->] (\from) -- (\to);
+ %\draw[dotted,->](n4) -- (n12);
+% \draw[dotted,->](n7) to[out=80, in=40](n11);
+\draw [decorate,decoration={brace,amplitude=5pt},xshift=-4pt,yshift=0pt]
+(-4,3) -- (-10.5,3) node [midway,yshift=-0.6cm]{ $1$};
+\draw [decorate,decoration={brace,amplitude=5pt},xshift=-4pt,yshift=0pt]
+(4,3) -- (-2,3) node [midway,yshift=-0.6cm]{ $2$};
+\draw [decorate,decoration={brace,amplitude=5pt},xshift=-4pt,yshift=0pt]
+(11.5,3) -- (5.5,3) node [midway,yshift=-0.6cm]{ $3$};
+    \end{tikzpicture}
+\end{center}
+\caption{An evolving directed graph with 3 time stamps $1$, $2$ and $3$.
+At each time stamp, the evolving graph is represented as a graph.
+The green filled circles represent active nodes while the red circles represent
+inactive nodes. Directed edges in each time stamp are shown as black arrows.}
+\label{fig:katz_eg2}
+\end{figure}
+
+In this cast, we have
+\begin{lstlisting}
+g2 = EvolvingGraph{Node{String}, Int}()
+add_bunch_of_edges!(g2, [("A", "B", 3), ("A", "C", 2),
+("A", "B", 2),("C", "A", 2),("B", "C", 1)])
+\end{lstlisting}
+
+The centrality ratings of the three nodes are
+
+\begin{lstlisting}
+katz(g2)
+3-element Array{Tuple{EvolvingGraphs.Node{String},Float64},1}:
+ (Node(A), 0.687679)
+ (Node(B), 0.490062)
+ (Node(C), 0.535666)
+\end{lstlisting}
+
+Notice the rating of $A$ decreased as its influence is not as important as in Figure \ref{fig:katz_eg}.
+
+% does not take account of walks in a long time. cost in time
+If the final communication between $A$ and $B$ are not on day $3$ but on day $100$, as shown in Figure \ref{fig:katz_eg3},
+we would expect the centrality ratings to change. However, according to \eqref{eq:q}, ratings are unchanged.
+We notice that the generalised Katz centrality on evolving graphs only takes account of the edges at each time stamp but not the communication time between edges at different time stamps.
+
+\begin{figure}[h]
+ \begin{center}
+    \begin{tikzpicture}[scale=.38, line width =1.5pt]
+  \node[circle,fill=green1, minimum size=0.2cm] (n7) at (-5,7) {B};
+  \node[circle,fill=green1, minimum size=0.2cm] (n8) at (-10,5) {C};
+  \node[circle,draw=red1, minimum size=0.2cm] (n10) at (-8,10) {A};
+  \node[circle,fill=green1, minimum size=0.2cm] (n6) at (3,7) {B};
+  \node[circle,fill=green1, minimum size=0.2cm] (n4) at (-2,5) {C};
+  \node[circle,fill=green1, minimum size=0.2cm] (n1) at (0,10) {A};
+   \node[circle,fill=green1, minimum size=0.2cm] (n11) at (11,7) {B};
+  \node[circle,draw=red1, minimum size=0.2cm] (n12) at (6,5)  {C};
+  \node[circle,fill=green1, minimum size=0.2cm] (n14) at (8,10) {A};
+  \foreach \from/\to in {n7/n8, n1/n4, n4/n1, n1/n6, n14/n11}
+   \draw[every edge,->] (\from) -- (\to);
+ %\draw[dotted,->](n4) -- (n12);
+% \draw[dotted,->](n7) to[out=80, in=40](n11);
+\draw [decorate,decoration={brace,amplitude=5pt},xshift=-4pt,yshift=0pt]
+(-4,3) -- (-10.5,3) node [midway,yshift=-0.6cm]{ $1$};
+\draw [decorate,decoration={brace,amplitude=5pt},xshift=-4pt,yshift=0pt]
+(4,3) -- (-2,3) node [midway,yshift=-0.6cm]{ $2$};
+\draw [decorate,decoration={brace,amplitude=5pt},xshift=-4pt,yshift=0pt]
+(11.5,3) -- (5.5,3) node [midway,yshift=-0.6cm]{ $100$};
+    \end{tikzpicture}
+\end{center}
+\caption{An evolving directed graph with 3 time stamps $1$, $2$ and $100$.
+At each time stamp, the evolving graph is represented as a graph.
+The green filled circles represent active nodes while the red circles represent
+inactive nodes. Directed edges in each time stamp are shown as black arrows.}
+\label{fig:katz_eg3}
+\end{figure}
+
+\section{Time-Preserving paths}
+\label{sec:time-pres-paths}
 
@@
 
-We now describe time-preserving walks in more detail. We follow the definition of
+We now describe time-preserving paths in more detail. We follow the definition of
 \emph{evolving graph}, \emph{temporal node} and \emph{active node} in \cite{chen16}.
@@
 
-\section{Centrality Measures}
-\label{sec:topol-temp-flow}
+\subsection{Evolving Graphs and Static Graphs}
+\label{sec:centr-block-adjac}
 
-In \cite{tang10s}, a temporal shortest walk is measured in time units only, i.e., if node
-$v_i$ can reach node $v_j$ in $k$ time steps then the distance between node
-$v_i$ and $v_j$ is $k$. We can apply temporal breadth first
-search (BFS) \cite{chen16} to discover the temporal walks and then only take account of the temporal difference between the first node $(v_1, t_1)$ and the last node $(v_n, t_n)$, i.e., $t_n - t_1$.
-
-If we use this definition of temporal walk for the temporal Katz centrality introduced in
-\cite{grindrod11}, we have a new centrality measure.
-In the matrix form, the nonzero entries of $A^{[t_i]} A^{[t_{i+1}]}$ counts all the temporal walks of length $1$, and
-$A^{[t_i]}\cdots A^{[t_j]}$, where $i < j$ counts all the temporal walks of length $j -i$.
-For example, $A^{[1]}A^{[4]}$, $A^{[1]}A^{[1]}A^{[4]}$ and $A^{[1]}A^{[2]}A^{[3]}A^{[4]}$ are all walks of length 3.
-In the original Katz centrality, the `attenuation' factor $\alpha$ is imposed on the
-number of walks, i.e., longer walks has smaller effect to the overall rating.
-Hence the final result is the summation of all products of the form
-\[
-\alpha^k A^{[i]} \cdots A^{[i+k]}
-\]
-% Note this can not be written in \eqref{eq:katz}, as discussed in Section \ref{sec:temp-katz-centr}.
-
-Another definition of temporal walk was introduced by \cite{chen16}. Here
-both static edges and causal edges are considered.
-We can represent an evolving graph by a block adjacency matrix, as shown in Section \ref{sec:centr-block-adjac}.
-Centrality on this block matrix gives the importance of each node at all time stamps.
-We can average these rating at different time stamps to
-get the final rating.
-
-We review a few well-known measures of evolving graph centrality.
-(Design a simple example and discuss it in each case below.)
-
-\subsection{Temporal Katz Centrality and Communicability Betweenness Centrality}
-\label{sec:temp-katz-centr}
-
-The Katz Centrality is a measure of importance
-
-In \cite{grindrod11}, Grindrod et al. define a \emph{dynamic walk} of length $m$ from
-node $v_1$ to node $v_{w+1}$  as a sequence of edges
-$(v_1, v_2), (v_2, v_3), \ldots (v_w, v_{w+1})$ and a non-decreasing sequence of times
-$t_{r_1} \leq t_{r_2} \leq \cdots \leq t_{r_w}$ such that the adjacency matrix at time stamp
-$r_m$, i.e., $A_{i_m, i_{m+1}}^{[r_m]} \ne 0$.
-Note that in this definition the authors only take account of the static edges and the length of a dynamic walk is determined by the number of static edges.
-
-The Katz centrality is based on a sequence of matrix products
-\begin{equation}
-\label{eq:katz}
-Q = (I - \alpha A^{[0]})^{-1}(I - \alpha A^{[1]})^{-1} \cdots (I - \alpha A^{[M]})^{-1}.
-\end{equation}
-The $i$th row and column sums
-$$
-C_i^{broadcast} = \sum_{k=1}^n Q_{ik}, \quad C_i^{receive} = \sum_{k=1}^n Q_{ki}
-$$
-are the broadcast centrality and receive centrality of node $i$.
-
-\subsection{Temporal Betweenness and Closeness Centrality}
-\label{sec:temp-betw-centr}
-
-Recall that betweenness centrality of a node in a static graph is defined by counting the fraction of shortest walks that traverse it.
-We could extend
-betweenness centrality on evolving graphs by replacing shortest walks with temporal shortest walks \cite{nicosia13}.
-\begin{equation}
-  \label{eq:bet1}
-C_i^{betweenness} = \sum_{j \in V}\sum_{k \in V, k \ne j}\frac{\alpha_{jk}(i)}{\alpha_{jk}},
-\end{equation}
-where $\alpha_{jk}$ represents the number of temporal shortest walks from node $j$ to node $k$ and $\alpha_{jk}(i)$ represents the number of temporal shortest walks from node $j$ to node $k$ that pass through the node $i$.
-
-One may want to take into account the length of time a node passes a message. The temporal betweenness centrality of the node $i$ at time stamp $t_m$ is defined as
-\begin{equation}
-  \label{eq:bet2}
-  C_i^{betweenness}(t_m) = \sum_{j\ne i}\sum_{k\ne j, k\ne i}\frac{U_{j,k,t_m}(i)}{\alpha_{j,k}},
-\end{equation}
-where, as before, $\alpha_{j,k}$ represents the number of temporal shortest walks from $j$ to $k$ and $U_{j,k,t_m}(i)$ represents the number of temporal shortest walks from $j$ to $k$ in which node $i$ is traversed from
-the walk in the time stamp $t_m$ or a previous time stamp $t_{m-1}$. Then
-average temporal betweenness of node $i$ is then defined as
-$$
-  C_i^{betweenness} = \frac{1}{M}\sum_m C_i^{betweenness}(t_m).
-$$
-Note \eqref{eq:bet1} only takes account of static edges while \eqref{eq:bet2} takes account of both static edges and causal edges.
-
-% closeness centrality
-Similar to betweenness centrality, let $d_{ij}$ be the length of a temporal shortest walk from $i$ and $j$ in an evolving graph. Then
-the closeness centrality of a node $i$ is defined
-$$
-C_i^{closeness} = \frac{N-1}{\sum_j d_{ij}}.
-$$
-Note that this depends on how we define the length of temporal shortest walk. The closeness centrality can takes account of only static edges, only causal edges, or both.
-
-\subsection{Mapping from Evolving Graphs to Static Graphs}
-\label{sec:centr-block-adjac}
+We can not simply use static graphs to replace evolving graphs for two main reasons.
+First, a path has to preseve the dimension, i.e., certain path is incorrect in the aggregated static graph.
+Second, two path between $A$ and $B$ are considered to be one path in the aggregated static graph.
 
@@
 
+\section{Centrality Measures}
+\label{sec:topol-temp-flow}
+
+In \cite{tang10s}, a temporal shortest walk is measured in time units only, i.e., if node
+$v_i$ can reach node $v_j$ in $k$ time steps then the distance between node
+$v_i$ and $v_j$ is $k$. We can apply temporal breadth first
+search (BFS) \cite{chen16} to discover the temporal paths and then only take account of the temporal difference between the first node $(v_1, t_1)$ and the last node $(v_n, t_n)$, i.e., $t_n - t_1$.
+
+If we use this definition of temporal walk for the temporal Katz centrality introduced in
+\cite{grindrod11}, we have a new centrality measure.
+In the matrix form, the nonzero entries of $A^{[t_i]} A^{[t_{i+1}]}$ counts all the temporal paths of length $1$, and
+$A^{[t_i]}\cdots A^{[t_j]}$, where $i < j$ counts all the temporal paths of length $j -i$.
+For example, $A^{[1]}A^{[4]}$, $A^{[1]}A^{[1]}A^{[4]}$ and $A^{[1]}A^{[2]}A^{[3]}A^{[4]}$ are all paths of length 3.
+In the original Katz centrality, the `attenuation' factor $\alpha$ is imposed on the
+number of paths, i.e., longer paths has smaller effect to the overall rating.
+Hence the final result is the summation of all products of the form
+\[
+\alpha^k A^{[i]} \cdots A^{[i+k]}
+\]
+% Note this can not be written in \eqref{eq:katz}, as discussed in Section \ref{sec:temp-katz-centr}.
+
+Another definition of temporal walk was introduced by \cite{chen16}. Here
+both static edges and causal edges are considered.
+We can represent an evolving graph by a block adjacency matrix, as shown in Section \ref{sec:centr-block-adjac}.
+Centrality on this block matrix gives the importance of each node at all time stamps.
+We can average these rating at different time stamps to
+get the final rating.
+
+We review a few well-known measures of evolving graph centrality.
+(Design a simple example and discuss it in each case below.)
+
+% can not simply aggregate nodes: introduce wrong paths.
+
+\subsection{Temporal Katz Centrality and Communicability Betweenness Centrality}
+\label{sec:temp-katz-centr}
+
+The Katz Centrality is a measure of importance
+
+In \cite{grindrod11}, Grindrod et al. define a \emph{dynamic walk} of length $m$ from
+node $v_1$ to node $v_{w+1}$  as a sequence of edges
+$(v_1, v_2), (v_2, v_3), \ldots (v_w, v_{w+1})$ and a non-decreasing sequence of times
+$t_{r_1} \leq t_{r_2} \leq \cdots \leq t_{r_w}$ such that the adjacency matrix at time stamp
+$r_m$, i.e., $A_{i_m, i_{m+1}}^{[r_m]} \ne 0$.
+Note that in this definition the authors only take account of the static edges and the length of a dynamic walk is determined by the number of static edges.
+
+The Katz centrality is based on a sequence of matrix products
+\begin{equation}
+\label{eq:katz}
+Q = (I - \alpha A^{[0]})^{-1}(I - \alpha A^{[1]})^{-1} \cdots (I - \alpha A^{[M]})^{-1}.
+\end{equation}
+The $i$th row and column sums
+$$
+C_i^{broadcast} = \sum_{k=1}^n Q_{ik}, \quad C_i^{receive} = \sum_{k=1}^n Q_{ki}
+$$
+are the broadcast centrality and receive centrality of node $i$.
+
+Note that the $(i,j)$th element of adjacency matrix $A^k$ counts the only of paths from $i$ to $j$.
+To simulate a Katz centrality,
+the shortest path algorithms search through all possible paths between $i$ and $j$.
+
+\subsection{Temporal Betweenness and Closeness Centrality}
+\label{sec:temp-betw-centr}
+
+Recall that betweenness centrality of a node in a static graph is defined by counting the fraction of shortest paths that traverse it.
+We could extend
+betweenness centrality on evolving graphs by replacing shortest paths with temporal shortest paths \cite{nicosia13}.
+\begin{equation}
+  \label{eq:bet1}
+C_i^{betweenness} = \sum_{j \in V}\sum_{k \in V, k \ne j}\frac{\alpha_{jk}(i)}{\alpha_{jk}},
+\end{equation}
+where $\alpha_{jk}$ represents the number of temporal shortest paths from node $j$ to node $k$ and $\alpha_{jk}(i)$ represents the number of temporal shortest paths from node $j$ to node $k$ that pass through the node $i$.
+
+One may want to take into account the length of time a node passes a message. The temporal betweenness centrality of the node $i$ at time stamp $t_m$ is defined as
+\begin{equation}
+  \label{eq:bet2}
+  C_i^{betweenness}(t_m) = \sum_{j\ne i}\sum_{k\ne j, k\ne i}\frac{U_{j,k,t_m}(i)}{\alpha_{j,k}},
+\end{equation}
+where, as before, $\alpha_{j,k}$ represents the number of temporal shortest paths from $j$ to $k$ and $U_{j,k,t_m}(i)$ represents the number of temporal shortest paths from $j$ to $k$ in which node $i$ is traversed from
+the walk in the time stamp $t_m$ or a previous time stamp $t_{m-1}$. Then
+average temporal betweenness of node $i$ is then defined as
+$$
+  C_i^{betweenness} = \frac{1}{M}\sum_m C_i^{betweenness}(t_m).
+$$
+Note \eqref{eq:bet1} only takes account of static edges while \eqref{eq:bet2} takes account of both static edges and causal edges.
+
+% closeness centrality
+Similar to betweenness centrality, let $d_{ij}$ be the length of a temporal shortest walk from $i$ and $j$ in an evolving graph. Then
+the closeness centrality of a node $i$ is defined
+$$
+C_i^{closeness} = \frac{N-1}{\sum_j d_{ij}}.
+$$
+Note that this depends on how we define the length of temporal shortest walk. The closeness centrality can takes account of only static edges, only causal edges, or both.
+
 \subsection{Reverse Temporal Flows}
@@
 In this section, we vary the edge
-weights in both static and causal edges to study the impact of time-preserving walks on evolving graph centrality.
+weights in both static and causal edges to study the impact of time-preserving paths on evolving graph centrality.
 We also compare evolving graph centrality with the aggregated static graph case to gain insight about the advantage of evolving graph model.

### 2018-05-11 paper.tex
add more experiments and update the paper content in Katz centrality

@@
 
-\title{A Closer Look at Time-Preserving paths on Evolving Graphs}
+\title{A Closer Look at Network Flow on Evolving Graphs}
 
@@
 
+\newenvironment{njh}{\begin{quote}\small\sf{\color{blue}$\diamondsuit$~NJH~}}{\end{quote}}
+\newenvironment{wz}{\begin{quote}\small\sf{\color{green}$\diamondsuit$~WZ~}}{\end{quote}}
+
 \begin{document}
@@
 We construct an evolving coauthor network from a collection of research papers for the experiments.
+
+We observe that time span has an important impact on evolving graph centrality. Build on this idea,
+we introduce more general definitions of walk and shortest path based centralities.
+Generalizing PageRank on evolving graphs is a hard problem.
+We provide two definitions of evolving graph centrality.
+Our experiments indicate our algorithm is effective.
+
 \end{abstract}
@@
 
-\section{Time-Preserving paths}
+\section{Time-Preserving Walks and Paths}
 \label{sec:time-pres-paths}
 
-For example, in Figure \ref{fig:eg_shortest_walk}
-$\langle (1, t_1), (2, t_1) \rangle$ is a static edge at time stamp $t_1$ and $\langle (3, t_2), (3, t_3) \rangle$ is a causal edge between time stamp $t_2$ and time stamp $t_3$.
-The difference between static edges and causal edges were first explicitly considered in \cite{chen16}.
+% what is walk and what is path?
+A walk of length $l$ is a sequence of nodes $v_1, v_2, \ldots, v_l, v_{l+1}$ such that for
+each $i = 1, 2, \ldots, l$, there is an edge from $v_i$ to $v_{i+1}$. A path of length $l$ is a walk of length $l$
+such that all the nodes are different.
+% relate to centrality
+The definition of centrality depends on the manner in which traffic flows through a network \cite{borgatti05}.
+Time-preserving walks induce temporal Katz centrality and temporal closeness Centrality while time-preserving paths
+induce betweenness centrality and closeness centrality.
+
+We now describe time-preserving paths in more detail. We follow the definition of
+\emph{evolving graph}, \emph{temporal node} and \emph{active node} in \cite{chen16}.
+
+\begin{definition}
+  An \textbf{evolving graph} $G_n$ is a sequence of (static) graphs
+$G_n = \langle G^{[1]}, G^{[2]},  \ldots ,G^{[n]} \rangle$ with associated time stamps
+$t_1, t_2, \ldots, t_n$ respectively. Each $G^{[t]} = (V^{[t]}, E^{[t]})$ represents a (static) graph labeled by a time t.
+\end{definition}
+
+Note the node sets $V^{[t]}$ can change over time, i.e., nodes may appear or disappear at a particular time stamp.
+For example, in Figure \ref{fig:eg_shortest_walk}, at time stamp $t_1$, $V^{[1]} = \langle 1, 2 \rangle$ and $E^{[1]} = \langle (1,2) \rangle$.
+Each graph $G^{[t]}$ can be represented by its adjacency matrix $A^{[t]}$.
+We can represent $G_n$ by a list of adjacency matrices $A_n = \langle A^{[1]}, A^{[2]}, \ldots, A^{[n]} \rangle$.
+
+If we use this definition of temporal walk for the temporal Katz centrality introduced in
+\cite{grindrod11}, we have a new centrality measure.
+In the matrix form, the nonzero entries of $A^{[t_i]} A^{[t_{i+1}]}$ counts all the temporal paths of length $1$, and
+$A^{[t_i]}\cdots A^{[t_j]}$, where $i < j$ counts all the temporal paths of length $j -i$.
+For example, $A^{[1]}A^{[4]}$, $A^{[1]}A^{[1]}A^{[4]}$ and $A^{[1]}A^{[2]}A^{[3]}A^{[4]}$ are all paths of length 3.
+In the original Katz centrality, the `attenuation' factor $\alpha$ is imposed on the
+number of paths, i.e., longer paths has smaller effect to the overall rating.
+Hence the final result is the summation of all products of the form
+\[
+\alpha^k A^{[i]} \cdots A^{[i+k]}
+\]
+% Note this can not be written in \eqref{eq:katz}, as discussed in Section \ref{sec:temp-katz-centr}.
+
+Another definition of temporal walk was introduced by \cite{chen16}. Here
+both static edges and causal edges are considered.
+We can represent an evolving graph by a block adjacency matrix, as shown in Section \ref{sec:centr-block-adjac}.
+Centrality on this block matrix gives the importance of each node at all time stamps.
+We can average these rating at different time stamps to
+get the final rating.
 
@@
 \draw [decorate,decoration={brace,amplitude=5pt},xshift=-4pt,yshift=0pt]
-(4,3) -- (-2,3) node [midway,yshift=-0.6cm]{ $t_2$};
+(-4,3) -- (-10.5,3) node [midway,yshift=-0.6cm]{ $1998$};
 \draw [decorate,decoration={brace,amplitude=5pt},xshift=-4pt,yshift=0pt]
-(-4,3) -- (-10.5,3) node [midway,yshift=-0.6cm]{ $t_1$};
+(4,3) -- (-2,3) node [midway,yshift=-0.6cm]{ $1999$};
 \draw [decorate,decoration={brace,amplitude=5pt},xshift=-4pt,yshift=0pt]
-(11.5,3) -- (5.5,3) node [midway,yshift=-0.6cm]{ $t_3$};
+(11.5,3) -- (5.5,3) node [midway,yshift=-0.6cm]{ $2018$};
     \end{tikzpicture}
 \end{center}
-\caption{An evolving directed graph with 3 time stamps $t_1$, $t_2$ and $t_3$.
+\caption{An evolving directed graph with 3 time stamps $1998$, $1999$ and $2018$.
 At each time stamp, the evolving graph is represented as a graph.
@@
 $\langle (1, t_1) ,(2, t_1) , (2, t_3), (3, t_3)\rangle$ in Figure \ref{fig:eg_shortest_walk} has length $4$ in total because two static edges $\langle (1, t_1) (2, t_1) \rangle$ and $\langle (2, t_3), (3, t_3) \rangle$ have length one, whereas $\langle (2, t_1) (2, t_3) \rangle$ traverse $2$ time stamps so has length $2$.
-
-We now describe time-preserving paths in more detail. We follow the definition of
-\emph{evolving graph}, \emph{temporal node} and \emph{active node} in \cite{chen16}.
-
-\begin{definition}
-  An \textbf{evolving graph} $G_n$ is a sequence of (static) graphs
-$G_n = \langle G^{[1]}, G^{[2]},  \ldots ,G^{[n]} \rangle$ with associated time stamps
-$t_1, t_2, \ldots, t_n$ respectively. Each $G^{[t]} = (V^{[t]}, E^{[t]})$ represents a (static) graph labeled by a time t.
-\end{definition}
-
-Note the node sets $V^{[t]}$ can change over time, i.e., nodes may appear or disappear at a particular time stamp.
-For example, in Figure \ref{fig:eg_shortest_walk}, at time stamp $t_1$, $V^{[1]} = \langle 1, 2 \rangle$ and $E^{[1]} = \langle (1,2) \rangle$.
-Each graph $G^{[t]}$ can be represented by its adjacency matrix $A^{[t]}$.
-We can represent $G_n$ by a list of adjacency matrices $A_n = \langle A^{[1]}, A^{[2]}, \ldots, A^{[n]} \rangle$.
 
@@
 
+ For example, in Figure \ref{fig:eg_shortest_walk}
+ $\langle (1, t_1), (2, t_1) \rangle$ is a static edge at time stamp $t_1$ and $\langle (3, t_2), (3, t_3) \rangle$ is a causal edge between time stamp $t_2$ and time stamp $t_3$.
+ The difference between static edges and causal edges were first explicitly considered in \cite{chen16}.
+
 A time-preserving walk can traverse both causal edges and static edges.
@@
 
-\subsection{Evolving Graphs and Static Graphs}
+The following function measure the temporal distance between two active nodes in an evolving graph.
+
+\begin{lstlisting}
+function temporal_distance(v1::TimeNode,
+                           v2::TimeNode, beta::Real = 1.)
+  return node_key(v1) == node_key(v2) ?
+  beta* abs(node_timestamp(v1) - node_timestamp(v2)) : 0
+end
+\end{lstlisting}
+which means if two active nodes have the same key name, the temporal distance is the difference between their time stamps.
+
+\section{Centrality Measures}
+\label{sec:topol-temp-flow}
+
+% what is centrality?
+Centrality measures the importance of nodes within a graph.
+% current evolving graph centrality approach
+To generalize centrality measures for evolving graphs, there are two common approaches.
+First, we could exploit the fact that matrix product of adjacency matrices at different time stamps counts the number of dynamic walks in an evolving graph.
+Using this idea, we can generalize walk-based centrality measures such as
+the Katz Centrality \cite{estrada09} and Communicability Betweenness \cite{alsayed15}.
+Second, we could generalize the definition of shortest paths as shortest temporal paths and replace shortest paths in centrality measures with shortest temporal paths.
+This way we can define temporal betweenness centrality and temporal closeness centrality \cite{nicosia13}.
+
+% our approach
+We observe both approaches ignore the communication time between edges at different time stamps, i.e., the time gap between different graph slices.
+We take account of this communication time by deriving centrality measures from original ideas and show communication time has important impact on the final rating (and ranking).
+We note that our goal is not about providing faster centrality algorithms which is out of the scope of this paper.
+
+\subsection{Temporal Katz Centrality}
+\label{sec:temp-katz-centr}
+
+% katz centrality from first principle
+Katz Centrality accounts the influence of nearest-neighbours to a give node and the influence of other nodes
+separated at a certain distance from it. The $k$th power of adjacency matrix $A$, i.e., $A^k$, of a graph $G$ accounts for walk of length $k$. The expansion
+\begin{equation}
+  \label{eq:a}
+  A^0 + \alpha A + \alpha^2 A^2 + \cdots,
+\end{equation}
+converges to $(I - \alpha A)^{-1}$ when $\alpha < 1/\rho(A)$, the spectral radius of $A$. The $(i,j)$ entry of \eqref{eq:a}
+accounts all walks from $i$ and $j$ with the influence of walks of length $k$ scaled by a factor of $\alpha^k$.
+The Katz centrality of node $i$ is the $i$th row sum of $(I - \alpha A)^{-1}$, which is the sum of influence of all the nodes that node $i$ can reach via a walk.
+In other words, we start with node $i$ and each out-neighbour of node $i$ has influence $\alpha$ on node $i$ and the out-neighbour of out-neighbour of node $i$ has influence $\alpha^2$ on node $i$, and so on.
+
+For evolving graphs, we replace out-neighbours with forward neighbours which preserve the direction of time.
+Then the Katz score of a node $i$ at time stamp $t$, denoted by $(i,t)$, is the sum of influence of all the active nodes that $(i,t)$ can reach via a time-preserving walk.
+Unlike \cite{grindrod11}, we also consider the temporal distance between two nodes. For example, the temporal distance between $(i, 2001)$ and $(i, 2018)$ is $17$.
+% julia code implementation
+With the defintion of \texttt{temporal\_distance} introduced in Section \ref{sec:time-pres-paths}.
+We define the temporal Katz score of node $(i, t)$ as
+
+\begin{lstlisting}
+function temporal_katz(g::AbstractEvolvingGraph,
+  v::TimeNode; alpha = 0.1, max_level = 5)
+  score = 0.
+  fronter = [v]
+  level = 0
+  while level < max_level
+      next = []
+      for u in fronter
+          for v in forward_neighbors(g, u)
+              push!(next, v)
+              d = temporal_distance(v, u)
+              d += level
+              score += alpha^d
+          end
+      end
+      fronter = next
+      level += 1
+  end
+  return score
+end
+\end{lstlisting}
+
+% explain the code
+The algorithm \texttt{temporal\_katz} performs breadth first search (BFS) starting at \texttt{TimeNode} $v$, which represent a node at a specific time stamp \footnote{See also \url{https://etymoio.github.io/EvolvingGraphs.jl/latest/base.html#EvolvingGraphs.TimeNode}}.
+For each \texttt{TimeNode} $v$, we accumulate the influence of linked nodes according to their spatial and temporal
+distance from $v$. The spatial distance is recorded in variable \texttt{level} and the temporal distance is calculated by
+\texttt{temporal\_distance}.
+
+% example on 3 timestamp evolving graph
+
+% compare the Katz in EvolvingGraphs.jl
+
+Let $A$ be an adjacency
+
+In \cite{grindrod11}, Grindrod et al. define a \emph{dynamic walk} of length $m$ from
+node $v_1$ to node $v_{w+1}$  as a sequence of edges
+$(v_1, v_2), (v_2, v_3), \ldots (v_w, v_{w+1})$ and a non-decreasing sequence of times
+$t_{r_1} \leq t_{r_2} \leq \cdots \leq t_{r_w}$ such that the adjacency matrix at time stamp
+$r_m$, i.e., $A_{i_m, i_{m+1}}^{[r_m]} \ne 0$.
+Note that in this definition the authors only take account of the static edges and the length of a dynamic walk is determined by the number of static edges.
+
+The Katz centrality is based on a sequence of matrix products
+\begin{equation}
+\label{eq:katz}
+Q = (I - \alpha A^{[0]})^{-1}(I - \alpha A^{[1]})^{-1} \cdots (I - \alpha A^{[M]})^{-1}.
+\end{equation}
+The $i$th row and column sums
+$$
+C_i^{broadcast} = \sum_{k=1}^n Q_{ik}, \quad C_i^{receive} = \sum_{k=1}^n Q_{ki}
+$$
+are the broadcast centrality and receive centrality of node $i$.
+
+Note that the $(i,j)$th element of adjacency matrix $A^k$ counts the only of paths from $i$ to $j$.
+To simulate a Katz centrality,
+the shortest path algorithms search through all possible paths between $i$ and $j$.
+
+\subsection{Temporal Communicability Betweenness Centrality}
+
+% communicability from first principle
+
+\subsection{Temporal Closeness Centrality}
+\label{sec:temp-betw-centr}
+
+\begin{wz}
+  We may also consider betweenness centrality.
+\end{wz}
+
+Recall that betweenness centrality of a node in a static graph is defined by counting the fraction of shortest paths that traverse it.
+We could extend
+betweenness centrality on evolving graphs by replacing shortest paths with temporal shortest paths \cite{nicosia13}.
+\begin{equation}
+  \label{eq:bet1}
+C_i^{betweenness} = \sum_{j \in V}\sum_{k \in V, k \ne j}\frac{\alpha_{jk}(i)}{\alpha_{jk}},
+\end{equation}
+where $\alpha_{jk}$ represents the number of temporal shortest paths from node $j$ to node $k$ and $\alpha_{jk}(i)$ represents the number of temporal shortest paths from node $j$ to node $k$ that pass through the node $i$.
+
+One may want to take into account the length of time a node passes a message. The temporal betweenness centrality of the node $i$ at time stamp $t_m$ is defined as
+\begin{equation}
+  \label{eq:bet2}
+  C_i^{betweenness}(t_m) = \sum_{j\ne i}\sum_{k\ne j, k\ne i}\frac{U_{j,k,t_m}(i)}{\alpha_{j,k}},
+\end{equation}
+where, as before, $\alpha_{j,k}$ represents the number of temporal shortest paths from $j$ to $k$ and $U_{j,k,t_m}(i)$ represents the number of temporal shortest paths from $j$ to $k$ in which node $i$ is traversed from
+the walk in the time stamp $t_m$ or a previous time stamp $t_{m-1}$. Then
+average temporal betweenness of node $i$ is then defined as
+$$
+  C_i^{betweenness} = \frac{1}{M}\sum_m C_i^{betweenness}(t_m).
+$$
+Note \eqref{eq:bet1} only takes account of static edges while \eqref{eq:bet2} takes account of both static edges and causal edges.
+
+% closeness centrality
+Similar to betweenness centrality, let $d_{ij}$ be the length of a temporal shortest walk from $i$ and $j$ in an evolving graph. Then
+the closeness centrality of a node $i$ is defined
+$$
+C_i^{closeness} = \frac{N-1}{\sum_j d_{ij}}.
+$$
+Note that this depends on how we define the length of temporal shortest walk. The closeness centrality can takes account of only static edges, only causal edges, or both.
+
+\subsection{Temporal PageRank}
+
+We derive two generalization of PageRank on evolving graphs.
+The first idea is based on reverse temporal flows.
+
+\subsubsection{Reverse Temporal Flows}
+
+We can not travel back in time. But reversing the direction of temporal flows can help
+identify the ``hub'' nodes or the source of the flows. The authority score of a page is
+proportional to its importance, and the hub score describes the quality of a page as a link collection of important related pages \cite{kleinberg99}.
+Indeed, reverse PageRank has
+been studied by \cite{bar08, fogaras03, gleich15}. In reverse PageRank we compute PageRank on the graph with reversed direction, i.e., reverse the direction of each edge $(i,j)$ to $(j, i)$.
+Fogaras \cite{fogaras03} shows that Reversed Page Rank scores express hub quality.
+
+Recall a time-preserving walk is a time-ordered sequence of active nodes. Here we define a \emph{reversed temporal walk} to be a reversed time-ordered sequence of active nodes, i.e.,
+$t_1 \ge t_2 \ge \cdots \ge t_m$.
+
+\subsubsection{Block Adjacency Matrices}
 \label{sec:centr-block-adjac}
@@
 We can not simply use static graphs to replace evolving graphs for two main reasons.
-First, a path has to preseve the dimension, i.e., certain path is incorrect in the aggregated static graph.
+First, a path has to preserve the dimension, i.e., certain path is incorrect in the aggregated static graph.
 Second, two path between $A$ and $B$ are considered to be one path in the aggregated static graph.
 
-In \cite{chen16}, we derive a block adjacency matrix representation of an evolvign graph.
+In \cite{chen16}, we derive a block adjacency matrix representation of an evolving graph.
 If $E'$ is the set of causal edges and $\hat E$ is the set of static edges then
@@
 
-\section{Centrality Measures}
-\label{sec:topol-temp-flow}
+We consider two generalisation of pagerank: a block matrix one and a dense matrix one that is based on probability
 
-In \cite{tang10s}, a temporal shortest walk is measured in time units only, i.e., if node
-$v_i$ can reach node $v_j$ in $k$ time steps then the distance between node
-$v_i$ and $v_j$ is $k$. We can apply temporal breadth first
-search (BFS) \cite{chen16} to discover the temporal paths and then only take account of the temporal difference between the first node $(v_1, t_1)$ and the last node $(v_n, t_n)$, i.e., $t_n - t_1$.
-
-If we use this definition of temporal walk for the temporal Katz centrality introduced in
-\cite{grindrod11}, we have a new centrality measure.
-In the matrix form, the nonzero entries of $A^{[t_i]} A^{[t_{i+1}]}$ counts all the temporal paths of length $1$, and
-$A^{[t_i]}\cdots A^{[t_j]}$, where $i < j$ counts all the temporal paths of length $j -i$.
-For example, $A^{[1]}A^{[4]}$, $A^{[1]}A^{[1]}A^{[4]}$ and $A^{[1]}A^{[2]}A^{[3]}A^{[4]}$ are all paths of length 3.
-In the original Katz centrality, the `attenuation' factor $\alpha$ is imposed on the
-number of paths, i.e., longer paths has smaller effect to the overall rating.
-Hence the final result is the summation of all products of the form
-\[
-\alpha^k A^{[i]} \cdots A^{[i+k]}
-\]
-% Note this can not be written in \eqref{eq:katz}, as discussed in Section \ref{sec:temp-katz-centr}.
-
-Another definition of temporal walk was introduced by \cite{chen16}. Here
-both static edges and causal edges are considered.
-We can represent an evolving graph by a block adjacency matrix, as shown in Section \ref{sec:centr-block-adjac}.
-Centrality on this block matrix gives the importance of each node at all time stamps.
-We can average these rating at different time stamps to
-get the final rating.
-
-We review a few well-known measures of evolving graph centrality.
-(Design a simple example and discuss it in each case below.)
-
-% can not simply aggregate nodes: introduce wrong paths.
-
-\subsection{Temporal Katz Centrality and Communicability Betweenness Centrality}
-\label{sec:temp-katz-centr}
-
-The Katz Centrality is a measure of importance
-
-In \cite{grindrod11}, Grindrod et al. define a \emph{dynamic walk} of length $m$ from
-node $v_1$ to node $v_{w+1}$  as a sequence of edges
-$(v_1, v_2), (v_2, v_3), \ldots (v_w, v_{w+1})$ and a non-decreasing sequence of times
-$t_{r_1} \leq t_{r_2} \leq \cdots \leq t_{r_w}$ such that the adjacency matrix at time stamp
-$r_m$, i.e., $A_{i_m, i_{m+1}}^{[r_m]} \ne 0$.
-Note that in this definition the authors only take account of the static edges and the length of a dynamic walk is determined by the number of static edges.
-
-The Katz centrality is based on a sequence of matrix products
-\begin{equation}
-\label{eq:katz}
-Q = (I - \alpha A^{[0]})^{-1}(I - \alpha A^{[1]})^{-1} \cdots (I - \alpha A^{[M]})^{-1}.
-\end{equation}
-The $i$th row and column sums
-$$
-C_i^{broadcast} = \sum_{k=1}^n Q_{ik}, \quad C_i^{receive} = \sum_{k=1}^n Q_{ki}
-$$
-are the broadcast centrality and receive centrality of node $i$.
-
-Note that the $(i,j)$th element of adjacency matrix $A^k$ counts the only of paths from $i$ to $j$.
-To simulate a Katz centrality,
-the shortest path algorithms search through all possible paths between $i$ and $j$.
-
-\subsection{Temporal Betweenness and Closeness Centrality}
-\label{sec:temp-betw-centr}
-
-Recall that betweenness centrality of a node in a static graph is defined by counting the fraction of shortest paths that traverse it.
-We could extend
-betweenness centrality on evolving graphs by replacing shortest paths with temporal shortest paths \cite{nicosia13}.
-\begin{equation}
-  \label{eq:bet1}
-C_i^{betweenness} = \sum_{j \in V}\sum_{k \in V, k \ne j}\frac{\alpha_{jk}(i)}{\alpha_{jk}},
-\end{equation}
-where $\alpha_{jk}$ represents the number of temporal shortest paths from node $j$ to node $k$ and $\alpha_{jk}(i)$ represents the number of temporal shortest paths from node $j$ to node $k$ that pass through the node $i$.
-
-One may want to take into account the length of time a node passes a message. The temporal betweenness centrality of the node $i$ at time stamp $t_m$ is defined as
-\begin{equation}
-  \label{eq:bet2}
-  C_i^{betweenness}(t_m) = \sum_{j\ne i}\sum_{k\ne j, k\ne i}\frac{U_{j,k,t_m}(i)}{\alpha_{j,k}},
-\end{equation}
-where, as before, $\alpha_{j,k}$ represents the number of temporal shortest paths from $j$ to $k$ and $U_{j,k,t_m}(i)$ represents the number of temporal shortest paths from $j$ to $k$ in which node $i$ is traversed from
-the walk in the time stamp $t_m$ or a previous time stamp $t_{m-1}$. Then
-average temporal betweenness of node $i$ is then defined as
-$$
-  C_i^{betweenness} = \frac{1}{M}\sum_m C_i^{betweenness}(t_m).
-$$
-Note \eqref{eq:bet1} only takes account of static edges while \eqref{eq:bet2} takes account of both static edges and causal edges.
-
-% closeness centrality
-Similar to betweenness centrality, let $d_{ij}$ be the length of a temporal shortest walk from $i$ and $j$ in an evolving graph. Then
-the closeness centrality of a node $i$ is defined
-$$
-C_i^{closeness} = \frac{N-1}{\sum_j d_{ij}}.
-$$
-Note that this depends on how we define the length of temporal shortest walk. The closeness centrality can takes account of only static edges, only causal edges, or both.
-
-\subsection{Reverse Temporal Flows}
-\label{sec:reverse-temp-flows}
-
-We can not travel back in time. But reversing the direction of temporal flows can help
-identify the ``hub'' nodes or the source of the flows. The authority score of a page is
-proportional to its importance, and the hub score describes the quality of a page as a link collection of important related pages \cite{kleinberg99}.
-Indeed, reverse PageRank has
-been studied by \cite{bar08, fogaras03, gleich15}. In reverse PageRank we compute PageRank on the graph with reversed direction, i.e., reverse the direction of each edge $(i,j)$ to $(j, i)$.
-Fogaras \cite{fogaras03} shows that Reversed Page Rank scores express hub quality.
-
-Recall a time-preserving walk is a time-ordered sequence of active nodes. Here we define a \emph{reversed temporal walk} to be a reversed time-ordered sequence of active nodes, i.e.,
-$t_1 \ge t_2 \ge \cdots \ge t_m$.
-
-\subsection{Temporal PageRank}
-
-We consider two generalisation of pagerank: a block matrix one and a dense matrix one that is based on probability
+We believe we shouldn't not just penolaize old walks but the time span between two edges.
 
@@
 
-In this section, we vary the edge
-weights in both static and causal edges to study the impact of time-preserving paths on evolving graph centrality.
-We also compare evolving graph centrality with the aggregated static graph case to gain insight about the advantage of evolving graph model.
+\subsection{Random Evolving Graphs}
+\label{sec:random}
 
@@
 
-\subsection{Paper Keyword Tag Network}
-
-We tag our research articles by subjects.
-
-We can construct a time-dependent tag network by link tags in each articles. For example,
-suppose a paper $p_1$ has three tags $t_1$, $t_2$, and $t_3$, where $t_1$ is a superclass of $t_2$ and $t_3$.
-We link $t_2$ and $t_3$ in both direction and create a link from $t_1$ to $t_2$ and a link from $t_1$ to $t_3$.
-The time stamp of these edges is the published date of the paper.
+% \subsection{Paper Keyword Tag Network}
+%
+% We tag our research articles by subjects.
+%
+% We can construct a time-dependent tag network by link tags in each articles. For example,
+% suppose a paper $p_1$ has three tags $t_1$, $t_2$, and $t_3$, where $t_1$ is a superclass of $t_2$ and $t_3$.
+% We link $t_2$ and $t_3$ in both direction and create a link from $t_1$ to $t_2$ and a link from $t_1$ to $t_3$.
+% The time stamp of these edges is the published date of the paper.
 

### 2018-05-14 paper.tex
add pagerank example

@@
 % julia code implementation
-With the defintion of \texttt{temporal\_distance} introduced in Section \ref{sec:time-pres-paths}.
+With the definition of \texttt{temporal\_distance} introduced in Section \ref{sec:time-pres-paths}.
 We define the temporal Katz score of node $(i, t)$ as
@@
 function temporal_katz(g::AbstractEvolvingGraph,
-  v::TimeNode; alpha = 0.1, max_level = 5)
+  start::TimeNode; alpha = 0.1, max_level = 5)
     score = 0.
+    v = start
     fronter = [v]
@@
                 push!(next, v)
-              d = temporal_distance(v, u)
-              d += level
+                td = temporal_distance(start, u)
+                d = td + level
                 score += alpha^d
@@
 distance from $v$. The spatial distance is recorded in variable \texttt{level} and the temporal distance is calculated by
-\texttt{temporal\_distance}.
+\texttt{temporal\_distance}. The algorithm stops searching when \texttt{level} is larger or equal to \texttt{max\_level}.
 
 % example on 3 timestamp evolving graph
+For Figure \ref{}
 
 % compare the Katz in EvolvingGraphs.jl
-
-Let $A$ be an adjacency
-
-In \cite{grindrod11}, Grindrod et al. define a \emph{dynamic walk} of length $m$ from
-node $v_1$ to node $v_{w+1}$  as a sequence of edges
-$(v_1, v_2), (v_2, v_3), \ldots (v_w, v_{w+1})$ and a non-decreasing sequence of times
-$t_{r_1} \leq t_{r_2} \leq \cdots \leq t_{r_w}$ such that the adjacency matrix at time stamp
-$r_m$, i.e., $A_{i_m, i_{m+1}}^{[r_m]} \ne 0$.
-Note that in this definition the authors only take account of the static edges and the length of a dynamic walk is determined by the number of static edges.
-
-The Katz centrality is based on a sequence of matrix products
-\begin{equation}
-\label{eq:katz}
-Q = (I - \alpha A^{[0]})^{-1}(I - \alpha A^{[1]})^{-1} \cdots (I - \alpha A^{[M]})^{-1}.
-\end{equation}
-The $i$th row and column sums
-$$
-C_i^{broadcast} = \sum_{k=1}^n Q_{ik}, \quad C_i^{receive} = \sum_{k=1}^n Q_{ki}
-$$
-are the broadcast centrality and receive centrality of node $i$.
-
-Note that the $(i,j)$th element of adjacency matrix $A^k$ counts the only of paths from $i$ to $j$.
-To simulate a Katz centrality,
-the shortest path algorithms search through all possible paths between $i$ and $j$.
 

### 2018-05-14 paper.tex
finish katz centrality example

@@
 function temporal_katz(g::AbstractEvolvingGraph,
-  start::TimeNode; alpha = 0.1, max_level = 5)
+  start::TimeNode; alpha = 0.2, max_level = 10)
     score = 0.
@@
 \texttt{temporal\_distance}. The algorithm stops searching when \texttt{level} is larger or equal to \texttt{max\_level}.
+We set \texttt{alpha} to be $0.2$ and \texttt{max\_level} to be $10$. Then
+% example on 3 timestamp evolving graph
+for Figure \ref{fig:katz_eg2}, we have
+\begin{lstlisting}
+Dict{Any,Any} with 7 entries:
+  TimeNode(B, 2) => 1.0
+  TimeNode(B, 3) => 0.0
+  TimeNode(A, 2) => 3.58333
+  TimeNode(C, 1) => 1.06867
+  TimeNode(A, 3) => 1.0
+  TimeNode(B, 1) => 3.25373
+  TimeNode(C, 2) => 1.71667
+\end{lstlisting}
+The total scores at all time stamps are
+\begin{lstlisting}
+DataStructures.DefaultDict{Any,Any,Float64} with 3 entries:
+  "B" => 4.25373
+  "A" => 4.58333
+  "C" => 2.78533
+\end{lstlisting}
+Notice that $A$ is still the most important node in the network. However, now $B$ is considered more important
+than $C$. This is because we consider causal edges as well as static edges. Node $B$ is active at all three time stamps
+and more connected causally than node $C$.
 
-% example on 3 timestamp evolving graph
-For Figure \ref{}
-
-% compare the Katz in EvolvingGraphs.jl
+For Figure \ref{fig:katz_eg3}, we have
+\begin{lstlisting}
+Dict{Any,Any} with 7 entries:
+  TimeNode(C, 1)   => 1.06833
+  TimeNode(B, 100) => 0.0
+  TimeNode(C, 2)   => 1.70833
+  TimeNode(B, 2)   => 1.0
+  TimeNode(B, 1)   => 3.25367
+  TimeNode(A, 100) => 1.0
+  TimeNode(A, 2)   => 3.54167
+\end{lstlisting}
+The sum of node scores at each time stamp is
+\begin{lstlisting}
+DataStructures.DefaultDict{Any,Any,Float64} with 3 entries:
+  "B" => 4.25367
+  "A" => 4.54167
+  "C" => 2.77667
+\end{lstlisting}
+We see the scores of all three nodes are decreased when the last time stamp is $100$.
+Node $A$ is affected the most.
 

### 2018-05-15 paper.tex
include more experiment code

@@
 \draw [decorate,decoration={brace,amplitude=5pt},xshift=-4pt,yshift=0pt]
-(4,3) -- (-2,3) node [midway,yshift=-0.6cm]{ $2$};
+(4,3) -- (-2,3) node [midway,yshift=-0.6cm]{ $10$};
 \draw [decorate,decoration={brace,amplitude=5pt},xshift=-4pt,yshift=0pt]
@@
 \end{center}
-\caption{An evolving directed graph with 3 time stamps $1$, $2$ and $100$.
+\caption{An evolving directed graph with 3 time stamps $1$, $10$ and $100$.
 At each time stamp, the evolving graph is represented as a graph.
@@
 
-\begin{lstlisting}
+\begin{lstlisting}[caption={Temporal Katz Centrality of Single Node},label={lst:katz}]
 function temporal_katz(g::AbstractEvolvingGraph,
@@
 
-\subsection{Temporal Communicability Betweenness Centrality}
+\subsubsection{Temporal Resolvent Betweenness Centrality}
 
-% communicability from first principle
+Betweenness centrality measures the importance of a node as the ability to facilitate the communication between other nodes in the network.
+Commonly it is defined based on the shortest paths.
+However, key messages do not necessarily follow the shortest paths and so it makes senses to consider walks instead.
+Recall the $(i,j)$ entry of the resolvent matrix $(I - \alpha A)^{-1}$ provide information about the communication from $i$ to $j$. We could therefore define the resolvent betweenness for node $v$ as
+\begin{equation}
+  \sum_{i}\sum_j \frac{(I-\alpha A)^{-1}_{i,j} - (I - \alpha (A - E_v))^{-1}_{i,j}}{(I - \alpha A)^{-1}_{i,j}}, \quad i \ne j, i \ne v, j \ne v.
+\end{equation}
+where $E_v$ has non-zeros only in row and column $v$, and in the $v$th row and column has $1$ where $A$ has $1$.
+The matrix $A - E_i$ represents a graph with all edges involving the node $v$ removed.
+For $(I-\alpha A)^{-1}_{i,j}$ we could simply modify Listing \ref{lst:katz} so that it only accumulate scores when the end node is $j$.
+For the $(I - \alpha (A-E_v))^{-1}_{i,j}$ part, we can apply the above the same algorithm on a graph with node $v$ and related edges removed.
+\begin{lstlisting}
+function temporal_resolvent_betweenness(g1::EvolvingGraph,
+  g2::EvolvingGraph, v::TimeNode; alpha = 0.2, k = 10)
+    r = 0.
+    ns = active_nodes(g1)
+    for i in ns
+        for j in ns
+            if i != j && i != v && j != v
+                score1 = temporal_katz(g1, i, j, alpha = alpha, k = k)
+                score2 = temporal_katz(g2, i, j, alpha = alpha, k = k)
+                r += score1 == 0.0 ? 0 : (score1 - score2)/score1
+            end
+        end
+    end
+    return r
+end
+\end{lstlisting}
+For example, by removing node $C$ a time stamp $2$ from Figure \ref{fig:katz_eg2} we find
+the temporal resolvent betweenness score is $6.09$. While the temporal resolvent betweenness score
+of node $A$ at time stamp $3$ is $5.0$. This shows $(C,2)$ is more important than $(A,3)$.
+
+Now consider Figure \ref{fig:katz_eg3}. If we remove $(C,2)$, the temproal resolvent betweenness score is $4.20$.
+The analysis for temporal communicability betweenness centrality is similar.
 
@@
 
-\begin{wz}
-  We may also consider betweenness centrality.
-\end{wz}
-
-Recall that betweenness centrality of a node in a static graph is defined by counting the fraction of shortest paths that traverse it.
-We could extend
-betweenness centrality on evolving graphs by replacing shortest paths with temporal shortest paths \cite{nicosia13}.
-\begin{equation}
-  \label{eq:bet1}
-C_i^{betweenness} = \sum_{j \in V}\sum_{k \in V, k \ne j}\frac{\alpha_{jk}(i)}{\alpha_{jk}},
-\end{equation}
-where $\alpha_{jk}$ represents the number of temporal shortest paths from node $j$ to node $k$ and $\alpha_{jk}(i)$ represents the number of temporal shortest paths from node $j$ to node $k$ that pass through the node $i$.
-
-One may want to take into account the length of time a node passes a message. The temporal betweenness centrality of the node $i$ at time stamp $t_m$ is defined as
-\begin{equation}
-  \label{eq:bet2}
-  C_i^{betweenness}(t_m) = \sum_{j\ne i}\sum_{k\ne j, k\ne i}\frac{U_{j,k,t_m}(i)}{\alpha_{j,k}},
-\end{equation}
-where, as before, $\alpha_{j,k}$ represents the number of temporal shortest paths from $j$ to $k$ and $U_{j,k,t_m}(i)$ represents the number of temporal shortest paths from $j$ to $k$ in which node $i$ is traversed from
-the walk in the time stamp $t_m$ or a previous time stamp $t_{m-1}$. Then
-average temporal betweenness of node $i$ is then defined as
-$$
-  C_i^{betweenness} = \frac{1}{M}\sum_m C_i^{betweenness}(t_m).
-$$
-Note \eqref{eq:bet1} only takes account of static edges while \eqref{eq:bet2} takes account of both static edges and causal edges.
-
 % closeness centrality
-Similar to betweenness centrality, let $d_{ij}$ be the length of a temporal shortest walk from $i$ and $j$ in an evolving graph. Then
+Let $d_{ij}$ be the length of a temporal shortest walk from $i$ and $j$ in an evolving graph. Then
 the closeness centrality of a node $i$ is defined
@@
 Note that this depends on how we define the length of temporal shortest walk. The closeness centrality can takes account of only static edges, only causal edges, or both.
+The definition of temporal closeness centrality is similar to temporal katz. The only difference is that here we traverse the shortest paths not just walks on evolving graphs.
+
+\begin{lstlisting}
+function temporal_closeness(g::AbstractEvolvingGraph, start::TimeNode)
+  v = start
+  level = Dict(v => 0)
+  i = 1
+  fronter = [v]
+  while length(fronter) > 0
+      next = []
+      for u in fronter
+          for v in forward_neighbors(g, u)
+              if !(v in keys(level))
+                  td = temporal_distance(start, u)
+                  level[v] = i + td
+                  push!(next, v)
+              end
+          end
+      end
+      fronter = next
+      i += 1
+  end
+
+  total_scores = sum(values(level))
+  return total_scores > 0. ? (length(level) - 1)/total_scores : 0.
+end
+\end{lstlisting}
+For Figure \ref{fig:katz_eg2} the scores are
+\begin{lstlisting}
+Dict{Any,Any} with 7 entries:
+TimeNode(B, 3) => 0.0
+TimeNode(B, 1) => 0.27027
+TimeNode(A, 3) => 1.0
+TimeNode(B, 2) => 1.0
+TimeNode(C, 1) => 0.259259
+TimeNode(A, 2) => 0.538462
+TimeNode(C, 2) => 0.416667
+\end{lstlisting}
+For Figure \ref{fig:katz_eg3}, the scores are
+\begin{lstlisting}
+Dict{Any,Any} with 7 entries:
+TimeNode(B, 100) => 0.0
+TimeNode(A, 2)   => 0.0636364
+TimeNode(A, 100) => 1.0
+TimeNode(C, 2)   => 0.0458716
+TimeNode(B, 1)   => 0.0746269
+TimeNode(C, 1)   => 0.0564516
+TimeNode(B, 2)   => 1.0
+\end{lstlisting}
+
+The analysis for temporal communicability betweenness centrality is similar.
 
@@
 
-We derive two generalization of PageRank on evolving graphs.
-The first idea is based on reverse temporal flows.
+We derive a generalization of PageRank on evolving graphs.
+The first idea is based on reverse temporal flows and block adjacency matrix.
 
@@
 
-We consider two generalisation of pagerank: a block matrix one and a dense matrix one that is based on probability
+We derive the block google matrix as a combination of block matrix $A$ and its transpose $A^T$.
 
-We believe we shouldn't not just penolaize old walks but the time span between two edges.
+The block google matrix is defined as
+
+\begin{lstlisting}
+function block_google_matrix(g::IntAdjacencyList; alpha = 0.85, balance = 0.75)
+  A = full(block_adjacency_matrix(g))
+  A = balance * A + (1-balance) * A'
+  N, N = size(A)
+  p = ones(N)/N
+  dangling_weights = p
+  dangling_nodes = find(x->x==0, sum(A,2))
+
+  for node in dangling_nodes
+      A[node,:] = dangling_weights
+  end
+  A ./= sum(A,2)
+  return alpha * A .+ (1- alpha) * p
+end
+\end{lstlisting}
+
+We find the ranking for Figure \ref{}
+
+\begin{lstlisting}
+9-element Array{Complex{Float64},1}:
+ 0.12278
+0.254264
+0.0533627
+ 0.36275
+0.350713
+0.406792
+0.0533627
+0.524112
+0.468848
+\end{lstlisting}
 
@@
 
+We test the influence of time on evolvign graph centralities.
+
 \subsection{Random Evolving Graphs}
 \label{sec:random}
+
+Note the random evolving graphs are conducted using \texttt{IntAdjacencyList}, which gives better performance for
+forward\_neighbors.
+
+We generate a random evolving graph with $100$ nodes and $9771$ static edges and $5$ time stamps.
+Here are the top $10$ nodes we find using the Katz Centrality
+
+Since we only are interested in the top nodes.
+
+\begin{tabular}{ l | c }
+  \hline
+  node & score \\
+  334 & 0.152288 \\
+  9 & 0.137403 \\
+  428 & 0.126793 \\
+  164 & 0.121582 \\
+  250 & 0.117862 \\
+  35 & 0.117627 \\
+  291 & 0.105793 \\
+  414 & 0.0975953 \\
+  123 & 0.096394 \\
+  478 & 0.0945754 \\
+  \hline
+\end{tabular}
+
+We find identify the top $10$
+
+We test temporal Katz centrality,  for top $20$
+temporal closeness, and temporal pagerank.
+by varing the influence of temporal distance.
+
+Katz score | temproal katz at with time influence 0.1 | temproal katz with time influence 1.0
+
+Closeness with time influence 0.1 | closeness with time influence 1.0
+
+PageRank with time influence 0.1 | PageRank with time influence 1.0
 
@@
 create a undirected edge (or two directed edges) between two authors if they have coauthored at least one paper.
-(add results here.)
 
-A second network is constructed by linking leading authors in different papers whose
-ideas are similar. The resulting network represent the connectivity of ideas in all the research papers in the database.
+Some experiments as above.
 
-(add results here.)
+Katz score | temproal katz at with time influence 0.1 | temproal katz with time influence 1.0
 
-% \subsection{Paper Keyword Tag Network}
-%
-% We tag our research articles by subjects.
-%
-% We can construct a time-dependent tag network by link tags in each articles. For example,
-% suppose a paper $p_1$ has three tags $t_1$, $t_2$, and $t_3$, where $t_1$ is a superclass of $t_2$ and $t_3$.
-% We link $t_2$ and $t_3$ in both direction and create a link from $t_1$ to $t_2$ and a link from $t_1$ to $t_3$.
-% The time stamp of these edges is the published date of the paper.
+Closeness with time influence 0.1 | closeness with time influence 1.0
+
+PageRank with time influence 0.1 | PageRank with time influence 1.0
 
@@
 
-To write later.
+We describe in details the generalizartion of centrality algorithms for evolving graphs.
+We introduce the generalization of PageRank centrality.
 

### 2018-05-15 simulations/temporal_closeness.jl

@@ -1,0 +1,23 @@
+function temporal_closeness(g::Union{AbstractEvolvingGraph, IntAdjacencyList}, start::Union{TimeNode,Tuple{Int,Int}})
+    v = start
+    level = Dict(v => 0)
+    i = 1
+    fronter = [v]
+    while length(fronter) > 0
+        next = []
+        for u in fronter
+            for v in forward_neighbors(g, u)
+                if !(v in keys(level))
+                    td = temporal_distance(start, u)
+                    level[v] = i + td
+                    push!(next, v)
+                end
+            end
+        end
+        fronter = next
+        i += 1
+    end
+
+    total_scores = sum(values(level))
+    return total_scores > 0. ? (length(level) - 1)/total_scores : 0.
+end

### 2018-05-15 simulations/temporal_katz_betweenness.jl

@@ -1,0 +1,78 @@
+function temporal_distance(v1::TimeNode, v2::TimeNode, beta::Real = 0.1)
+    return beta* abs(node_timestamp(v1) - node_timestamp(v2))
+end
+function temporal_distance(v1::Tuple{Int,Int}, v2::Tuple{Int,Int}, beta::Real = 0.1)
+    return beta * abs(v1[2] - v2[2])
+end
+
+
+function temporal_katz(g::IntAdjacencyList, start::Tuple{Int,Int}; alpha = 0.1, k = 10)
+    score = 0.
+    v = start
+    fronter = [v]
+    level = 0
+    while level < k
+        next = []
+        for u in fronter
+            fn = forward_neighbors(g, u)
+            fn = sample(fn, min(100, length(fn)), replace=false)
+            println("number of neighbors $(length(fn))")
+            for v in fn
+                push!(next, v)
+                td = temporal_distance(start, u)
+                d = td + level
+
+                score += alpha^d
+            end
+        end
+        fronter = next
+        level += 1
+    end
+    return score
+end
+
+
+
+
+function temporal_katz(g::AbstractEvolvingGraph, start_node::TimeNode, end_node::TimeNode; alpha = 0.2, k = 10)
+    score = 0.
+    v = start_node
+    fronter = [v]
+    level = 0
+    while level < k
+        next = []
+        for u in fronter
+            fn = forward
+            for v in forward_neighbors(g, u)
+                push!(next, v)
+                if u == end_node
+                    td = temporal_distance(start_node, u)
+                    d = td + level
+                    score += alpha^d
+                end
+            end
+        end
+        fronter = next
+        level += 1
+    end
+    return score
+end
+
+
+function temporal_resolvent_betweenness(g1::EvolvingGraph, g2::EvolvingGraph, v::TimeNode; alpha = 0.2, k = 10)
+    r = 0.
+    ns = active_nodes(g1)
+    for i in ns
+        for j in ns
+            if i != j && i != v && j != v
+
+                score1 = temporal_katz(g1, i, j, alpha = alpha, k = k)
+                score2 = temporal_katz(g2, i, j, alpha = alpha, k = k)
+#                 println("From node $i to node $j")
+#                 println("score1 $score1 and score2 $score2")
+                r += score1 == 0.0 ? 0 : (score1 - score2)/score1
+            end
+        end
+    end
+    return r
+end

### 2018-05-15 simulations/temporal_pagerank.jl

@@ -1,0 +1,21 @@
+function block_google_matrix(g::IntAdjacencyList; alpha = 0.85, balance = 0.75)
+    A = full(block_adjacency_matrix(g))
+    A = balance * A + (1-balance) * A'
+    N, N = size(A)
+    p = ones(N)/N
+    dangling_weights = p
+    dangling_nodes = find(x->x==0, sum(A,2))
+
+    for node in dangling_nodes
+        A[node,:] = dangling_weights
+    end
+    A ./= sum(A,2)
+    return alpha * A .+ (1- alpha) * p
+end
+
+function temporal_pagerank(g::AbstractEvolvingGraph)
+    A = block_google_matrix(g)
+    F = eigfact(A')
+    println("F values $(F[:values])")
+    return F[:vectors][:,1]
+end

### 2018-05-15 simulations/test_JMLR.jl

@@ -1,18 +1,20 @@
 # testing evolving graph katz centrality on author network data
 using EvolvingGraphs
+using EvolvingGraphs.Centrality
 import EzXML
 
 jmlr_dict = Dict()
 
 # load graph data at each year
 # form evolving graph
-eg= evolving_graph(String, Int)
+g = EvolvingGraph{Node{String}, Int}()
+
 for year in range(2001, 17)
-    g = load_graphml("jmlr_$(year).graphml")
-    add_graph!(eg, g, year)
+    sg = load_graphml("jmlr_$(year).graphml")
+    add_graph!(g, sg, year)
 end
 
-rating = katz_centrality(eg)
+rating = katz(g, 0.1, 0.01; mode = :receive)
 
 sorted_authors = sort(rating, by = x -> x[2], rev = true)
 

### 2018-05-15 simulations/test_random.jl

@@ -1,0 +1,6 @@
+using EvolvingGraphs
+using EvolvingGraphs.Centrality
+
+include("temporal_katz_betweenness.jl")
+include("temporal_closeness.jl")
+include("temporal_pagerank.jl")

### 2018-05-15 paper.tex
rewrite abstract and intro part

@@
 
-\title{A Closer Look at Network Flow on Evolving Graphs}
+\title{A Closer Look at Network Flow on Evolving Graph Centrality}
 
@@
 \begin{abstract}
-This paper studies evolving graph centrality from the perspective of time-preserving paths.
-We describe time-preserving paths based on two dimensions of variation, namely static edges and causal edges.
+This paper studies the influence of the temporal information in an evolving graph on the node centrality scores.
+In particular, we look at four important centrality measures, namely Katz centrality,
+Resolvent Betweenness centrality, Closeness centrality, and PageRank.
 
-A time-preserving walk on evolving graphs makes implicit assumptions about the type of edges that a walk traverses.
-For example, the walk can count only static edges or can take account of both static edges and causal edges.
-In addition, the length of a time-preserving walk can be either spatial or temporal.
-
-We study the impact of different time-preserving paths on node centrality by varying the edge weights of static and causal edges.
-We also compare evolving graph centrality with the aggregated static graph case to gain insight about the advantage of an evolving graph model.
-We construct an evolving coauthor network from a collection of research papers for the experiments.
-
-We observe that time span has an important impact on evolving graph centrality. Build on this idea,
-we introduce more general definitions of walk and shortest path based centralities.
-Generalizing PageRank on evolving graphs is a hard problem.
-We provide two definitions of evolving graph centrality.
-Our experiments indicate our algorithm is effective.
-
+We derive evolving graph centrality measures from the perspective of network flow and
+observe that the amount of temporal distance between nodes has an important impact on the final evolving graph centrality scores, especially on the top ranked nodes.
+Build on this idea, we introduce a generalised PageRank on evolving graph that is based on two ideas:
+reverse network flow and block adjacency matrix.
+We conduct our experiments on random evolving graphs and the JMLR co-author networks to illustrate our idea.
 \end{abstract}
@@
 However, we cannot travel back in time or even send a message to the past.
-To traverse an evolving graph, a.k.a a time-dependent graph, one has to consider order of time stamps.
-In particular, a walk on an evolving graph needs to be time-preserving, meaning a node can not pass a massage (through an edge) to a node at a earlier time.
+To traverse an evolving graph, a.k.a a time-dependent graph, one has to consider order of time stamps. In particular, a walk on an evolving graph needs to be time-preserving, meaning we
+can not pass a massage (through an edge) to a node at a earlier time.
+Time-preversing walks and paths are very important concepts for
+network flow on evolving graphs.
 
@@
 
-In general, a node $v$ on $G^{[t]}$ is represented by a pair $(v, t)$, where $t$ is the time stamp of the temporal slice.
+In general, a node $v$ on $G^{[t]}$ is represented by a pair $(v, t)$, where $t$ is the time stamp of the graph $G^{[t]}$.
 A sequence of interactions between users form a walk. Suppose $A$ sent a message to $B$ at time stamp $t_1$
@@
 
-A time-respecting walk is a sequence of $\langle (v_1, t_1), (v_2, t_2), \ldots ,(v_m, t_m)\rangle$, where $t_1 \le t_2 \le \cdots \le t_n$ are the corresponding time stamps.
+A time-respecting walk is a sequence of nodes $\langle (v_1, t_1), (v_2, t_2), \ldots ,(v_m, t_m)\rangle$, where $t_1 \le t_2 \le \cdots \le t_n$ are the corresponding time stamps.
 If $t_i = t_j$, then $\langle (v_i, t_i), (v_j, t_j) \rangle$ is an edge where both nodes are on the same temporal slice,  otherwise it is an edge linking nodes from different temporal slices.
@@
 Another approach is to define evolving graph centrality algorithms using time-respecting paths.
-This approach is applicable to algorithms that are defined using paths or paths.
+This approach is applicable to algorithms that are defined using shortest paths.
 
@@
 
-In Higham's following up papers, time delay is considered as alternative format of Katz centrality.
-But the impact of temporal is left unconsidered.
+% In Higham's following up papers, time delay is considered as alternative format of Katz centrality.
+% But the impact of temporal is left unconsidered.
 We studied the problem on centrality from two different types of centrality: one that depends on matrix unfolding and one that depends on temporal walk.
@@
 % our contribution this paper
-Inspired by Borgatti's work \cite{borgatti05} on simulating different flow process on static graphs, we
-
-Borgatti noted in  that the manner of traffic flow entails a new way to think about centrality.
-where the author simulate different traffic flows to study centrality.
-
+Borgatti \cite{borgatti05} noted that the manner of traffic flow entails a new way to think about centrality.
 In particularly, the importance of a node in a network can not be determined without reference to how traffic flows through the network.
-To develop a centrality algorithm on evolving graphs, one has to consider the manner of temporal traffic flow.
-A time-preserving walk on evolving graphs can be described by static edges, causal edges, or both.
-
+Inspired by this idea, we simulate network flows in evolving graphs to measure the centrality scores.
 % Grindrod et al.'s definition of dynamic walk \cite{grindrod11} only counts static edges.
@@
 Chen and Zhang \cite{chen16} considered both static edges and causal edges in their definition of temporal walk.
-
 The aims of this paper are as follows.
-First, to identify the type of time-preserving walk in a list of common evolving graph centrality measures.
-Second, to vary static and causal edge weights and analyze the impact on selected measures of centrality.
-Third, to solve a real world problem using evolving graph centrality: identify key authors in an evolving coauthor network.
+First, to derive important evolving graph centrality from first principle via network flow.
+Second, to study the impact of temporal distance between nodes on centrality.
+Third, to generalise PageRank on evolving graphs.
 We carry out the experiment using the Julia dynamic network analysis package
@@
 
-We let $G_n = \langle G^{[1]}, G^{[2]}, \ldots, G^{[n]} \rangle$ be an evolving graph
+We let $G_generalisede G^{[1]}, G^{[2]}, \ldots, G^{[n]} \rangle$ be an evolving graph
 and $A^{[1]}, A^{[2]}, \dots A^{[n]}$ be the corresponding adjacency matrices.

### 2018-05-15 paper.tex
update the temporal path and walk part

@@
 
-We let $G_generalisede G^{[1]}, G^{[2]}, \ldots, G^{[n]} \rangle$ be an evolving graph
+We let $G_n = \langle G^{[1]}, G^{[2]}, \ldots, G^{[n]} \rangle$ be an evolving graph
 and $A^{[1]}, A^{[2]}, \dots A^{[n]}$ be the corresponding adjacency matrices.
@@
 If we reverse the time of communication between day $1$ and $3$, i.e., $B$ shares a new idea with $C$ on day $1$ and $A$ shares a new idea with $B$ on day $3$.
-Then the idea $A$ had on day $3$ can not pass to $C$ in this case.
+Then in this case the idea $A$ had on day $3$ can not pass to $C$.
 This is illustrated in Figure \ref{fig:katz_eg2}.
@@
 Notice the rating of $A$ decreased as its influence is not as important as in Figure \ref{fig:katz_eg}.
-
 % does not take account of walks in a long time. cost in time
-If the final communication between $A$ and $B$ are not on day $3$ but on day $100$, as shown in Figure \ref{fig:katz_eg3},
-we would expect the centrality ratings to change. However, according to \eqref{eq:q}, ratings are unchanged.
+If the communication between $A$, $B$, and $C$ are not on three consecutive days
+but on day $1$, day $10$, and day $100$, as shown in Figure \ref{fig:katz_eg3},
+we would expect the centrality scores to change. However, according to \eqref{eq:q}, scores are unchanged.
 We notice that the generalised Katz centrality on evolving graphs only takes account of the edges at each time stamp but not the communication time between edges at different time stamps.
@@
 The definition of centrality depends on the manner in which traffic flows through a network \cite{borgatti05}.
-Time-preserving walks induce temporal Katz centrality and temporal closeness Centrality while time-preserving paths
-induce betweenness centrality and closeness centrality.
+Time-preserving walks induce temporal Katz centrality and temporal closeness centrality while time-preserving paths induce betweenness centrality and closeness centrality.
 
-We now describe time-preserving paths in more detail. We follow the definition of
-\emph{evolving graph}, \emph{temporal node} and \emph{active node} in \cite{chen16}.
+We now describe evolving graph network flow in more details. We follow the definition of
+\emph{evolving graph} in \cite{chen16}.
 
@@
 $G_n = \langle G^{[1]}, G^{[2]},  \ldots ,G^{[n]} \rangle$ with associated time stamps
-$t_1, t_2, \ldots, t_n$ respectively. Each $G^{[t]} = (V^{[t]}, E^{[t]})$ represents a (static) graph labeled by a time t.
+$t_1, t_2, \ldots, t_n$ respectively. Each $G^{[t]} = (V^{[t]}, E^{[t]})$ represents a (static) graph labelled by a time t.
 \end{definition}
@@
 Note the node sets $V^{[t]}$ can change over time, i.e., nodes may appear or disappear at a particular time stamp.
-For example, in Figure \ref{fig:eg_shortest_walk}, at time stamp $t_1$, $V^{[1]} = \langle 1, 2 \rangle$ and $E^{[1]} = \langle (1,2) \rangle$.
+For example, in Figure \ref{fig:eg_shortest_walk}, at time stamp $1998$, $V^{[1998]} = \langle 1, 2 \rangle$ and $E^{[1998]} = \langle (1,2) \rangle$.
 Each graph $G^{[t]}$ can be represented by its adjacency matrix $A^{[t]}$.
@@
 
-If we use this definition of temporal walk for the temporal Katz centrality introduced in
-\cite{grindrod11}, we have a new centrality measure.
-In the matrix form, the nonzero entries of $A^{[t_i]} A^{[t_{i+1}]}$ counts all the temporal paths of length $1$, and
-$A^{[t_i]}\cdots A^{[t_j]}$, where $i < j$ counts all the temporal paths of length $j -i$.
-For example, $A^{[1]}A^{[4]}$, $A^{[1]}A^{[1]}A^{[4]}$ and $A^{[1]}A^{[2]}A^{[3]}A^{[4]}$ are all paths of length 3.
+If we only measure the temporal difference in a temporal walk, we have a new definition of Katz centrality.
+In the matrix form, the nonzero entries of $A^{[t_i]} A^{[t_{i+1}]}$ counts all the temporal walks of length $1$, and
+$A^{[t_i]}\cdots A^{[t_j]}$, where $i < j$ counts all the temporal walks of length $j -i$.
+For example, $A^{[1]}A^{[4]}$, $A^{[1]}A^{[1]}A^{[4]}$ and $A^{[1]}A^{[2]}A^{[3]}A^{[4]}$ are all walks of length 3.
 In the original Katz centrality, the `attenuation' factor $\alpha$ is imposed on the
@@
 \]
-% Note this can not be written in \eqref{eq:katz}, as discussed in Section \ref{sec:temp-katz-centr}.
+Note this can not be written in \eqref{eq:q} as discussed in Section \ref{sec:temp-katz-centr}.
 
-Another definition of temporal walk was introduced by \cite{chen16}. Here
-both static edges and causal edges are considered.
+% Another definition of temporal walk was introduced by \cite{chen16}. Here
+% both static edges and causal edges are considered.
 We can represent an evolving graph by a block adjacency matrix, as shown in Section \ref{sec:centr-block-adjac}.
@@
 We can average these rating at different time stamps to
-get the final rating.
+% get the final rating.
 
@@
 
-It is natural to define the length of a walk on a static graph as the number of nodes travelled through the walk.
-For the weighted graph case, the length of a walk is the total weight of all the edges in the walk.
-We observe that static edges link nodes in space while causal edges link nodes in time.
-Hence we would like to distinguish temporal distance from spatial distance on an evolving graph: the length of a static edge is equal to the edge weight (or $1$ in the unweighted graph case); the length of a causal edge is the time distance between the two nodes.
-In the simplest case, the time-respecting walk
-$\langle (1, t_1) ,(2, t_1) , (2, t_3), (3, t_3)\rangle$ in Figure \ref{fig:eg_shortest_walk} has length $4$ in total because two static edges $\langle (1, t_1) (2, t_1) \rangle$ and $\langle (2, t_3), (3, t_3) \rangle$ have length one, whereas $\langle (2, t_1) (2, t_3) \rangle$ traverse $2$ time stamps so has length $2$.
-
 \begin{definition}
@@
 the $i$th row or the $i$th column of $A^{[t]}$ has at least one none-zero entry.
+
+ \begin{definition}
+ A \textbf{static edge} $\langle (v_i, t), (v_j, t)\rangle$ is a pair of elements of $V^{[t]}$, i.e., $v_i \in V^{[t]}$ and
+ $v_j \in V^{[t]}$.
+  A \textbf{causal edge} $\langle (v, t_i), (v, t_j)\rangle$ is a pair of the same node at different time stamps.
+ \end{definition}
+
+ For example, in Figure \ref{fig:eg_shortest_walk}
+ $\langle (1, 1998), (2, 1998) \rangle$ is a static edge at time stamp $1998$ and $\langle (3, 1999), (3, 2018) \rangle$ is a causal edge between time stamp $1999$ and time stamp $2018$.
+ The difference between static edges and causal edges were first explicitly considered in \cite{chen16}.
+
+ We can denote a \emph{weighted static edge} as $\langle (v_i, t), (v_j, t), w_s \rangle$ and a \emph{weighted causal edge} as $\langle (v, t_i), (v, t_j), w_t \rangle$.
+ Here $w_s$ represents the spatial distance between the two nodes $v_i$ and $v_j$; $w_t$ represents the
+ temporal distance of $v$ at different time stamps.
+ In Figure \ref{fig:eg_shortest_walk}, the black arrows represent static edges and the dotted arrows represent causal edges.
+ Suppose we assign all the static edge weight to $1$ and
+ let the causal edge weight be the number of time stamps between the pair of nodes. Then in Figure \ref{fig:eg_shortest_walk}
+ the edge weight between $(1, 1998)$ and $(2, 1998)$ is $1$ and the edge weight between $(2, 1998)$ and $(2, 2018)$ is $10$.
 In general, a time-preserving walk can be defined as follows.
@@
 
-Note $\langle (v_i, t_i), (v_j, t_i) \rangle$ represents a static edge on graph $G^{[t_i]}$ while $\langle (v_i, t_i), (v_i, t_j) \rangle$ represents a causal edge from time stamp $t_i$ to time stamp $t_j$.
+It is natural to define the length of a walk on a static graph as the number of nodes travelled through the walk.
+For the weighted graph case, the length of a walk is the total weight of all the edges in the walk.
+We observe that static edges link nodes in space while causal edges link nodes in time.
+Hence we would like to distinguish temporal distance from spatial distance in an evolving graph: we let the length of a static edge be one and the length of a causal edge be the temporal distance between the two nodes.
+In the simplest case, the time-respecting walk
+$\langle (1, 1998) ,(2, 1998) , (2, 2018), (3, 2018)\rangle$ in Figure \ref{fig:eg_shortest_walk} has length $12$ in total because two static edges $\langle (1, 1998) (2, 1998) \rangle$ and $\langle (2, 2018), (3, 2018) \rangle$ each have length one, and $\langle (2, 1998) (2, 2018) \rangle$
+traverse $10$ time stamps and thuse has length $10$.
 
-\begin{definition}
-A \textbf{static edge} $\langle (v_i, t), (v_j, t)\rangle$ is a pair of elements of $V^{[t]}$, i.e., $v_i \in V^{[t]}$ and
-$v_j \in V^{[t]}$.
- A \textbf{causal edge} $\langle (v, t_i), (v, t_j)\rangle$ is a pair of the same node at different time stamps.
-\end{definition}
-
-We can denote a \emph{weighted static edge} as $\langle (v_i, t), (v_j, t), w_s \rangle$ and a \emph{weighted causal edge} as $\langle (v, t_i), (v, t_j), w_t \rangle$.
-Here $w_s$ represents the spatial distance between the two nodes $v_i$ and $v_j$; $w_t$ represents the
-temporal distance of $v$ at different time stamps.
-In Figure \ref{fig:eg_shortest_walk}, the black arrows represent static edges and the dotted arrows represent causal edges.
-Suppose we assign all the static edge weight to be $1$ and
-assign the causal edge to be the number of time stamps between the pair. Then in Figure \ref{fig:eg_shortest_walk}
-the edge weight between $(1, t_1)$ and $(2, t_1)$ is $1$ and the edge weight between $(2, t_1)$ and $(2, t_3)$
- is $2$.
-
- For example, in Figure \ref{fig:eg_shortest_walk}
- $\langle (1, t_1), (2, t_1) \rangle$ is a static edge at time stamp $t_1$ and $\langle (3, t_2), (3, t_3) \rangle$ is a causal edge between time stamp $t_2$ and time stamp $t_3$.
- The difference between static edges and causal edges were first explicitly considered in \cite{chen16}.
-
-A time-preserving walk can traverse both causal edges and static edges.
-We will see in the next section that evolving centrality measures make implicit assumptions about the type of edges in the
-time-preserving walk that is used.
-
-The following function measure the temporal distance between two active nodes in an evolving graph.
+A time-preserving walk (and path) can traverse both causal edges and static edges.
+The following Julia function measures the temporal distance between two active nodes in an evolving graph.
 
@@
                            v2::TimeNode, beta::Real = 1.)
-  return node_key(v1) == node_key(v2) ?
-  beta* abs(node_timestamp(v1) - node_timestamp(v2)) : 0
+  beta* abs(node_timestamp(v1) - node_timestamp(v2))
 end
 \end{lstlisting}
-which means if two active nodes have the same key name, the temporal distance is the difference between their time stamps.
+which means the temporal distance is the difference between their time stamps scaled a hyper-parameter
+\texttt{beta}.
 
@@
 
-Now consider Figure \ref{fig:katz_eg3}. If we remove $(C,2)$, the temproal resolvent betweenness score is $4.20$.
+Now consider Figure \ref{fig:katz_eg3}. If we remove $(C,2)$, the temporal resolvent betweenness score is $4.20$.
 The analysis for temporal communicability betweenness centrality is similar.
@@
 
-Katz score | temproal katz at with time influence 0.1 | temproal katz with time influence 1.0
+Katz score | temporal katz at with time influence 0.1 | temporal katz with time influence 1.0
 

### 2018-05-15 paper.tex
update temporal katz and temporal resolvent betweenness section

@@
 
-\title{A Closer Look at Network Flow on Evolving Graph Centrality}
+\title{A Closer Look at Network Flow on Evolving Graphs}
 
@@
 % current evolving graph centrality approach
-To generalize centrality measures for evolving graphs, there are two common approaches.
+To generalize centrality measures for evolving graphs there are two common approaches.
 First, we could exploit the fact that matrix product of adjacency matrices at different time stamps counts the number of dynamic walks in an evolving graph.
@@
 the Katz Centrality \cite{estrada09} and Communicability Betweenness \cite{alsayed15}.
-Second, we could generalize the definition of shortest paths as shortest temporal paths and replace shortest paths in centrality measures with shortest temporal paths.
+Second, we could generalize the definition of shortest paths as shortest temporal paths and replace shortest paths in centrality measures with shortest temporal paths where possible.
 This way we can define temporal betweenness centrality and temporal closeness centrality \cite{nicosia13}.
@@
 % our approach
-We observe both approaches ignore the communication time between edges at different time stamps, i.e., the time gap between different graph slices.
-We take account of this communication time by deriving centrality measures from original ideas and show communication time has important impact on the final rating (and ranking).
-We note that our goal is not about providing faster centrality algorithms which is out of the scope of this paper.
+We observe both approaches ignore the communication time between edges at different time stamps, i.e., the time gap between different (static) graph slices.
+We take account of this communication time by deriving centrality measures from the original theses of the ideas and show communication time has important impact on the final node ratings (and rankings).
+We note that our goal is not about providing efficient centrality algorithms which is out of the scope of this paper.
 
@@
                 push!(next, v)
+                if node_key(v) != node_key(u)
                   td = temporal_distance(start, u)
@@
             end
+        end
         fronter = next
@@
     end
-    return score
+    return score / num_edges(g)
 end
@@
 % explain the code
-The algorithm \texttt{temporal\_katz} performs breadth first search (BFS) starting at \texttt{TimeNode} $v$, which represent a node at a specific time stamp \footnote{See also \url{https://etymoio.github.io/EvolvingGraphs.jl/latest/base.html#EvolvingGraphs.TimeNode}}.
+The algorithm \texttt{temporal\_katz} performs a breadth first search (BFS) on evolving graph $g$ that
+starts at \texttt{TimeNode} $v$, which represents a node at a specific time stamp \footnote{See also \url{https://etymoio.github.io/EvolvingGraphs.jl/latest/base.html#EvolvingGraphs.TimeNode}}.
 For each \texttt{TimeNode} $v$, we accumulate the influence of linked nodes according to their spatial and temporal
@@
 \begin{lstlisting}
-Dict{Any,Any} with 7 entries:
-  TimeNode(B, 2) => 1.0
+  TimeNode(A, 2) => 0.466667
+  TimeNode(A, 3) => 0.2
+  TimeNode(B, 2) => 0.0
   TimeNode(B, 3) => 0.0
-  TimeNode(A, 2) => 3.58333
-  TimeNode(C, 1) => 1.06867
-  TimeNode(A, 3) => 1.0
-  TimeNode(B, 1) => 3.25373
-  TimeNode(C, 2) => 1.71667
+  TimeNode(B, 1) => 0.202347
+  TimeNode(C, 1) => 0.0117333
+  TimeNode(C, 2) => 0.293333
 \end{lstlisting}
@@
 \begin{lstlisting}
-DataStructures.DefaultDict{Any,Any,Float64} with 3 entries:
-  "B" => 4.25373
-  "A" => 4.58333
-  "C" => 2.78533
+  "A" => 0.666667
+  "B" => 0.202347
+  "C" => 0.305067
 \end{lstlisting}
-Notice that $A$ is still the most important node in the network. However, now $B$ is considered more important
-than $C$. This is because we consider causal edges as well as static edges. Node $B$ is active at all three time stamps
-and more connected causally than node $C$.
+Notice that $A$ is the most important node in the evolving graph and $C$ is the second most important node.
+Thus the ranking agrees with the Katz centrality rankings in Section \ref{sec:motivation}.
 
@@
 \begin{lstlisting}
-Dict{Any,Any} with 7 entries:
-  TimeNode(C, 1)   => 1.06833
+  TimeNode(A, 10)  => 0.458333
+  TimeNode(A, 100) => 0.2
+  TimeNode(B, 1)   => 0.2
+  TimeNode(B, 10)  => 0.0
   TimeNode(B, 100) => 0.0
-  TimeNode(C, 2)   => 1.70833
-  TimeNode(B, 2)   => 1.0
-  TimeNode(B, 1)   => 3.25367
-  TimeNode(A, 100) => 1.0
-  TimeNode(A, 2)   => 3.54167
+  TimeNode(C, 1)   => 2.98666e-8
+  TimeNode(C, 10)  => 0.291667
 \end{lstlisting}
@@
 \begin{lstlisting}
-DataStructures.DefaultDict{Any,Any,Float64} with 3 entries:
-  "B" => 4.25367
-  "A" => 4.54167
-  "C" => 2.77667
+  "A" => 0.658333
+  "B" => 0.2
+  "C" => 0.291667
 \end{lstlisting}
-We see the scores of all three nodes are decreased when the last time stamp is $100$.
-Node $A$ is affected the most.
+We see the scores of all three nodes are decreased when it takes longer to communicate between different time stamps.
+In this case, the overall ranking is not affected but in general the communication time between time stamps can change the overall ranking.
 
@@
 
-Betweenness centrality measures the importance of a node as the ability to facilitate the communication between other nodes in the network.
+Betweenness centrality measures the importance of a node as the ability to facilitate the communication among other nodes in the network.
 Commonly it is defined based on the shortest paths.
-However, key messages do not necessarily follow the shortest paths and so it makes senses to consider walks instead.
+However, key messages do not necessarily follow the shortest paths and thus it makes senses to consider walks instead of shortest paths.
 Recall the $(i,j)$ entry of the resolvent matrix $(I - \alpha A)^{-1}$ provide information about the communication from $i$ to $j$. We could therefore define the resolvent betweenness for node $v$ as
@@
 For the $(I - \alpha (A-E_v))^{-1}_{i,j}$ part, we can apply the above the same algorithm on a graph with node $v$ and related edges removed.
+Therefore the general temporal resolvent betweenness centrality can be defined as
 \begin{lstlisting}
-function temporal_resolvent_betweenness(g1::EvolvingGraph,
-  g2::EvolvingGraph, v::TimeNode; alpha = 0.2, k = 10)
+function temporal_resolvent_betweenness(g1, g2,
+  v::TimeNode; alpha = 0.2, k = 10)
     r = 0.
@@
             if i != j && i != v && j != v
-                score1 = temporal_katz(g1, i, j, alpha = alpha, k = k)
-                score2 = temporal_katz(g2, i, j, alpha = alpha, k = k)
-                r += score1 == 0.0 ? 0 : (score1 - score2)/score1
+                score1 = temporal_katz(g1, i, j,
+                    alpha = alpha, k = k)
+                score2 = temporal_katz(g2, i, j,
+                    alpha = alpha, k = k)
+                r += score1 == 0.0 ? 0 :
+                    (score1 - score2)/score1
             end
@@
 \end{lstlisting}
-For example, by removing node $C$ a time stamp $2$ from Figure \ref{fig:katz_eg2} we find
-the temporal resolvent betweenness score is $6.09$. While the temporal resolvent betweenness score
-of node $A$ at time stamp $3$ is $5.0$. This shows $(C,2)$ is more important than $(A,3)$.
+Here \texttt{temporal\_katz} only takes account of walks from node $i$ to $j$. Evolving graph
+\texttt{g1} is the original evolving graph and evolving graph \texttt{g2} is \texttt{g1} with all the edges
+related to \texttt{v} removed.
 
-Now consider Figure \ref{fig:katz_eg3}. If we remove $(C,2)$, the temporal resolvent betweenness score is $4.20$.
-The analysis for temporal communicability betweenness centrality is similar.
+For example, by removing node $(A, 2)$, i.e., node $A$ at time stamp $2$, from Figure \ref{fig:katz_eg2} we find
+the temporal resolvent betweenness score of node $A$ is $5.0$. While the temporal resolvent betweenness score of node $(B,3)$ is $4.0$. This shows that $(A,2)$ is more important than $(B,3)$.
+We note that temporal communicability betweenness centrality can be analysed similarly.
 
@@
 
+One potential problem is the computational cost. Since the dimension of the block matrix
+is $|V| \times |T|$, where $|V|$ represents the number of nodes and $|T|$ represents the number of time stamps. The block matrix may become very large for an evolving graph with many time stamps.
+
 \section{Experiments}

### 2018-05-16 paper.tex
update temporal closeness and pagerank part

@@
 % closeness centrality
-Let $d_{ij}$ be the length of a temporal shortest walk from $i$ and $j$ in an evolving graph. Then
+
+Let $d_{ij}$ be the length of the shortest path from $i$ and $j$ in a static graph. Then
 the closeness centrality of a node $i$ is defined
 $$
-C_i^{closeness} = \frac{N-1}{\sum_j d_{ij}}.
+C_i^{closeness} = \frac{N-1}{\sum_j d_{ij}},
 $$
-Note that this depends on how we define the length of temporal shortest walk. The closeness centrality can takes account of only static edges, only causal edges, or both.
-The definition of temporal closeness centrality is similar to temporal katz. The only difference is that here we traverse the shortest paths not just walks on evolving graphs.
+where $N-1$ is the total number of reachable nodes.
+For evolving graphs, we need to consider the shortest temporal path from $(i,t_i)$ to $(j,t_j)$, for any time stamp $t_i \leq t_j$.
+Depends on how define the length of shortest temporal path, the closeness centrality can counts static edges, causal edges, or both.
+The key difference between Katz centrality and closeness centrality is the fact here we only consider shortest temporal paths, not just every temporal walks.
+We could apply BFS to find the shortest temporal path from $(v,t)$ to any other nodes in the evolving graphs. The algorithm is shown as follows.
 
 \begin{lstlisting}
-function temporal_closeness(g::AbstractEvolvingGraph, start::TimeNode)
+function temporal_closeness(g::AbstractEvolvingGraph,
+  start::TimeNode)
   v = start
@@
               if !(v in keys(level))
+                  if node_key(u) != node_key(v)
                     td = temporal_distance(start, u)
                     level[v] = i + td
+                  else
+                    level[v] = i - 1
+                  end
                   push!(next, v)
@@
   total_scores = sum(values(level))
-  return total_scores > 0. ? (length(level) - 1)/total_scores : 0.
+  return total_scores > 0. ?
+      (length(level) - 1)/total_scores : 0.
 end
 \end{lstlisting}
+The algorithm starts at node \texttt{start} and explores the forward neighbours and store all the
+reached nodes so far in \texttt{level}.
+If \texttt{node\_key(u) == node\_key(v)}, we traverse the same node at different time stamps.
+In this case, we consider that we've already reached it at the previous time stamp.
+
 For Figure \ref{fig:katz_eg2} the scores are
 \begin{lstlisting}
-Dict{Any,Any} with 7 entries:
+TimeNode(A, 2) => 0.666667
+TimeNode(A, 3) => 1.0
+TimeNode(B, 1) => 0.346154
+TimeNode(B, 2) => 0.0
 TimeNode(B, 3) => 0.0
-TimeNode(B, 1) => 0.27027
-TimeNode(A, 3) => 1.0
-TimeNode(B, 2) => 1.0
-TimeNode(C, 1) => 0.259259
-TimeNode(A, 2) => 0.538462
-TimeNode(C, 2) => 0.416667
+TimeNode(C, 1) => 0.315789
+TimeNode(C, 2) => 0.5
 \end{lstlisting}
+and the sum of scores at different time stamps gives
+\begin{lstlisting}
+"A" => 1.66667
+"B" => 0.346154
+"C" => 0.815789
+\end{lstlisting}
+Note that the ranking is the same as the temporal Katz centrality case.
 For Figure \ref{fig:katz_eg3}, the scores are
 \begin{lstlisting}
-Dict{Any,Any} with 7 entries:
+TimeNode(A, 10)  => 0.0707071
+TimeNode(A, 100) => 1.0
+TimeNode(B, 1)   => 0.0597015
+TimeNode(B, 10)  => 0.0
 TimeNode(B, 100) => 0.0
-TimeNode(A, 2)   => 0.0636364
-TimeNode(A, 100) => 1.0
-TimeNode(C, 2)   => 0.0458716
-TimeNode(B, 1)   => 0.0746269
-TimeNode(C, 1)   => 0.0564516
-TimeNode(B, 2)   => 1.0
+TimeNode(C, 1)   => 0.0390625
+TimeNode(C, 10)  => 0.0412371
 \end{lstlisting}
-
-The analysis for temporal communicability betweenness centrality is similar.
+and the sums are
+\begin{lstlisting}
+"A" => 1.07071
+"B" => 0.0597015
+"C" => 0.0802996
+\end{lstlisting}
+Similar to the temporal Katz centrality case, we see a decrease of centrality scores
+for all the nodes in the evolving graph.
+We note that the analysis for temporal betweenness centrality is similar to above.
 
@@
 
-We derive a generalization of PageRank on evolving graphs.
-The first idea is based on reverse temporal flows and block adjacency matrix.
+We see from our analysis for temporal Katz centrality and temporal betweenness centrality
+that the temporal distance between nodes in an evolving graph can impact the final centrality scores.
+We would like to design a temporal PageRank algorithm that takes account of between
+the temporal distance and the spatial distance. The generalisation is based on two ideas:
+reversed temporal walks and block adjacency matrix.
 
-\subsubsection{Reverse Temporal Flows}
+\subsubsection{Reversed Temporal Walks}
 
 We can not travel back in time. But reversing the direction of temporal flows can help
-identify the ``hub'' nodes or the source of the flows. The authority score of a page is
-proportional to its importance, and the hub score describes the quality of a page as a link collection of important related pages \cite{kleinberg99}.
-Indeed, reverse PageRank has
-been studied by \cite{bar08, fogaras03, gleich15}. In reverse PageRank we compute PageRank on the graph with reversed direction, i.e., reverse the direction of each edge $(i,j)$ to $(j, i)$.
-Fogaras \cite{fogaras03} shows that Reversed Page Rank scores express hub quality.
+identify the ``hub'' nodes or the source of the flows. Recall in the HITS algorithm \cite{kleinberg99},
+the hub score describes the quality of a web page as a link collection of important related pages.
+In reverse PageRank we compute PageRank on the graph with reversed direction, i.e., reverse the direction of each edge $(i,j)$ to $(j,i)$.
+Fogaras \cite{fogaras03, gleich15} shows that Reversed Page Rank scores express hub quality.
 
-Recall a time-preserving walk is a time-ordered sequence of active nodes. Here we define a \emph{reversed temporal walk} to be a reversed time-ordered sequence of active nodes, i.e.,
+Recall a time-preserving walk is a time-ordered sequence of active nodes. We define a \emph{reversed temporal walk} to be a reversed time-ordered sequence of active nodes
+$\langle (v_1, t_1), (v_2,t_2), \ldots, (v_m, t_m)\rangle$, where
 $t_1 \ge t_2 \ge \cdots \ge t_m$.
@@
 
-We can not simply use static graphs to replace evolving graphs for two main reasons.
-First, a path has to preserve the dimension, i.e., certain path is incorrect in the aggregated static graph.
-Second, two path between $A$ and $B$ are considered to be one path in the aggregated static graph.
-
-In \cite{chen16}, we derive a block adjacency matrix representation of an evolving graph.
-If $E'$ is the set of causal edges and $\hat E$ is the set of static edges then
+Aggregating edges at each time stamp to form
+a simple static graph can provide misleading information about the structure of the network.
+In \cite{chen16}, we derive a block adjacency matrix representation of an evolving graph and prove it is the correct representation of an evolving graph.
+Let $E'$ is the set of causal edges and $\hat E$ is the set of static edges then
 an evolving graph can be represented as
@@
 The adjacency matrix blocks $A^{[t]}$ encode the static edge set $\hat E$, whereas the off-diagonal blocks $M^{[t_i, t_j]}$ encode the causal edge set $E'$.
-
-(Need to justify the benefit of this approach.)
-We can apply static graph centrality algorithms to $M_n$ and then take the average of ratings at each each time stamp. For example, we can construct the Google matrix
-$G_n$ from $M_n$ and the ranking of the nodes can be found by solving
+To take account of the temporal distance between nodes, we could let
 $$
- r= G_n r.
+  M_{uv}^{[t_i, t_j]} =
+  \begin{cases}
+    \frac{1}{|t_j - t_i|} & \mbox{if} (u, v) \in E' \\
+    0 & \mbox{otherwise}.
+  \end{cases}
 $$
 
-For Figue \ref{fig:eg_shortest_walk}, we have
+For Figure \ref{fig:eg_shortest_walk}, we have
 
 \begin{align*}
-V & = \{(1,\!t_1), (2,\!t_1), (1,\!t_2), (3,\!t_2), (2,\!t_3), (3,\!t_3)\},\\
-\tilde E &= \{((1,\!t_1), (2,\!t_1)), ((1,\!t_2), (3,\!t_2)), ((2,\!t_3), (3,\!t_3))\},\\
-E'  &= \{((1,\!t_1), (1,\!t_2)), ((2,\!t_2), (2,\!t_3)), ((3,\!t_2), (3,\!t_3))\}.
+V & = \{(1,\!1998), (2,\!1998), (1,\!1999), (3,\!1999), (2,\!2018), (3,\!2018)\},\\
+\tilde E &= \{((1,\!1998), (2,\!1998)), ((1,\!1999), (3,\!1999)), ((2,\!2018), (3,\!2018))\},\\
+E'  &= \{((1,\!1998), (1,\!1999)), ((2,\!1999), (2,\!2018)), ((3,\!1999), (3,\!2018))\}.
 \end{align*}
@@
 0 & 1 & 1 & 0 & 0 & 0 \\
-0 & 0 & 0 & 0 & 1 & 0 \\
+0 & 0 & 0 & 0 & 1/9 & 0 \\
 0 & 0 & 0 & 1 & 0 & 0 \\
-0 & 0 & 0 & 0 & 0 & 1 \\
+0 & 0 & 0 & 0 & 0 & 1/9 \\
 0 & 0 & 0 & 0 & 0 & 1 \\
@@
 
-We derive the block google matrix as a combination of block matrix $A$ and its transpose $A^T$.
-
-The block google matrix is defined as
+Notice that the lower triangular blocks of matrix $\bm M_n$ are zeros.
+This is because all the causal edges are time preserving. We consider the transpose of matrix $\bm M_n$, which reverse the direction of static edges and causal edges.
+Let $b \in [0,1]$ be a balance scalar. Then the block matrix
+$$
+b \bm M_n + (1-b) \bm M_n^T
+$$
+takes account of both the temporal walks and reversed temporal walks.
+We now derive the block Google matrix as
 
 \begin{lstlisting}
-function block_google_matrix(g::IntAdjacencyList; alpha = 0.85, balance = 0.75)
-  A = full(block_adjacency_matrix(g))
-  A = balance * A + (1-balance) * A'
-  N, N = size(A)
+function block_google_matrix(g; alpha = 0.85, balance = 0.75)
+  M = full(block_adjacency_matrix(g))
+  M = balance * M + (1-balance) * M'
+  N, N = size(M)
   p = ones(N)/N
   dangling_weights = p
-  dangling_nodes = find(x->x==0, sum(A,2))
-
+  dangling_nodes = find(x->x==0, sum(M,2))
   for node in dangling_nodes
-      A[node,:] = dangling_weights
+      M[node,:] = dangling_weights
   end
-  A ./= sum(A,2)
-  return alpha * A .+ (1- alpha) * p
+  M ./= sum(M,2)
+  return alpha * M .+ (1- alpha) * p
 end
@@
 
-We find the ranking for Figure \ref{}
+The function \texttt{block\_adjacency\_matrix} convert an evolving graph $g$ to a block adjacency matrix $\bm M$.
+Every row sum of the block Google matrix is equal to one.
+Each element of the dominant eigenvector of the block Google matrix
+represents the PageRank rating of a node.
 
+For Figure \ref{fig:katz_eg2}, we set $alpha$ be $0.85$ and $balance$ be $1.0$.
+Then the PageRank scores are
 \begin{lstlisting}
-9-element Array{Complex{Float64},1}:
- 0.12278
-0.254264
-0.0533627
- 0.36275
-0.350713
-0.406792
-0.0533627
-0.524112
-0.468848
+ TimeNode(A, 2) => 0.289123
+ TimeNode(A, 3) => 0.128054
+ TimeNode(B, 1) => 0.182477
+ TimeNode(B, 2) => 0.354335
+ TimeNode(B, 3) => 0.480941
+ TimeNode(C, 1) => 0.128054
+ TimeNode(C, 2) => 0.250931
 \end{lstlisting}
+and the sum of node scores at all three time stamps are
+\begin{lstlisting}
+ "A" => 0.417177
+ "B" => 1.01775
+ "C" => 0.378986
+\end{lstlisting}
+We see node $B$ is the most important node in an evolving graph.
+On the other extreme, if we set $balance$ to be $0.0$, we get the overall scores
+\begin{lstlisting}
+ "A" => 0.678502
+ "B" => 0.647353
+ "C" => 0.527927
+\end{lstlisting}
+Thus $A$ is the most important node in this case.
 
-One potential problem is the computational cost. Since the dimension of the block matrix
-is $|V| \times |T|$, where $|V|$ represents the number of nodes and $|T|$ represents the number of time stamps. The block matrix may become very large for an evolving graph with many time stamps.
-
+One potential problem with temporal PageRank is that the computational cost is expensive for large evolving graphs with many time stamps. The dimension of the block matrix
+is $|V| \times |T|$, where $|V|$ represents the number of nodes and $|T|$ represents the number of time stamps.
 \section{Experiments}
@@
 
-We test the influence of time on evolvign graph centralities.
+We test the influence of time on evolving graph centralities.
+Justify use \texttt{IntAdjacencyList}.
 

### 2018-05-16 paper.tex
include experiments part

@@
 reverse network flow and block adjacency matrix.
-We conduct our experiments on random evolving graphs and the JMLR co-author networks to illustrate our idea.
+We conduct our experiments on random evolving graphs to illustrate our idea.
 \end{abstract}
@@
 
-We test the influence of time on evolving graph centralities.
-Justify use \texttt{IntAdjacencyList}.
+We conduct the following experiments using \texttt{IntAdjacencyList}, which represents an evolving graph $g$ with integer nodes and integer time stamps as adjacency lists.
+Each active node stores its forward neighbours as a list.
+We count both static edges and causal edges.
+The following experiments study the influence of temporal distance on centrality scores. All experiments are conducted on a MacOS system with $8$ GB of RAM running at $2.3$ GHz clock speed.
 
@@
 
-Note the random evolving graphs are conducted using \texttt{IntAdjacencyList}, which gives better performance for
-forward\_neighbors.
-
-We generate a random evolving graph with $100$ nodes and $9771$ static edges and $5$ time stamps.
+We generate a random evolving graph $g$ with $500$ nodes and about $499183$ static edges and $10$ time stamps.
 Here are the top $10$ nodes we find using the Katz Centrality
 
-Since we only are interested in the top nodes.
-
-\begin{tabular}{ l | c }
-  \hline
-  node & score \\
-  334 & 0.152288 \\
-  9 & 0.137403 \\
-  428 & 0.126793 \\
-  164 & 0.121582 \\
-  250 & 0.117862 \\
-  35 & 0.117627 \\
-  291 & 0.105793 \\
-  414 & 0.0975953 \\
-  123 & 0.096394 \\
-  478 & 0.0945754 \\
-  \hline
+\begin{lstlisting}
+(459, 0.126296)
+(147, 0.116541)
+(326, 0.113667)
+(183, 0.108705)
+(469, 0.0936847)
+(296, 0.0925748)
+(424, 0.0921004)
+(377, 0.091973)
+(313, 0.0910352)
+(127, 0.089123)
+\end{lstlisting}
+
+Since we are usually interested in the ranking of top score nodes,
+we apply temporal Katz centrality on these above $10$ nodes.
+We set $alpha = 0.5$  and $max\_level = 3$. We report the change of ranking and rating in Table \ref{table:ranking}
+
+  \begin{table}[h]
+    \begin{center}
+  \begin{tabular}{ c | c | c | c }
+    Ranking at $t_1$ & Rating at $t_1$ & Overall ranking & Overall rating \\
+     469 & $0.7193$ & 183 & $5.975$ \\
+     459 & $0.7180$ & 469 & $5.932$ \\
+     424 & $0.7108$ & 326 & $5.804$ \\
+     296 & $0.7042$ & 313 & $5.797$ \\
+     326 & $0.6853$ & 459 & $5.788$ \\
+     183 & $0.6647$ & 147 & $5.782$ \\
+     377 & $0.6622$ & 377 & $5.691$ \\
+     127 & $0.6316$ & 296 & $5.681$ \\
+     147 & $0.6303$ & 424 & $5.636$ \\
+     313 & $0.5715$ & 127 & $5.613$ \\
   \end{tabular}
-
-We find identify the top $10$
-
-We test temporal Katz centrality,  for top $20$
-temporal closeness, and temporal pagerank.
-by varing the influence of temporal distance.
-
-Katz score | temporal katz at with time influence 0.1 | temporal katz with time influence 1.0
-
-Closeness with time influence 0.1 | closeness with time influence 1.0
-
-PageRank with time influence 0.1 | PageRank with time influence 1.0
-
-\subsection{JMLR Coauthor Network}
-\label{sec:jmlr-coauth-netw}
-
-We construct the evolving coauthor network from Etymo (\url{https://etymo.io}).
-We collected $1566$ publications published by Journal of Machine Learning Research (JMLR) from $2001$ to $2017$ with authors involved. We regard each year
-as a time stamp and there are $17$ time stamps in total. At each time stamp, we
-create a undirected edge (or two directed edges) between two authors if they have coauthored at least one paper.
-
-Some experiments as above.
-
-Katz score | temporal katz at with time influence 0.1 | temporal katz with time influence 1.0
-
-Closeness with time influence 0.1 | closeness with time influence 1.0
-
-PageRank with time influence 0.1 | PageRank with time influence 1.0
+  \end{center}
+  \caption{Temporal Katz centrality ranking and rating of evolving graph $g$.
+We set the weight of all causal edges to zero.}
+  \label{table:ranking}
+  \end{table}
+
+  \begin{table}[h]
+    \begin{center}
+  \begin{tabular}{ c | c | c | c }
+    Ranking at $t_1$ & Rating at $t_1$ & Overall ranking & Overall rating \\
+     \textbf{459} & $0.6290$ & 183 & $5.576$ \\
+     \textbf{469} & $0.6281$ & 469 & $5.533$ \\
+     424 & $0.6236$ & 326 & $5.414$ \\
+     296 & $0.6167$ & 313 & $5.409$ \\
+     326 & $0.5983$ & 459 & $5.401$ \\
+     183 & $0.5778$ & 147 & $5.396$ \\
+     377 & $0.5775$ & 377 & $5.311$ \\
+     127 & $0.5492$ & 296 & $5.299$ \\
+     147 & $0.5471$ & 424 & $5.258$ \\
+     313 & $0.4916$ & 127 & $5.237$ \\
+  \end{tabular}
+  \end{center}
+  \caption{Temporal Katz centrality ranking and rating of evolving graph $g$.
+  We set the weight of a causal edge between two active nodes to be their temporal difference.
+  Compare with Table \ref{table:ranking}, we highlight the ranking difference using bold font.}
+  \label{table:ranking2}
+  \end{table}
+
+We observe the rating of all nodes are smaller when we take account of the temporal information. The only difference between the rankings of two table
+is the top two nodes $459$ and $469$. The overall ranking stays unchanged.
+This shows that temporal Katz centrality is stable for changing temporal information.
+
+On the same random evolving graph $g$, we compute temporal closeness centrality.
+
+\begin{table}[h]
+  \begin{center}
+\begin{tabular}{ c | c | c | c }
+  Ranking at $t_1$ & Rating at $t_1$ & Overall ranking & Overall rating \\
+   296 & $0.4938$ & 469 & $5.040$ \\
+   469 & $0.4933$ & 183 & $5.030$ \\
+   459 & $0.4915$ & 313 & $5.016$ \\
+   424 & $0.4888$ & 326 & $5.009$ \\
+   326 & $0.4879$ & 147 & $5.008$ \\
+   377 & $0.4872$ & 459 & $5.003$ \\
+   183 & $0.4858$ & 296 & $4.002$ \\
+   127 & $0.4831$ & 377 & $4.996$ \\
+   147 & $0.4790$ & 127 & $4.989$ \\
+   313 & $0.4773$ & 424 & $4.986$ \\
+\end{tabular}
+\end{center}
+\caption{Temporal closeness centrality ranking and rating of evolving graph $g$.
+We set the weight of all causal edges to zero.}
+\label{table:ranking3}
+\end{table}
+
+\begin{table}[h]
+  \begin{center}
+\begin{tabular}{ c | c | c | c }
+  Ranking at $t_1$ & Rating at $t_1$ & Overall ranking & Overall rating \\
+   296 & $0.2540$ & 469 & $3.562$ \\
+   469 & $0.2487$ & \textbf{147} & $3.557$ \\
+   \textbf{377} & $0.2478$ & \textbf{183} & $3.555$ \\
+   \textbf{459} & $0.2475$ & \textbf{313} & $3.548$ \\
+   \textbf{424} & $0.2471$ & \textbf{377} & $3.545$ \\
+   \textbf{326} & $0.2470$ & \textbf{296} & $3.541$ \\
+   \textbf{127} & $0.2445$ & \textbf{459} & $3.540$ \\
+   \textbf{183} & $0.2422$ & \textbf{127} & $3.538$ \\
+   \textbf{313} & $0.2389$ & \textbf{424} & $3.535$ \\
+   \textbf{147} & $0.2373$ & \textbf{326} & $3.533$ \\
+\end{tabular}
+\end{center}
+\caption{Temporal closeness centrality ranking and rating of evolving graph $g$.
+We set the weight of a causal edge between two active nodes to be their temporal difference. Compare with Table \ref{table:ranking3}, we highlight the ranking difference using bold font.}
+\label{table:ranking4}
+\end{table}
+
+For temporal closeness centrality, we notice that most of rankings are changed when we take account of temporal information.
+
+% \subsection{JMLR Coauthor Network}
+% \label{sec:jmlr-coauth-netw}
+%
+% We construct the evolving coauthor network from Etymo (\url{https://etymo.io}).
+% We collected $1566$ publications published by Journal of Machine Learning Research (JMLR) from $2001$ to $2017$ with authors involved. We regard each year
+% as a time stamp and there are $17$ time stamps in total. At each time stamp, we
+% create a undirected edge (or two directed edges) between two authors if they have coauthored at least one paper.
+%
+% Some experiments as above.
+%
+% Katz score | temporal katz at with time influence 0.1 | temporal katz with time influence 1.0
+%
+%
+% Closeness with time influence 0.1 | closeness with time influence 1.0
+%
+%
+% PageRank with time influence 0.1 | PageRank with time influence 1.0
+%
+% also show trends of an author.
 
@@
 
-We describe in details the generalizartion of centrality algorithms for evolving graphs.
+We describe in details the generalizartion of centrality algorithms for evolving graphs and find
 We introduce the generalization of PageRank centrality.

### 2018-05-16 paper.tex
update conclusion

@@
 We conduct the following experiments using \texttt{IntAdjacencyList}, which represents an evolving graph $g$ with integer nodes and integer time stamps as adjacency lists.
-Each active node stores its forward neighbours as a list.
+In particular, each active node in $g$ stores its forward neighbours in a list.
 We count both static edges and causal edges.
@@
 
-We generate a random evolving graph $g$ with $500$ nodes and about $499183$ static edges and $10$ time stamps.
-Here are the top $10$ nodes we find using the Katz Centrality
-
+We generate a random evolving graph $g$ with $500$ nodes and $499183$ static edges and $10$ time stamps. Using the Katz centrality in \eqref{eq:q}, we find the top $10$ most important nodes.
 \begin{lstlisting}
@@
 \end{lstlisting}
-
-Since we are usually interested in the ranking of top score nodes,
-we apply temporal Katz centrality on these above $10$ nodes.
-We set $alpha = 0.5$  and $max\_level = 3$. We report the change of ranking and rating in Table \ref{table:ranking}
+Instead of running temporal Katz centrality for each active node in the evolving graph $g$,
+we only consider these $10$ most important nodes because in practice we usually are just interested in the rankings and ratings of the most important nodes. For each node in the above list,
+we compute the node score at each time stamp and the overall score.
+Here we set $alpha = 0.5$  and $max\_level = 3$.  The results are shown in Table \ref{table:ranking}
+and Table \ref{table:ranking2}.
+We observe that the Katz ratings in general are smaller when we take account of the temporal information. The rankings, however, are stable. For rankings at time stamp $1$,
+only the top two nodes $459$ and $469$ change positions.
+The overall rankings stays unchanged.
 
@@
   \end{center}
-  \caption{Temporal Katz centrality ranking and rating of evolving graph $g$.
+  \caption{Temporal Katz centrality ranking and rating on evolving graph $g$.
   We set the weight of all causal edges to zero.}
@@
   \end{center}
-  \caption{Temporal Katz centrality ranking and rating of evolving graph $g$.
+  \caption{Temporal Katz centrality ranking and rating on evolving graph $g$.
   We set the weight of a causal edge between two active nodes to be their temporal difference.
-  Compare with Table \ref{table:ranking}, we highlight the ranking difference using bold font.}
+  We use bold font to highlight the differences in ranking from Table \ref{table:ranking}.}
   \label{table:ranking2}
@@
 
-We observe the rating of all nodes are smaller when we take account of the temporal information. The only difference between the rankings of two table
-is the top two nodes $459$ and $469$. The overall ranking stays unchanged.
-This shows that temporal Katz centrality is stable for changing temporal information.
-
-On the same random evolving graph $g$, we compute temporal closeness centrality.
+For the same random evolving graph $g$, we also compute temporal closeness centrality scores.
+The results are shown in Table \ref{table:ranking3} and Table \ref{table:ranking4}.
+For temporal closeness centrality, we notice that most of rankings are changed when we take account of the temporal information.
 
@@
 \caption{Temporal closeness centrality ranking and rating of evolving graph $g$.
-We set the weight of a causal edge between two active nodes to be their temporal difference. Compare with Table \ref{table:ranking3}, we highlight the ranking difference using bold font.}
+We set the weight of a causal edge between two active nodes to be their temporal difference.
+We use bold font to highlight the differences in ranking from Table \ref{table:ranking3}.}
 \label{table:ranking4}
 \end{table}
-
-For temporal closeness centrality, we notice that most of rankings are changed when we take account of temporal information.
 
@@
 
-We describe in details the generalizartion of centrality algorithms for evolving graphs and find
-We introduce the generalization of PageRank centrality.
+We describe in details the generalisation of centrality algorithms for evolving graphs.
+We conduct experiments to show that temporal information is an important factor for evolving graph centrality ranking and rating.
+In particular, we observe temporal Katz centrality is much more stable than temporal closeness centrality if we vary the influence of temporal information.
+We also derive a temporal PageRank centrality using reversed temporal walks and block adjacency matrix.
 

### 2018-10-10 paper.tex
update experiments and conclusion part

@@
 However, we cannot travel back in time or even send a message to the past.
-To traverse an evolving graph, a.k.a a time-dependent graph, one has to consider order of time stamps. In particular, a walk on an evolving graph needs to be time-preserving, meaning we
+To traverse an evolving graph (a time-dependent graph), one has to consider the order of time stamps. In particular, a walk on an evolving graph needs to be time-preserving, meaning we
 can not pass a massage (through an edge) to a node at a earlier time.
@@
 % time-respecting walk
-We represent an evolving graph as a time-ordered sequences of graphs, similar to the work of Tang and coworkers \cite{nicosia13, tang09, tang102, tang10} and Grindrod, Higham and coworkers \cite{grindrod13,grindrod11}.
-The idea is to divide the system's time span into temporal slices and regards it as a sequence of static graphs $G^{[t]}$, one for each layer.
-Such representation arises naturally in many real-world applications.
+We represent an evolving graph as a time-ordered sequences of graphs, similar to the work of Tang and coworkers \cite{ntmm13, tmml09, tmml10, tsmm09} and Grindrod, Higham and coworkers \cite{grihig13,gphe11}.
+The idea is to divide the system's time span into temporal slices and regard it as a sequence of static graphs $G^{[t]}$, one for each layer.
+Such a representation arises naturally in many real-world applications.
 For example,
 consider networks of users interacting through messaging.
-Each interaction between two users $A$ and $B$ are stored with a time stamp $t$.
-If we represent a user as a node then a user $A$ at time stamp $t$ is represented by a pair $(v,t)$ and a message sent from user $A$ to user $B$ at time stamp $t$ can be represented as $\langle (A, t) (B, t) \rangle$.
+Each interaction between two users $A$ and $B$ is stored with a time stamp $t$.
+If we represent user $A$ as a node then user $A$ at time stamp $t$ is represented by a pair $(A,t)$ and a message sent from user $A$ to user $B$ at time stamp $t$ can be represented as $\langle (A, t), (B, t) \rangle$.
 
@@
 and then $B$ sent this message to $C$ at time stamp $t_2$.
-We can represent this activity as $\langle (A,t_1), (B,t_1), (B, t_2), (C,t_2)\rangle$, where each pair of two nodes has meanings: $\langle (A,t_1), (B,t_1) \rangle$ and $\langle (B,t_2), (C,t_2) \rangle$ represent interactions between users $A$, $B$, and $C$ and $\langle (B,t_1), (B,t_2) \rangle$ represents the fact that user $B$ holds the message at time stamp $t_1$ and $t_2$.
+We can represent this activity as $\langle (A,t_1), (B,t_1), (B, t_2), (C,t_2)\rangle$, where each pair of two nodes has meanings: $\langle (A,t_1), (B,t_1) \rangle$ and $\langle (B,t_2), (C,t_2) \rangle$ represent interactions between users $A$, $B$, and $C$ and $\langle (B,t_1), (B,t_2) \rangle$ represents the fact that user $B$ holds the message at time stamps $t_1$ and $t_2$.
 
@@
 We call edges of the first kind \emph{static edges} and of the second kind \emph{causal edges}.
-Recall in static graph, a walk of length $m$ is defined as a sequence of nodes $v_1, v_2, \ldots, v_{m+1}$ such that for each $i = 1, \ldots, m$ there is an edge from $v_i$ to $v_{i+1}$.
-How to determine the length of a time-respecting walk?
-One could define the length of a time-respecting walk as the total number of temporal slices (see shortest temporal distance in \cite{tang09}) or the number of static edges (see dynamic walk in \cite{grindrod11}).
+Recall that in static graph, a walk of length $m$ is defined as a sequence of nodes $v_1, v_2, \ldots, v_{m+1}$ such that for each $i = 1, \ldots, m$ there is an edge from $v_i$ to $v_{i+1}$.
+How can we  determine the length of a time-respecting walk?
+One could define the length of a time-respecting walk as the total number of temporal slices (see the shortest temporal distance in \cite{tmml09}) or the number of static edges (see the dynamic walk in \cite{gphe11}).
 This paper studies the impact of these two different definitions.
-In particular, we studies a general definition of temporal distance that takes account of both temporal slices and static edges.
+In particular, we study a general definition of temporal distance that takes account of both temporal slices and static edges.
 
@@
 
-% no work on pagerank so far. By understanding temporal walk, we could provide a generalization of pagerank on evolving graphs.
-
-% In Higham's following up papers, time delay is considered as alternative format of Katz centrality.
-% But the impact of temporal is left unconsidered.
-We studied the problem on centrality from two different types of centrality: one that depends on matrix unfolding and one that depends on temporal walk.
-
 % our contribution this paper
 Borgatti \cite{borgatti05} noted that the manner of traffic flow entails a new way to think about centrality.
-In particularly, the importance of a node in a network can not be determined without reference to how traffic flows through the network.
+In particular, the importance of a node in a network cannot be determined without reference to how traffic flows through the network.
 Inspired by this idea, we simulate network flows in evolving graphs to measure the centrality scores.
-% Grindrod et al.'s definition of dynamic walk \cite{grindrod11} only counts static edges.
+% Grindrod et al.'s definition of dynamic walk \cite{gphe11} only counts static edges.
 % Tang et al. \cite{tang10s} measure a temporal shortest walk in time unit (or causal edges) only.
@@
 The aims of this paper are as follows.
-First, to derive important evolving graph centrality from first principle via network flow.
+First, to derive important evolving graph centrality from first principles via network flow.
 Second, to study the impact of temporal distance between nodes on centrality.
@@
 \end{equation}
-where parameter $\alpha < 1/ \max_k \rho(A^{[k]})$, the spectral radius of $A^{[k]}$.
+where the parameter $\alpha$ satisfies $\alpha < 1/ \max_k \rho(A^{[k]})$, the spectral radius of $A^{[k]}$.
 The $i$th row sum of $Q^{[k]}$ is the broadcast centrality.
@@
 Suppose $A$, $B$, and $C$ are three co-workers in a large internet company. Figure \ref{fig:katz_eg}
-shows how they exchange ideas during $3$ days at work. The directions of the arrows indicate the direction of the flow of ideas.
-For example, $A$ shares a new idea with $B$ on day $1$ and $B$ shares a new idea with $C$ on dat $3$. As a result, $A$'s idea can influence $C$.
+shows how they exchange ideas during three days at work. The directions of the arrows indicate the direction of the flow of ideas.
+For example, $A$ shares a new idea with $B$ on day $1$ and $B$ shares a new idea with $C$ on dat $3$.
+As a result, $A$'s idea can influence $C$.
+Here, and in subsequent figures, green filled circles represent active node and red circles represent inactive nodes.
 
@@
 \end{center}
-\caption{An evolving directed graph with 3 time stamps $1$, $2$ and $3$.
+\caption[An evolving directed graph with 3 time stamps $1$, $2$ and $3$.]{An evolving directed graph with 3 time stamps $1$, $2$ and $3$.
 At each time stamp, the evolving graph is represented as a graph.
@@
 
-As expected $A$ is the most important node in the network. $C$ is the second important node in the network as it influenced
+As expected $A$ is the most important node in the network. $C$ is the second most important node in the network as it influenced
 $A$ at time stamp $2$.
 If we reverse the time of communication between day $1$ and $3$, i.e., $B$ shares a new idea with $C$ on day $1$ and $A$ shares a new idea with $B$ on day $3$.
-Then in this case the idea $A$ had on day $3$ can not pass to $C$.
+Then in this case the idea $A$ had on day $3$ cannot pass to $C$.
 This is illustrated in Figure \ref{fig:katz_eg2}.
-
 \begin{figure}[h]
@@
 \end{center}
-\caption{An evolving directed graph with 3 time stamps $1$, $2$ and $3$.
-At each time stamp, the evolving graph is represented as a graph.
-The green filled circles represent active nodes while the red circles represent
-inactive nodes. Directed edges in each time stamp are shown as black arrows.}
+\caption{An evolving directed graph with 3 time stamps $1$, $2$ and $3$.}
 \label{fig:katz_eg2}
 \end{figure}
-
-In this cast, we have
+In this case, we have
 \begin{lstlisting}
@@
 The centrality ratings of the three nodes are
-
 \begin{lstlisting}
@@
 but on day $1$, day $10$, and day $100$, as shown in Figure \ref{fig:katz_eg3},
-we would expect the centrality scores to change. However, according to \eqref{eq:q}, scores are unchanged.
+we would expect the centrality scores to change. However, according to \eqref{eq:q}, the scores are unchanged.
 We notice that the generalised Katz centrality on evolving graphs only takes account of the edges at each time stamp but not the communication time between edges at different time stamps.
@@
 \end{center}
-\caption{An evolving directed graph with 3 time stamps $1$, $10$ and $100$.
+\caption[An evolving directed graph with 3 time stamps $1$, $10$ and $100$.]{An evolving directed graph with 3 time stamps $1$, $10$ and $100$.
 At each time stamp, the evolving graph is represented as a graph.
@@
 % what is walk and what is path?
-A walk of length $l$ is a sequence of nodes $v_1, v_2, \ldots, v_l, v_{l+1}$ such that for
-each $i = 1, 2, \ldots, l$, there is an edge from $v_i$ to $v_{i+1}$. A path of length $l$ is a walk of length $l$
+A walk of length $\ell$ is a sequence of nodes $v_1, v_2, \ldots, v_l, v_{l+1}$ such that for
+each $i = 1, 2, \ldots, \ell$, there is an edge from $v_i$ to $v_{i+1}$. A path of length $\ell$ is a walk of length $\ell$
 such that all the nodes are different.
+% what is time-preserving walks
+Similarly, we define a temporal walk to be a time-ordered sequence of temporal nodes. A temporal path is a temporal walk such that all the temporal nodes are different.
 % relate to centrality
@@
 $G_n = \langle G^{[1]}, G^{[2]},  \ldots ,G^{[n]} \rangle$ with associated time stamps
-$t_1, t_2, \ldots, t_n$ respectively. Each $G^{[t]} = (V^{[t]}, E^{[t]})$ represents a (static) graph labelled by a time t.
+$t_1 \leq t_2 \leq \ldots \leq t_n$.
+Each $G^{[t]} = (V^{[t]}, E^{[t]})$ represents a (static) graph labelled by a time t.
 \end{definition}
 
-Note the node sets $V^{[t]}$ can change over time, i.e., nodes may appear or disappear at a particular time stamp.
+Note that the node sets $V^{[t]}$ can change over time, i.e., nodes may appear or disappear at a particular time stamp.
 For example, in Figure \ref{fig:eg_shortest_walk}, at time stamp $1998$, $V^{[1998]} = \langle 1, 2 \rangle$ and $E^{[1998]} = \langle (1,2) \rangle$.
@@
 $A^{[t_i]}\cdots A^{[t_j]}$, where $i < j$ counts all the temporal walks of length $j -i$.
-For example, $A^{[1]}A^{[4]}$, $A^{[1]}A^{[1]}A^{[4]}$ and $A^{[1]}A^{[2]}A^{[3]}A^{[4]}$ are all walks of length 3.
+For example, $A^{[1]}A^{[4]}$, $A^{[1]}A^{[1]}A^{[4]}$ and $A^{[1]}A^{[2]}A^{[3]}A^{[4]}$ count all walks of length 3.
 In the original Katz centrality, the `attenuation' factor $\alpha$ is imposed on the
@@
 \]
-Note this can not be written in \eqref{eq:q} as discussed in Section \ref{sec:temp-katz-centr}.
+Note this is different from \eqref{eq:q} as discussed in Section \ref{sec:temp-katz-centr}.
 
@@
 \end{center}
-\caption{An evolving directed graph with 3 time stamps $1998$, $1999$ and $2018$.
+\caption[An evolving directed graph with 3 time stamps $1998$, $1999$ and $2018$.]{An evolving directed graph with 3 time stamps $1998$, $1999$ and $2018$.
 At each time stamp, the evolving graph is represented as a graph.
-The green filled circles represent active nodes while the red circles represent
-inactive nodes. Directed edges in each time stamp are shown as black arrows and directed edges between graphs are shown as dotted arrows, where $w_1, w_2 \ldots w_5$ are edge weights.}
+Directed edges in each time stamp are shown as black arrows and directed edges between graphs are shown as dotted arrows, where $w_1, w_2 \ldots w_5$ are edge weights.}
 \label{fig:eg_shortest_walk}
@@
 
-In Figure \ref{fig:eg_shortest_walk}, the filled green circles are active nodes. For the adjacency matrix representation, a node $i$ is active at time stamp $t$, then
+In Figure \ref{fig:eg_shortest_walk}, the filled green circles are active nodes. For the adjacency matrix representation, if a node $i$ is active at time stamp $t$ then
 the $i$th row or the $i$th column of $A^{[t]}$ has at least one none-zero entry.
@@
  $\langle (1, 1998), (2, 1998) \rangle$ is a static edge at time stamp $1998$ and $\langle (3, 1999), (3, 2018) \rangle$ is a causal edge between time stamp $1999$ and time stamp $2018$.
- The difference between static edges and causal edges were first explicitly considered in \cite{chen16}.
+ The difference between static edges and causal edges was first explicitly considered in \cite{chen16}.
 
@@
  In Figure \ref{fig:eg_shortest_walk}, the black arrows represent static edges and the dotted arrows represent causal edges.
- Suppose we assign all the static edge weight to $1$ and
+ Suppose we assign all the static edge weights to $1$ and
  let the causal edge weight be the number of time stamps between the pair of nodes. Then in Figure \ref{fig:eg_shortest_walk}
  the edge weight between $(1, 1998)$ and $(2, 1998)$ is $1$ and the edge weight between $(2, 1998)$ and $(2, 2018)$ is $10$.
-In general, a time-preserving walk can be defined as follows.
+In general, a weighted time-preserving walk can be defined as follows.
 
 \begin{definition}
-A \textbf{time-preserving walk}  of length $m$ on an evolving graph $G_n$ is a time-ordered sequence of active nodes, $\langle (v_1, t_1), (v_2, t_2), \ldots, (v_m, t_m) \rangle$, where $t_1 \le t_2 \le \cdots \le t_m$ and
-$v_i = v_j$ if and only if $t_i \ne t_j$.
+A \textbf{weighted time-preserving walk} of length $m$ on an evolving graph $G_n$ is an alternating
+time-ordered sequence of active nodes and edges, $\langle (v_1, t_1), e_1, (v_2, t_2), e_2, (v_3, t_3) \ldots, e_m, (v_m, t_m) \rangle$, where $t_1 \le t_2 \le \cdots \le t_m$ and
+$v_i = v_j$ if and only if $t_i \ne t_j$, and $e_i$ can be either a weighted static edge or weighted causal edge.
 \end{definition}
@@
 We observe that static edges link nodes in space while causal edges link nodes in time.
-Hence we would like to distinguish temporal distance from spatial distance in an evolving graph: we let the length of a static edge be one and the length of a causal edge be the temporal distance between the two nodes.
+Hence we would like to distinguish temporal distance from spatial distance in an evolving graph.
+For two linked temporal nodes, we set the length of a static edge between them to be one and the length of a causal edge to be the temporal distance between them.
+The following Julia function measures the temporal distance between two active nodes in an evolving graph.
+\begin{lstlisting}
+function temporal_distance(v1::TimeNode,
+                           v2::TimeNode, beta::Real = 1.)
+  beta* abs(node_timestamp(v1) - node_timestamp(v2))
+end
+\end{lstlisting}
+This function defines the temporal distance to be the difference between their time stamps scaled by a hyper-parameter
+\texttt{beta}.
 In the simplest case, the time-respecting walk
@@
 traverse $10$ time stamps and thuse has length $10$.
-
 A time-preserving walk (and path) can traverse both causal edges and static edges.
-The following Julia function measures the temporal distance between two active nodes in an evolving graph.
-
-\begin{lstlisting}
-function temporal_distance(v1::TimeNode,
-                           v2::TimeNode, beta::Real = 1.)
-  beta* abs(node_timestamp(v1) - node_timestamp(v2))
-end
-\end{lstlisting}
-which means the temporal distance is the difference between their time stamps scaled a hyper-parameter
-\texttt{beta}.
 
@@
 Using this idea, we can generalize walk-based centrality measures such as
-the Katz Centrality \cite{estrada09} and Communicability Betweenness \cite{alsayed15}.
+the Katz centrality \cite{estrada09} and communicability betweenness \cite{alsayed15}.
 Second, we could generalize the definition of shortest paths as shortest temporal paths and replace shortest paths in centrality measures with shortest temporal paths where possible.
-This way we can define temporal betweenness centrality and temporal closeness centrality \cite{nicosia13}.
+This way we can define temporal betweenness centrality and temporal closeness centrality \cite{ntmm13}.
 
@@
 We take account of this communication time by deriving centrality measures from the original theses of the ideas and show communication time has important impact on the final node ratings (and rankings).
-We note that our goal is not about providing efficient centrality algorithms which is out of the scope of this paper.
+We note that our goal is not to provide efficient centrality algorithms, which is out of the scope of this paper.
 
@@
 % katz centrality from first principle
-Katz Centrality accounts the influence of nearest-neighbours to a give node and the influence of other nodes
-separated at a certain distance from it. The $k$th power of adjacency matrix $A$, i.e., $A^k$, of a graph $G$ accounts for walk of length $k$. The expansion
+Katz centrality accounts the influence of nearest-neighbours to a give node and the influence of other nodes
+separated at a certain distance from it. The $k$th power of the adjacency matrix $A$ of a graph $G$ accounts for walk of length $k$. The expansion
 \begin{equation}
   \label{eq:a}
-  A^0 + \alpha A + \alpha^2 A^2 + \cdots,
+  A^0 + \alpha A + \alpha^2 A^2 + \cdots
 \end{equation}
-converges to $(I - \alpha A)^{-1}$ when $\alpha < 1/\rho(A)$, the spectral radius of $A$. The $(i,j)$ entry of \eqref{eq:a}
-accounts all walks from $i$ and $j$ with the influence of walks of length $k$ scaled by a factor of $\alpha^k$.
+converges to $(I - \alpha A)^{-1}$ when $\alpha < 1/\rho(A)$. The $(i,j)$ entry of \eqref{eq:a}
+counts all walks from $i$ and $j$ with the influence of walks of length $k$ scaled by a factor of $\alpha^k$.
 The Katz centrality of node $i$ is the $i$th row sum of $(I - \alpha A)^{-1}$, which is the sum of influence of all the nodes that node $i$ can reach via a walk.
@@
 Then the Katz score of a node $i$ at time stamp $t$, denoted by $(i,t)$, is the sum of influence of all the active nodes that $(i,t)$ can reach via a time-preserving walk.
-Unlike \cite{grindrod11}, we also consider the temporal distance between two nodes. For example, the temporal distance between $(i, 2001)$ and $(i, 2018)$ is $17$.
+Unlike \cite{gphe11}, we also consider the temporal distance between two nodes. For example, the temporal distance between $(i, 2001)$ and $(i, 2018)$ is $17$.
 % julia code implementation
 With the definition of \texttt{temporal\_distance} introduced in Section \ref{sec:time-pres-paths}.
-We define the temporal Katz score of node $(i, t)$ as
-
-\begin{lstlisting}[caption={Temporal Katz Centrality of Single Node},label={lst:katz}]
+We define the temporal Katz score of node $(i, t)$ by the algorithm given in Listing \ref{lst:katz}.
+
+\begin{lstlisting}[caption={Temporal Katz Centrality of Single Node},label={lst:katz}, captionpos=b]
 function temporal_katz(g::AbstractEvolvingGraph,
@@
 % explain the code
-The algorithm \texttt{temporal\_katz} performs a breadth first search (BFS) on evolving graph $g$ that
-starts at \texttt{TimeNode} $v$, which represents a node at a specific time stamp \footnote{See also \url{https://etymoio.github.io/EvolvingGraphs.jl/latest/base.html#EvolvingGraphs.TimeNode}}.
+The algorithm \texttt{temporal\_katz} performs a breadth first search (BFS) on an evolving graph $g$ that
+starts at \texttt{TimeNode} $v$, which represents a node at a specific time stamp.
+% \footnote{See also \url{https://etymoio.github.io/EvolvingGraphs.jl/latest/base.html#EvolvingGraphs.TimeNode}}.
 For each \texttt{TimeNode} $v$, we accumulate the influence of linked nodes according to their spatial and temporal
@@
 % example on 3 timestamp evolving graph
-for Figure \ref{fig:katz_eg2}, we have
+for Figure \ref{fig:katz_eg2}, we find the rating of each active node as shown below.
 \begin{lstlisting}
@@
 \end{lstlisting}
-The total scores at all time stamps are
+Here, for example, \texttt{TimeNode(A,2)} represents active node $(A,2)$.
+
+The overall score of a node is the sum of scores of the node at different time stamps. We use the overall scores to measure the overall importance of nodes in an evolving graph.
+Here are the overall scores of the three nodes.
 \begin{lstlisting}
@@
 Commonly it is defined based on the shortest paths.
-However, key messages do not necessarily follow the shortest paths and thus it makes senses to consider walks instead of shortest paths.
-Recall the $(i,j)$ entry of the resolvent matrix $(I - \alpha A)^{-1}$ provide information about the communication from $i$ to $j$. We could therefore define the resolvent betweenness for node $v$ as
+However, key messages do not necessarily follow the shortest paths and thus it makes sense to consider walks instead of shortest paths.
+Recall that the $(i,j)$ entry of the resolvent matrix $(I - \alpha A)^{-1}$ provides information about the communication from $i$ to $j$.
+By considering the difference in rating with and without edges linking to node $v$, we could define the resolvent betweenness for node $v$ as
 \begin{equation}
@@
 The matrix $A - E_i$ represents a graph with all edges involving the node $v$ removed.
-For $(I-\alpha A)^{-1}_{i,j}$ we could simply modify Listing \ref{lst:katz} so that it only accumulate scores when the end node is $j$.
-For the $(I - \alpha (A-E_v))^{-1}_{i,j}$ part, we can apply the above the same algorithm on a graph with node $v$ and related edges removed.
-Therefore the general temporal resolvent betweenness centrality can be defined as
-\begin{lstlisting}
+For $(I-\alpha A)^{-1}_{i,j}$ we could simply modify Listing \ref{lst:katz} so that it only accumulates scores when the end node is $j$.
+For the $(I - \alpha (A-E_v))^{-1}_{i,j}$ part, we can apply the same algorithm on a graph with node $v$ and related edges removed.
+Therefore the general temporal resolvent betweenness centrality can be defined by the algorithm in Listing \ref{lst:resolvent}.
+\begin{lstlisting}[caption={Temporal Resolvent Betweenness of Single Node},label={lst:resolvent}, captionpos=b]
 function temporal_resolvent_betweenness(g1, g2,
@@
 % closeness centrality
-
-Let $d_{ij}$ be the length of the shortest path from $i$ and $j$ in a static graph. Then
-the closeness centrality of a node $i$ is defined
+Let $d_{ij}$ be the length of the shortest path from $i$ and $j$ in a static graph.
+The closeness centrality of a node $i$ is a measure of importance calculated by considering all the shortest paths between node $i$ and all other nodes in the graph, that is
 $$
@@
 where $N-1$ is the total number of reachable nodes.
+The more important a node is, the closer it is to all other nodes.
 For evolving graphs, we need to consider the shortest temporal path from $(i,t_i)$ to $(j,t_j)$, for any time stamp $t_i \leq t_j$.
-Depends on how define the length of shortest temporal path, the closeness centrality can counts static edges, causal edges, or both.
-The key difference between Katz centrality and closeness centrality is the fact here we only consider shortest temporal paths, not just every temporal walks.
-We could apply BFS to find the shortest temporal path from $(v,t)$ to any other nodes in the evolving graphs. The algorithm is shown as follows.
-
-\begin{lstlisting}
+Depending on how we define the length of shortest temporal path, the closeness centrality can counts static edges, causal edges, or both.
+The key difference between Katz centrality and closeness centrality is the fact here we only consider shortest temporal path, not every temporal walk.
+We could apply BFS to find the shortest temporal path from $(v,t)$ to any other nodes in the evolving graphs. The algorithm is shown as the algorithm given in Listing
+\ref{lst:closeness}.
+
+\begin{lstlisting}[caption={Temporal Closeness of Single Node},label={lst:closeness}, captionpos=b]
 function temporal_closeness(g::AbstractEvolvingGraph,
@@
 that the temporal distance between nodes in an evolving graph can impact the final centrality scores.
-We would like to design a temporal PageRank algorithm that takes account of between
+We would like to design a temporal PageRank algorithm that takes account of
 the temporal distance and the spatial distance. The generalisation is based on two ideas:
@@
 a simple static graph can provide misleading information about the structure of the network.
-In \cite{chen16}, we derive a block adjacency matrix representation of an evolving graph and prove it is the correct representation of an evolving graph.
-Let $E'$ is the set of causal edges and $\hat E$ is the set of static edges then
+In \cite{chen16}, we derive a block adjacency matrix representation of an evolving graph and
+show it is possible to represent an evolvig graph as a block adjacency matrix.
+Let $E'$ be the set of causal edges and $\hat E$ be the set of static edges. Then
 an evolving graph can be represented as
@@
 \tilde E &= \{((1,\!1998), (2,\!1998)), ((1,\!1999), (3,\!1999)), ((2,\!2018), (3,\!2018))\},\\
-E'  &= \{((1,\!1998), (1,\!1999)), ((2,\!1999), (2,\!2018)), ((3,\!1999), (3,\!2018))\}.
+E'  &= \{((1,\!1998), (1,\!1999)), ((2,\!1999), (2,\!2018)), ((3,\!1999), (3,\!2018))\}
 \end{align*}
@@
 0 & 0 & 0 & 0 & 0 & 0
-\end{pmatrix}
+\end{pmatrix}.
 \]
@@
 \end{center}
-\caption{A static graph corresponding to the evolving graph example of
-Figure~\ref{fig:eg_shortest_walk}. The green nodes are active nodes while the
-red nodes are inactive nodes.
+\caption[A static graph corresponding to the evolving graph example of
+Figure~\ref{fig:eg_shortest_walk}.]{A static graph corresponding to the evolving graph example of
+Figure~\ref{fig:eg_shortest_walk}.
 The black lines are edges in the static edge set $\tilde E$ and are encoded
@@
 
-Notice that the lower triangular blocks of matrix $\bm M_n$ are zeros.
+Notice that the lower triangular blocks of matrix $\bm M_n$ are zero.
 This is because all the causal edges are time preserving. We consider the transpose of matrix $\bm M_n$, which reverse the direction of static edges and causal edges.
@@
 
-The function \texttt{block\_adjacency\_matrix} convert an evolving graph $g$ to a block adjacency matrix $\bm M$.
+The function \texttt{block\_adjacency\_matrix} converts an evolving graph $g$ to a block adjacency matrix $\bm M$.
 Every row sum of the block Google matrix is equal to one.
@@
 represents the PageRank rating of a node.
-
-For Figure \ref{fig:katz_eg2}, we set $alpha$ be $0.85$ and $balance$ be $1.0$.
+The rank of each node can be computed iteratively from the block Google matrix using the power method.
+For Figure \ref{fig:katz_eg2}, we let $alpha$ be $0.85$ and $balance$ be $1.0$.
+% power method
 Then the PageRank scores are
@@
 
-We conduct the following experiments using \texttt{IntAdjacencyList}, which represents an evolving graph $g$ with integer nodes and integer time stamps as adjacency lists.
+We conduct the following experiments using graph type \texttt{IntAdjacencyList} from EvolvingGraphs.jl, which represents an evolving graph $g$ with integer nodes and integer time stamps as adjacency lists.
 In particular, each active node in $g$ stores its forward neighbours in a list.
@@
 
-We generate a random evolving graph $g$ with $500$ nodes and $499183$ static edges and $10$ time stamps. Using the Katz centrality in \eqref{eq:q}, we find the top $10$ most important nodes.
+% need to compute it for all 500 nodes and check the changes.
+% maybe run it on AWS.
+We generate a random evolving graph $g$ with $500$ nodes and $499183$ static edges and $10$ time stamps.
+We focus on studying the changes of rating of the following nodes.
+The second element in each tuple is the Katz Centrality rating computed using \eqref{eq:q}.
 \begin{lstlisting}
@@
 \end{lstlisting}
-Instead of running temporal Katz centrality for each active node in the evolving graph $g$,
-we only consider these $10$ most important nodes because in practice we usually are just interested in the rankings and ratings of the most important nodes. For each node in the above list,
+% Instead of running temporal Katz centrality for each active node in the evolving graph $g$,
+% we only consider these $10$ most important nodes because in practice we usually are just interested in the rankings and ratings of the most important nodes.
+For each node in the above list,
 we compute the node score at each time stamp and the overall score.
-Here we set $alpha = 0.5$  and $max\_level = 3$.  The results are shown in Table \ref{table:ranking}
-and Table \ref{table:ranking2}.
-We observe that the Katz ratings in general are smaller when we take account of the temporal information. The rankings, however, are stable. For rankings at time stamp $1$,
-only the top two nodes $459$ and $469$ change positions.
+Here we set $alpha = 0.5$  and $max\_level = 3$.  The results are shown in Table \ref{table:ranking} and Table \ref{table:ranking2}.
+Table \ref{table:ranking} shows the ratings where the causal edges
+all have edge weight zero. Table \ref{table:ranking2} shows the ratings where the weights of causal edges are their temporal differences.
+For each table we notice that ratings (and rankings) at the first time stamp $t_1$ are very different from the overall ratings (and rankings).
+Comparing the two tables, we observe that the Katz ratings in general are smaller when we take account of the temporal information.
+The rankings, however, are stable.
+For rankings at time stamp $1$, only the top two nodes $459$ and $469$ change positions.
 The overall rankings stays unchanged.
@@
   \begin{tabular}{ c | c | c | c }
-    Ranking at $t_1$ & Rating at $t_1$ & Overall ranking & Overall rating \\
+    Ranking at $t_1$ & Rating at $t_1$ & Overall ranking & Overall rating \\ \hline
      469 & $0.7193$ & 183 & $5.975$ \\
@@
   \begin{tabular}{ c | c | c | c }
-    Ranking at $t_1$ & Rating at $t_1$ & Overall ranking & Overall rating \\
+    Ranking at $t_1$ & Rating at $t_1$ & Overall ranking & Overall rating \\ \hline
      \textbf{459} & $0.6290$ & 183 & $5.576$ \\
@@
 The results are shown in Table \ref{table:ranking3} and Table \ref{table:ranking4}.
-For temporal closeness centrality, we notice that most of rankings are changed when we take account of the temporal information.
+As before, for both tables the ratings (and rankings) at the first
+time stamp $t_1$ are very different from the overall ratings (and rankings).
+However, when we compare the two tables Table \ref{table:ranking3}
+and \ref{table:ranking4}, we notice that
+for temporal closeness centrality most of rankings are changed when we take account of the temporal information.
 
@@
 \begin{tabular}{ c | c | c | c }
-  Ranking at $t_1$ & Rating at $t_1$ & Overall ranking & Overall rating \\
+  Ranking at $t_1$ & Rating at $t_1$ & Overall ranking & Overall rating \\ \hline
    296 & $0.4938$ & 469 & $5.040$ \\
@@
 \begin{tabular}{ c | c | c | c }
-  Ranking at $t_1$ & Rating at $t_1$ & Overall ranking & Overall rating \\
+  Ranking at $t_1$ & Rating at $t_1$ & Overall ranking & Overall rating \\ \hline
    296 & $0.2540$ & 469 & $3.562$ \\
@@
 
-We describe in details the generalisation of centrality algorithms for evolving graphs.
-We conduct experiments to show that temporal information is an important factor for evolving graph centrality ranking and rating.
-In particular, we observe temporal Katz centrality is much more stable than temporal closeness centrality if we vary the influence of temporal information.
-We also derive a temporal PageRank centrality using reversed temporal walks and block adjacency matrix.
+When we consider evolving graph centrality, it is very useful to
+consider the influence of temporal information.
+A time-preserving path contains both static edges and causal edges.
+We study the influence of causal edges on graph centrality by varying
+the edge weights. We derive the centrality algorithms from the view of traffic flow.
+
+We observe that temporal Katz centrality is stable when we vary the causal edge weights. However the rankings of nodes computed by temporal closeness centrality changes a lot in our experiment.
+Further experiments especially on larger real world datasets are needed to confirm our observation.
+We also derive a temporal PageRank centrality algorithm by considering reversed temporal walks and block adjacency matrix.
+It would be interesting to compare the ratings (and rankings) computed by this temporal PageRank algorithm on an evolving graph with the original PageRank on the corresponding aggregated static graph.
 
